---
title: "Geomorphology_ANTE"
author: "KWhitmore"
date: "10/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(plotly)
library(dplyr)
library(tidyr)
library(zoo)
library(plot3D)
library(splines)
library(Ecdat)
library(dplyr)
library(sp)
library(geosphere)


```

## BUild the geomorphology data frame for ATENAS

```{r build df}

Geomorph <- read.csv(here::here("/Geomorphology/Atenas/ANTENAS_GEOMORPH_2021-09-28.csv"))
Geomorph$X <- NULL
Geomorph$ID <- NULL
Geomorph$trksegID <- NULL
Geomorph$name <- NULL
Geomorph$dist <- NULL

Geomorph <- Geomorph[,c("lon","lat","ele","time","lat_wypt","lon_wypt","ele_wypt")]


```

##Plot the geomorphology data in 3-d

```{r 3d plot no synop, echo=FALSE}


fig <- plot_ly(Geomorph, x = ~lat, y = ~lon, z = ~ele, size = 1
)
fig <- fig %>% add_markers()
#fig <- fig %>% add_trace(x = ~lat, y = ~lon, z = ~ele, #color = ~EOS_no#, colors = c('Blue','Yellow'),
#                         mode = 'markers')
fig <- fig %>% layout(scene = list(xaxis = list(title = 'lat'),
                                   yaxis = list(title = 'lon'),
                                   zaxis = list(title = 'elevation')))

fig


```

## Now Plot data in 3D including synoptic points


```{r 3d plot and synop, echo=FALSE}

df <- full_join(synop,Geomorph, by=c("lat","lon","ele")) 

fig <- plot_ly(df, x = ~lat, y = ~lon, z = ~ele, size = 1,
               marker = list(color = ~log10(CO2_ppm_ave), colorscale = c('#FFE1A1', '#683531'), showscale = TRUE)
            )
fig <- fig %>% add_markers()
#fig <- fig %>% add_trace(x = ~lat, y = ~lon, z = ~ele, #color = ~EOS_no#, colors = c('Blue','Yellow'),
#                         mode = 'markers')
fig <- fig %>% layout(scene = list(xaxis = list(title = 'lat'),
                                   yaxis = list(title = 'lon'),
                                   zaxis = list(title = 'elevation')))

fig
```
#are you seeing the problem? 
The synoptic data points seem to be fairly well geolocated for lat long, but not for elevation. 
So we need to build a smoothinf 

We need to 

#working with 3-D is hard. full stop.
In this code chunk, we start by smooting a line to the lat long data, which appears to be more accurate than the elevation

We will do this in parts though, be cause the relationship between lat lon can not be described as a function
```{r first spline, echo=FALSE}

#Cut up lat long into peices, and then fit spline


Geomorph_sub <-Geomorph %>% filter(lon >= -78.19302)
model <- lm(lon~bs(lat,
                   knots = c(-0.3164286,-0.3163748,-0.3162296,-0.3161252,-0.3161399,-.3156738, -0.3154703,-0.3152688,-0.3152838), 
                   degree = 6),
            data=Geomorph_sub)

latlims <- range(Geomorph_sub$lat)
lat.grid <- seq(from=latlims[1],to=latlims[2], by=.000001)

pred <-predict(model,newdata=list(lat=lat.grid),se=T)

plot(Geomorph_sub$lat,Geomorph_sub$lon,main="regressionSplinePLot")
lines(lat.grid,pred$fit,col='red',lwd=3)

#this looks pretty good! So we will save the data in a data frame

lat <- lat.grid
lon <- pred$fit
df1<-as.data.frame(lat)
df1$lon <- lon
df1$num <- '1'
df1 <-df1 %>% filter(lat <= -0.3152791)

fig<-plot_ly(data = df1, x = ~lat, y = ~lon)


```
#next section is very small
```{r second spline, echo=FALSE}
Geomorph_sub <-Geomorph %>% filter(lon <= -78.19310 &
                                     lon >= -78.19333)

model <- lm(lon~bs(lat,
                   knots = c(0), 
                   degree = 3),
            data=Geomorph_sub)

latlims <- range(Geomorph_sub$lat)
lat.grid <- seq(from=latlims[1],to=latlims[2], by=.000001)
pred <-predict(model,newdata=list(lat=lat.grid),se=T)

plot(Geomorph$lat,Geomorph$lon,main="regressionSplinePLot")
lines(lat.grid,pred$fit,col='red',lwd=3)

lat <- lat.grid
lon <- pred$fit
df2<-as.data.frame(lat)
df2$lon <- lon
df2$num <- '2'
df2 <- df2[order(-lat),]

```
third section, here we go!

```{r third spline, echo=FALSE}

#Geomorph_sub <-Geomorph %>% filter(lon <= -78.19340)
Geomorph_sub <-Geomorph %>% filter(lon <= -78.19336)


model <- lm(lon~bs(lat,
                   knots = c(0), 
                   degree = 3),
            data=Geomorph_sub)

latlims <- range(Geomorph_sub$lat)
lat.grid <- seq(from=latlims[1],to=latlims[2], by=.000001)
pred <-predict(model,newdata=list(lat=lat.grid),se=T)

plot(Geomorph$lat,Geomorph$lon,main="regressionSplinePLot")
lines(lat.grid,pred$fit,col='red',lwd=3)

##dataframe 3
lat <- lat.grid
lon <- pred$fit
df3<-as.data.frame(lat)
df3$lon <- lon
df3$num <- '3'
##
```
good job! now lets bind all the dataframes together
```{r bind dataframes, echo=FALSE}

#now we need to make a dataframe that discribes this relationship between lat lon
df_prediction <- rbind(df1,df2,df3)


plot(df_prediction$lon~df_prediction$lat,col=df_prediction$num)

plot(Geomorph$lat,Geomorph$lon)

```

This is looking pretty darn good. But there is a gap in the lon data that we need to deal with. It's proving hard to deal with because this is not a function!

So we will add some data to the dataframe  to fill the gap.
Just a simple linear regression between the df1 and df3
```{r manual add dataframes}
#point1 -0.3152791	-78.19296
#point2 -0.3152543	-78.19312
m = (-78.19312	- (-78.19296))/(-0.3152543 - (-0.3152791))
#slope = 3.597122
b = -78.19296 - m*(-0.3152791)
latlims <- range(Geomorph_sub$lat)
lat.grid <- seq(from=-0.3152791,to=-0.3152543, by=.000001)

##dataframe 4
lat <- lat.grid
df4<-as.data.frame(lat)
df4$lon <- m*df4$lat + b

df4 <-df4 %>% filter(lon < -78.19296)

df4$num <- '4'
df4 <- df4[order(lat),]

##also fill in between df 2 and 3 
#point1 -0.3153853	-78.19334	2
#point2 -0.3153644	-78.19338	3
m = (-78.19334	- (-78.19338))/(-0.3153853 - (-0.3153644))
#slope = 3.597122
b = -78.19338 - m*(-0.3153644)
latlims <- range(Geomorph_sub$lat)
lat.grid <- seq(from=-0.3153853,to=-0.3153644, by=.000001)

##dataframe 5
lat <- lat.grid
df5<-as.data.frame(lat)
df5$lon <- m*df5$lat + b

df5 <-df5 %>% filter(lat > -0.3153853 & lat < -0.3146854)

df5$num <- '5'
df5 <- df5[order(lat),]

```

ok, lets bind in that last dataframe

```{r bind dataframes, echo=FALSE}

#now we need to make a dataframe that discribes this relationship between lat lon
df_prediction <- rbind(df1,df4,df2,df3,df5)

plot(df_prediction$lon~df_prediction$lat,col=df_prediction$num)

plot(Geomorph$lat,Geomorph$lon)

```
now we have a smooth data frame of lat/lon data, we calculate the distance between each point
```{r calc dist}

###create a loop and calculate distance along the river from the predict_df. THen we can bind in the GEOMORPH!
df_prediction <- rbind(df1,df4,df2,df5,df3) %>% drop_na(lat)

df_prediction$num <- NULL
df_prediction <- df_prediction[,c("lon","lat")]
colnames(df_prediction) <- c("lon_fit","lat_fit")
df_prediction$lon_dist <- NA
df_prediction$lat_dist <- NA
i <- 2
for(i in 1:nrow(df_prediction)) {
  if (i == 1) {

      df_prediction$dist <- 0
#      df_prediction[i,"lon_dist"] <- 0
#      df_prediction[i,"lat_dist"] <- 0
      
    } else {
      df_prediction[i,"lon_dist"] <- df_prediction[i-1,"lon_fit"]
      df_prediction[i,"lat_dist"] <- df_prediction[i-1,"lat_fit"]
      df_prediction[i,"dist"] <- df_prediction[i-1,"dist"] + distHaversine(
        c(df_prediction[i,"lon_fit"], df_prediction[i,"lat_fit"]), 
        c(df_prediction[i,"lon_dist"], df_prediction[i,"lat_dist"]))
      }
}
```

snap the points in our origional dama frame to bring in the elevation data


```{r snap points to lat lon}


#df_prediction <- df_prediction[,c("lon","lat","num")] 
x <- SpatialPoints(Geomorph[,c(1:2)])
y <- SpatialPoints(df_prediction[,c(1:2)]) 
plot(x, col = "red")
points(y, col = "green")
snap = apply(spDists(x, y), 1, which.min)
points(y[snap,], pch = 3)


snap_df <- y[snap,]
coords_df <- snap_df@coords
pred <- as.data.frame(coords_df)
Geomorph$lon_fit <- pred$lon
Geomorph$lat_fit <- pred$lat


df_prediction <- full_join(df_prediction,Geomorph,by=c("lon_fit","lat_fit"))
```
first I need to make sure that what I have done really worked

```{r testing snap to line, echo=FALSE}


fig <- plot_ly(Geomorph, x = ~lat, y = ~lon, z = ~ele, size = 1)
fig <- fig %>% add_markers()
fig <- fig %>% add_trace(x = ~lat_fit, y = ~lon_fit, z = ~ele, colors = c('Yellow'),
                         mode = 'markers')
fig <- fig %>% layout(scene = list(xaxis = list(title = 'lat'),
                                   yaxis = list(title = 'lon'),
                                   zaxis = list(title = 'elevation')))

fig


```

ok sweet that looks really good

We also need to snap the synoptic df 
```{r snap synop pts}

#read in synop data

#synop <- read.csv(here::here("Synoptic/ANTE_2022-01-09.csv"))
#synop <- read.csv(here::here("Synoptic/ANTE_2022-01-27.csv"))
#synop <- read.csv(here::here("Synoptic/ANTE_2022-02-11.csv"))
#synop <- read.csv(here::here("Synoptic/ANTE_2022-02-13.csv"))
synop <- read.csv(here::here("Synoptic/ANTE_2022-03-23.csv"))


synop$X <- NULL
synop$ID <- NULL
#colnames(synop) <- c("lon","lat","ele","Date","EOS_no","Flux_ave","Tract","Point","CO2_ppm_ave","DateTime","SampleID","DOC","TDN","Notes")


#there is a bad elevation data in synop, I am replacing it here, but need to work on figuring out what is up
#synop$ele<-replace(synop$ele, synop$ele<4100,4302) 


x <- SpatialPoints(synop[,c(1:2)])
y <- SpatialPoints(df_prediction[,c(1:2)]) 
plot(x, col = "red")
points(y, col = "green")
snap = apply(spDists(x, y), 1, which.min)
points(y[snap,], pch = 3)


snap_df <- y[snap,]
coords_df <- snap_df@coords
pred <- as.data.frame(coords_df)
synop$lon_fit <- pred$lon
synop$lat_fit <- pred$lat
synop <- synop[,c("Date","EOS_no","Flux_ave","Tract","Point","CO2_ppm_ave","adjusted_ppm", "DOC","TDN","lon_fit","lat_fit","AirTemp_c","VaisalaType","Total_hPa","GAVI_waterTempAve")]


df_prediction <- full_join(df_prediction,synop,by=c("lon_fit","lat_fit"))
#Geomorph <- full_join(Geomorph,synop_2, by = c("lon_fit","lat_fit"))

```

```{r snap waterchem pts}

WaterChem <- read.csv(here::here("/WaterChem/WaterChem_synoptic_2022-01-28.csv")) %>% filter (Wetland == "ANTE")%>%drop_na(lat)
WaterChem <- WaterChem[,c("lon","lat","DOC","TDN")]

#look at this again later, I think there are some bad data here, there's a really big gap

x <- SpatialPoints(WaterChem[,c(1:2)])
y <- SpatialPoints(df_prediction[,c(1:2)]) 
plot(x, col = "red")
points(y, col = "green")
snap = apply(spDists(x, y), 1, which.min)
points(y[snap,], pch = 3)


snap_df <- y[snap,]
coords_df <- snap_df@coords
pred <- as.data.frame(coords_df)
WaterChem$lon_fit <- pred$lon
WaterChem$lat_fit <- pred$lat
WaterChem <- synop[,c("DOC","TDN","lon_fit","lat_fit")]


```

now read in other other measurments of geomorphology -width and depth




##calculate distance between each coordinate.
Here's the deal. We need to calcualte the distance between each coordinate 

First, lets find the most western lat point



now we have created a distance column that we can plot the elevation data against. lets see how that looks

```{r plot dist v ele, echo = FALSE}

fig <- plot_ly(df_prediction, x = ~dist, y = ~ele, size = 1)
fig
```

kriddie, you are doing so good!
Okay, now lets fit another spline to this puppy


##loess spline
 loess is good for this

```{r diff way}

fit <- loess(ele ~ dist, degree=2, span = 0.20, data=df_prediction)

df_prediction %>% 
  drop_na(ele) %>%
  mutate(smooth = fit$fitted) %>%
  ggplot(aes(dist, ele)) +
  geom_point(size = 3, alpha = .5, color = "grey") +
  geom_line(aes(dist, smooth), color="red")

fig <- plot_ly(df_prediction, x = ~dist, y = ~ele, size = 1)
fig

```

we have a bit of a problem with the two ends. The spline is not extrapolating the beginning value and downstream is not leveling out, instead it curves up. So we need to extrapolate to distance 0 and do *something* for distanceds more than 432 or so.


take the loess spline and make a data frame that interpolates these data points

```{r interpolate loess, echo=FALSE}
#save <- df_prediction
#df_prediction <- save

#fit <- loess(ele ~ dist, degree=2, span = 0.30, data=df_prediction)
fit <- loess(ele ~ dist, degree=2, span = 0.20, data=df_prediction)
distlims <- range(df_prediction$dist)

pred1 <- predict(fit, data.frame(dist = df_prediction$dist), se = TRUE)

df_prediction$ele_fit <- pred1$fit

##fix upstream
#how about we find the slope of the first predicted point dist = 0.7506700 and about a meter downstream
up <- which.min(abs(df_prediction$dist-0.7506700))
down <- which.min(abs(df_prediction$dist-1.8))

slope <- (df_prediction[down,"ele_fit"] - df_prediction[up,"ele_fit"])/(df_prediction[down,"dist"] - df_prediction[up,"dist"])
b = df_prediction[down,"ele_fit"] - slope*df_prediction[down,"dist"]
df_prediction_a <- df_prediction %>% filter(dist < df_prediction[up,"dist"])
df_prediction_b <- df_prediction %>% filter(dist >= df_prediction[up,"dist"])
df_prediction_a$ele_fit <- slope*df_prediction_a$dist + b
df_prediction <- rbind(df_prediction_a,df_prediction_b)
rm(df_prediction_a,df_prediction_b)
###
##fix downstream - maybe i should just approximate to .01?

up <- which.min(abs(df_prediction$dist-432.7489))
#down <- which.min(abs(df_prediction$dist-434))

slope <- -.01
b = df_prediction[up,"ele_fit"] - slope*df_prediction[up,"dist"]
df_prediction_a <- df_prediction %>% filter(dist > 432.7489)
df_prediction_b <- df_prediction %>% filter(dist <= 432.7489)
df_prediction_a$ele_fit <- slope*df_prediction_a$dist + b
df_prediction <- rbind(df_prediction_a,df_prediction_b)
rm(df_prediction_a,df_prediction_b)
##

## there are problems in the middle too. 

up <- which.min(abs(df_prediction$dist-240.6755))
down <- which.min(abs(df_prediction$dist-245.2735))

slope <- (df_prediction[down,"ele_fit"] - df_prediction[up,"ele_fit"])/(df_prediction[down,"dist"] - df_prediction[up,"dist"])
b = df_prediction[up,"ele_fit"] - slope*df_prediction[up,"dist"]
df_prediction_a <- df_prediction %>% 
  filter(dist > df_prediction[up,"dist"] & dist < df_prediction[down,"dist"])
df_prediction_b <- df_prediction %>% 
  filter(dist < df_prediction[up,"dist"] | dist > df_prediction[down,"dist"])
df_prediction_a$ele_fit <- slope*df_prediction_a$dist + b
df_prediction <- rbind(df_prediction_a,df_prediction_b)
rm(df_prediction_a,df_prediction_b)

##

## there are problems in the middle too. 

up <- which.min(abs(df_prediction$dist-247.8527))
down <- which.min(abs(df_prediction$dist-251.5112))

slope <- (df_prediction[down,"ele_fit"] - df_prediction[up,"ele_fit"])/(df_prediction[down,"dist"] - df_prediction[up,"dist"])
b = df_prediction[up,"ele_fit"] - slope*df_prediction[up,"dist"]
df_prediction_a <- df_prediction %>% 
  filter(dist > df_prediction[up,"dist"] & dist < df_prediction[down,"dist"])
df_prediction_b <- df_prediction %>% 
  filter(dist < df_prediction[up,"dist"] | dist > df_prediction[down,"dist"])
df_prediction_a$ele_fit <- slope*df_prediction_a$dist + b
df_prediction <- rbind(df_prediction_a,df_prediction_b)
rm(df_prediction_a,df_prediction_b)

##

## there are problems in the middle too. 

up <- which.min(abs(df_prediction$dist-348.5920))
down <- which.min(abs(df_prediction$dist-355.0635	))

slope <- (df_prediction[down,"ele_fit"] - df_prediction[up,"ele_fit"])/(df_prediction[down,"dist"] - df_prediction[up,"dist"])
b = df_prediction[up,"ele_fit"] - slope*df_prediction[up,"dist"]
df_prediction_a <- df_prediction %>% 
  filter(dist > df_prediction[up,"dist"] & dist < df_prediction[down,"dist"])
df_prediction_b <- df_prediction %>% 
  filter(dist < df_prediction[up,"dist"] | dist > df_prediction[down,"dist"])
df_prediction_a$ele_fit <- slope*df_prediction_a$dist + b
df_prediction <- rbind(df_prediction_a,df_prediction_b)
rm(df_prediction_a,df_prediction_b)

##

## there are problems in the middle too. 

up <- which.min(abs(df_prediction$dist-376.3404))
down <- which.min(abs(df_prediction$dist-390.7298	))

slope <- (df_prediction[down,"ele_fit"] - df_prediction[up,"ele_fit"])/(df_prediction[down,"dist"] - df_prediction[up,"dist"])
b = df_prediction[up,"ele_fit"] - slope*df_prediction[up,"dist"]
df_prediction_a <- df_prediction %>% 
  filter(dist > df_prediction[up,"dist"] & dist < df_prediction[down,"dist"])
df_prediction_b <- df_prediction %>% 
  filter(dist < df_prediction[up,"dist"] | dist > df_prediction[down,"dist"])
df_prediction_a$ele_fit <- slope*df_prediction_a$dist + b
df_prediction <- rbind(df_prediction_a,df_prediction_b)
rm(df_prediction_a,df_prediction_b)

##
```

```{r calc slope, echo=FALSE}

df_prediction$slope <- NA
for(i in 1:nrow(df_prediction)) {       # for-loop over rows
  df_prediction$dist_down[i] <- df_prediction$dist[i+1]
  df_prediction$ele_down[i] <- df_prediction$ele_fit[i+1]
}

df_prediction$slope <- (df_prediction$ele_fit - df_prediction$ele_down)/(df_prediction$dist - df_prediction$dist_down)
df_prediction$dist_down <- NULL
df_prediction$ele_down <- NULL

df_predictionblah <- df_prediction%>%filter(slope>0)

###
df_prediction <- df_prediction[order(df_prediction$dist),]
df_prediction$slope <- NA
loop <- df_prediction%>%drop_na(ele_fit)
for(i in 1:nrow(loop)) {       # for-loop over rows
  x = loop$dist[i] - 5
  loop$ele_minus[i] <- loop[which.min(abs(loop$dist-x)),]$ele_fit
  loop$dist_minus[i] <- loop[which.min(abs(loop$dist-x)),]$dist
  
  y = loop$dist[i] + 5
  loop$ele_plus[i] <- loop[which.min(abs(loop$dist-y)),]$ele_fit
  loop$dist_plus[i] <- loop[which.min(abs(loop$dist-y)),]$dist
  
  loop$slope <- (loop$ele_minus-loop$ele_plus)/(loop$dist_minus-loop$dist_plus)
  
}
loop$dist_minus <- NULL
loop$dist_plus <- NULL
loop$ele_minus <- NULL
loop$ele_plus <- NULL

df_prediction <- loop 


```

```{r calc ante slope, echo=FALSE}

###
df_prediction <- df_prediction[order(df_prediction$dist),]
df_prediction$slope50m <- NA
loop <- df_prediction%>%drop_na(ele_fit)
for(i in 1:nrow(loop)) {       # for-loop over rows
  x = loop$dist[i] - 50
  loop$ele_minus[i] <- loop[which.min(abs(loop$dist-x)),]$ele_fit
  loop$dist_minus[i] <- loop[which.min(abs(loop$dist-x)),]$dist
  
  y = loop$dist[i] + 3
  loop$ele_plus[i] <- loop[which.min(abs(loop$dist-y)),]$ele_fit
  loop$dist_plus[i] <- loop[which.min(abs(loop$dist-y)),]$dist
  
  loop$slope50m <- (loop$ele_minus-loop$ele_plus)/(loop$dist_minus-loop$dist_plus)
  
}
loop$dist_minus <- NULL
loop$dist_plus <- NULL
loop$ele_minus <- NULL
loop$ele_plus <- NULL

df_prediction <- loop 

```

```{r plot final predict, echo=FALSE}
ggplot(data=df_prediction, aes(dist, ele_fit, color=log10(CO2_ppm_ave)),size=5) +
  geom_point(size=5)

ggplot(data=df_prediction%>%drop_na(Flux_ave), aes(dist, ele_fit, color=log10(CO2_ppm_ave)),size=5) + geom_point(size=5)
ggplot(data=df_prediction%>%drop_na(Flux_ave), aes(dist, ele_fit, color=log10(adjusted_ppm))) +
  geom_point(size=5)
ggplot(data=df_prediction %>%drop_na(Flux_ave), aes(dist, ele_fit, color=Flux_ave)) +
  geom_point(size=5)

#ggplot(data=df_prediction, aes(dist, ele_fit, col="CO2_ppm_ave")) +
 # geom_point(size = 3, alpha = .5, color = "blue")

#fig <- plot_ly(df_prediction, x = ~dist, y = ~ele_fit, size = 1)
#fig
```


##write it out

```{r write, echo=FALSE}
#df_prediction$DOC <- NULL
#df_prediction$TDN <- NULL


write.csv(df_prediction, here::here("ProcessedData/ANTE_synoptic_2022-03-23.csv"))

df_prediction_join <- df_prediction[,c("lon_fit","lat_fit","dist","ele_fit","Date")]

WaterChem2 <- left_join(WaterChem,df_prediction_join,by=c("lon_fit","lat_fit"))
WaterChem2 <- unique(WaterChem2)%>%drop_na(DOC)

write.csv(WaterChem2, here::here("ProcessedData/ANTE_WaterChem_synop_2022-03-23.csv"))

```




i said plot it!
```{r plot that fucker, echo=FALSE}



fit <- loess(ele ~ dist, degree=2, span = 0.30, data=df_prediction)

df_prediction %>% 
  drop_na(Flux_ave) %>%
  mutate(smooth = fit$fitted) %>%
  ggplot(aes(dist, ele_fit, color = CO2_ppm_ave)) +
  geom_point(size = 3, alpha = .5) +
  scale_color_continuous(low="thistle2", high="darkred", 
                       guide="colorbar",na.value="") +
  geom_line(aes(dist, smooth), color="blue")



df_prediction %>% 
  drop_na(Flux_ave) %>%
  mutate(smooth = fit$fitted) %>%
  ggplot(aes(dist, ele_fit, color = Flux_ave)) +
  geom_point(size = 3, alpha = .5) +
  scale_color_continuous(low="green", high="darkred", 
                       guide="colorbar",na.value="") +
  geom_line(aes(dist, smooth), color="blue")


#ggplot(data=df_prediction%>%drop_na(Flux_ave), aes(dist, ele_fit, color=CO2_ppm_ave)) +
#  geom_point()



```
