---
title: "ANTE_moreGeomorph_2022-02-16"
author: "Kriddie"
date: "2/16/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(plotly)
library(dplyr)
library(tidyr)
library(zoo)
library(plot3D)
library(splines)
library(Ecdat)
library(dplyr)
library(sp)
library(geosphere)
library(DescTools)
library(data.table)
```

##Geomorph Data
make a another  data frame with rest of the geomorphdata - width, depth, and some notes relating to wetland/waterfall stuff

Start by reading in most recent synoptic data

```{r add function}
##arrange df vars by position
##'vars' must be a named vector, e.g. c("var.name"=1)
arrange.vars <- function(data, vars){
    ##stop if not a data.frame (but should work for matrices as well)
    stopifnot(is.data.frame(data))

    ##sort out inputs
    data.nms <- names(data)
    var.nr <- length(data.nms)
    var.nms <- names(vars)
    var.pos <- vars
    ##sanity checks
    stopifnot( !any(duplicated(var.nms)), 
               !any(duplicated(var.pos)) )
    stopifnot( is.character(var.nms), 
               is.numeric(var.pos) )
    stopifnot( all(var.nms %in% data.nms) )
    stopifnot( all(var.pos > 0), 
               all(var.pos <= var.nr) )

    ##prepare output
    out.vec <- character(var.nr)
    out.vec[var.pos] <- var.nms
    out.vec[-var.pos] <- data.nms[ !(data.nms %in% var.nms) ]
    stopifnot( length(out.vec)==var.nr )

    ##re-arrange vars by position
    data <- data[ , out.vec]
    return(data)
}
```

```{r read in data}
#df_prediction <- read.csv(here::here("ProcessedData/COLMILLO_synoptic_2022-03-24.csv"))
#df_prediction <- read.csv(here::here("ProcessedData/COLMILLO_synoptic_2022-04-19.csv"))
df_prediction <- read.csv(here::here("ProcessedData/COLMILLO_synoptic_2022-06-04.csv"))
df_prediction$X <- NULL
df_prediction$lat <- NULL
df_prediction$lon_dist <- NULL
df_prediction$lat_dist <- NULL
df_prediction$lon <- NULL
df_prediction$ele <- NULL
df_prediction$time <- NULL

df_prediction <- unique(df_prediction)
df_prediction <- df_prediction%>%filter(dist_diff>0)

ggplot(data=df_prediction, aes(dist, ele_fit, color=log10(CO2_ppm_ave)),size=5) +
  geom_point(size=5)

ggplot(data=df_prediction, aes(lon_fit, lat_fit, color=log10(CO2_ppm_ave)),size=5) +
  geom_point(size=5)
```
#read in x, w, d data frame

```{r x and w and d, echo=FALSE}
XWD <- read.csv(here::here("Geomorphology/Colmillo/COLM_geomorph_2022-01-28.csv"))

XWD <- XWD[,c("lon","lat","x","d","w","ele","notes")]

#oh what rotten luck. XWD data was collected downstream to upstream and df_prediction is opposite. Let use right this wrong
#also the distances are all messed up because of the gavi wetland, so we will reverse order one at a time

XWD <- XWD[order(XWD$x),]
XWD$x_diff <- NA

for(i in 1:nrow(XWD)) {       # for-loop over rows
  if (i == 1) {
    XWD$x_diff[i] <- 0
  } else {
    XWD[i,"x_diff"] <-   XWD[i,"x"] - XWD[i-1,"x"]
  }
}
XWD <- XWD[order(-XWD$x),]
XWD$x_new <- NA
for(i in 1:nrow(XWD)) {       # for-loop over rows
  if (i == 1) {
    XWD$x_new[i] <- 0
  } else {
    XWD[i,"x_new"] <-   XWD[i-1,"x_diff"] + XWD[i-1,"x_new"]
  }
}

#great. now get rid of the stuff you don't want
XWD <- XWD[,c("lon","lat","x_new","d","w","ele","notes")]
names(XWD)[names(XWD) == 'x_new'] <- 'x'


```

now we snap XWD data to prediction

```{r snap XDW, echo=FALSE}
df_prediction <- arrange.vars(df_prediction, c("lon_fit"=1))
#seeing some problems around GAVI wetland. Distance don't match up. So we will restart distance 

XWD_1 <- XWD %>%drop_na(lon)
#XWD_2 <- XWD
#XWD_2$x[which(XWD_2$x>1043)] <- XWD_2$x[which(XWD_2$x>1043)] - (1045 - 507.6455874)

x <- SpatialPoints(XWD_1[,c(1:2)])
y <- SpatialPoints(df_prediction[,c(1:2)]) 
plot(x, col = "red")
points(y, col = "green")
snap = apply(spDists(x, y), 1, which.min)
points(y[snap,], pch = 3)


snap_df <- y[snap,]
coords_df <- snap_df@coords
pred <- as.data.frame(coords_df)
XWD_1$lon_fit <- pred$lon
XWD_1$lat_fit <- pred$lat
XWD_1 <- full_join(XWD[,c("x","d","w","notes")],XWD_1[,c("lon_fit","lat_fit","x","d","w","notes")],by=c("x","d","w","notes"))

df_prediction_1 <- full_join(df_prediction,XWD_1,by=c("lon_fit","lat_fit"))
#df_prediction_1 <- df_prediction_1%>%drop_na(x) 
df_prediction_1 <- df_prediction_1[,c("lon_fit","lat_fit","dist","x","d","w","notes")]
df_prediction_1 <- unique(df_prediction_1)

```
We've snapped in the waypoints collected while sampling x/width/depth, but there are many points in between don't have corresponding lat/lon/ele. So how to fix these gaps?


Our tools are dist (modeled) and x (measured). Some x are already associated with dist we need to associate all xs with distance. 

If we can identify the xs assiciated with distance, we can then calcualte the difference between each each one. Then calcualte the ratio of x inbetween and total difference


##do this:
if pt1 and pt2 are known values of x, and pt-btw is known dist but unknown x, then:

(Dist[pt-btw] - Dist[pt1])/(Dist[pt2] - Dist[pt1]) = (unknown - x[pt1])/(x[pt2] - x[pt1])

unknown = (Dist[pt-btw] - Dist[pt1])/(Dist[pt2] - Dist[pt1])*(x[pt2] - x[pt1]) + x[pt1]

##but how do that in a loop?
key to this is being able idntify the next known x in between NAs.

the code below realtes x as measured in the field to distance as calculated with way points. The ancors are waypoints collected every 50 meters in the field 

```{r dist and x, echo=FALSE}
df_prediction_1$notes <- NULL
df_prediction_1$dist_pred <- NULL
df_prediction_1$x_pred <- NULL

df_prediction_1 <- df_prediction_1[order(df_prediction_1$dist),]
pred_df <- na.omit(df_prediction_1[,c("x","dist")])


for(i in 1:nrow(df_prediction_1)) {       # for-loop over rows
  if (is.na(df_prediction_1[i,"x"]) == FALSE) {
    df_prediction_1$x_pred[i] <- df_prediction_1$x[i]

  } else {
    pt2btw <- df_prediction_1$dist[i]
    dist1 = Closest(pred_df$dist, pt2btw, which = FALSE, na.rm = FALSE)
    if (dist1 < pt2btw ) {#x[! x %in% 2:10]
    dist2 = Closest(pred_df$dist[pred_df$dist > dist1], pt2btw, which = FALSE, na.rm = FALSE)}
    else{
      dist2 = Closest(pred_df$dist[pred_df$dist < dist1], pt2btw, which = FALSE, na.rm = FALSE)
    }
    pt1dist = min(dist1,dist2)
    pt2dist = max(dist1,dist2)
    
    pt1x = pred_df$x[which(pred_df$dist == pt1dist)]
    pt2x = pred_df$x[which(pred_df$dist == pt2dist)]
    df_prediction_1$x_pred[i] <- pt2x - (pt2dist-df_prediction_1$dist[i])/(pt2dist-pt1dist)*(pt2x-pt1x)
  }
}
```

Now we have a data frame with x predicted and associated with distance. Now we associate the closest actual x measurments, depth and width with the predicted x  



```{r width loop, echo=FALSE}
df_prediction_2 <- df_prediction_1[,c("lon_fit","lat_fit","dist","x_pred")]%>%drop_na(dist)

XWD_fit <- XWD_1[,c("x","w","d","notes")]
colnames(XWD_fit) <- c("x_pred","w","d","notes")

setDT(df_prediction_2)
setDT(XWD_fit)

df_prediction_3 <- df_prediction_2[XWD_fit, roll = "nearest", on = "x_pred"]

# now we calculate surface area of each width measurment using trapazoid method


df <- df_prediction_3%>%drop_na(w)
df$midpoint <- NA
df$length <- NA
df$area <- NA

#run this 2x for some reason (but no more than 2x!) make sure area column is filled in and reasonable

for(i in 1:nrow(df)) {       # for-loop over rows
  if (i==1) {
    df$midpoint[i] <- 0
    df$length[i] <- (df$dist[i+1] + (df$dist[i] - df$dist[i+1])/2) - 0
    df$area[i] <- df$length[i] * df$w[i]/100
    
  } else {
    df$midpoint[i] <- df$dist[i-1] + (df$dist[i] - df$dist[i-1])/2
    df$length[i-1] <- df$midpoint[i] - df$midpoint[i-1]
    df$area[i] <- df$length[i] * df$w[i]/100
  }
}

##
for(i in 1:nrow(df)) {       # for-loop over rows
  if (i==1) {
    df$midpoint[i] <- 0
    df$length[i] <- (df$dist[i+1] + (df$dist[i] - df$dist[i+1])/2) - 0
    df$area[i] <- df$length[i] * df$w[i]/100
    
  } else {
    df$midpoint[i] <- df$dist[i-1] + (df$dist[i] - df$dist[i-1])/2
    df$length[i-1] <- df$midpoint[i] - df$midpoint[i-1]
    df$area[i] <- df$length[i] * df$w[i]/100
  }
}

##

df_prediction_3 <- df

```

AHHHH i can't believe that wooooorrrrkkkkeedddddddddddd!!!!!!


So now we need to associate this data frame with actual measurments from the synoptic data

we need to get synop data back in here. deep breath. here we go

```{r synop, echo=FALSE}

##find midpoint distance between synop measurments. Then add up all areas that fall between way points
synop <- df_prediction[,c("lon_fit","lat_fit","dist","Flux_ave")]%>%drop_na(Flux_ave)
synop <- synop[order(synop$dist),]

for(i in 1:nrow(synop)) {       # for-loop over rows
  if (i==50) {
        synop$midpoint[i] <- 0
  } else {
synop$midpoint[i] <- (synop$dist[i+1] - synop$dist[i])/2 + synop$dist[i]
  }
}

## now we add up all of 

#
synop <- synop[order(synop$dist),]

synop$surface_area <- NULL

for(i in 1:nrow(synop)) { 
  if (i==1){
      synop$surface_area[i] <- sum(df_prediction_3$area[ df_prediction_3$dist < synop$midpoint[i]], na.rm = TRUE)
  }else if (i==which(synop$dist==max(synop$dist))){
       synop$surface_area[i] <- sum(df_prediction_3$area[ df_prediction_3$dist > synop$midpoint[i-1]], na.rm = TRUE)
      }
  else{
  synop$surface_area[i] <- sum(df_prediction_3$area[df_prediction_3$dist > synop$midpoint[i-1] & df_prediction_3$dist < synop$midpoint[i]], na.rm = TRUE)
  }
}

synop$flux_umolpers <- synop$Flux_ave*synop$surface_area
#synop <- synop[,-c(3,4,6:12)]



synop <- synop%>%drop_na(flux_umolpers)
synop <- synop[order(synop$dist),]

for(i in 1:nrow(synop)) {       # for-loop over rows
    if (i == 1) {
      synop$Totalflux_umolpers[i] <- synop$flux_umolpers[1]
    } else {
      synop[i,"Totalflux_umolpers"] <- synop[i-1,"Totalflux_umolpers"] + synop[i,"flux_umolpers"]
    }
  }
  

df_prediction_4 <- left_join(df_prediction,synop[,c("lon_fit","lat_fit","dist","Flux_ave","midpoint","surface_area","flux_umolpers","Totalflux_umolpers")], by=c("lon_fit","lat_fit","dist","Flux_ave"))



```

I guess what I want is a column associated with each CO2 measurment that gives me surface area associated with the measurment.

I now have some cra


```{r plot and write, echo=FALSE}
#df_prediction_4$flux_umolpers
ggplot(data=df_prediction_4, aes(dist, Totalflux_umolpers),size=5) +
  geom_point(size=5)

write.csv(df_prediction_4, here::here("ProcessedData/COLM_synopticGeom_2022-06-07.csv"))

```