---
title: "Geomorphology_GAVI-UP"
author: "KWhitmore"
date: "09/03/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(lubridate)
library(plotly)
library(dplyr)
library(tidyr)
library(zoo)
library(splines)
library(Ecdat)
library(dplyr)
library(sp)
library(geosphere)
library(ggmap)
library(data.table)
library(MALDIquant)


#funtion
#what does this function do?

##arrange df vars by position
##'vars' must be a named vector, e.g. c("var.name"=1)
arrange.vars <- function(data, vars){
    ##stop if not a data.frame (but should work for matrices as well)
    stopifnot(is.data.frame(data))

    ##sort out inputs
    data.nms <- names(data)
    var.nr <- length(data.nms)
    var.nms <- names(vars)
    var.pos <- vars
    ##sanity checks
    stopifnot( !any(duplicated(var.nms)), 
               !any(duplicated(var.pos)) )
    stopifnot( is.character(var.nms), 
               is.numeric(var.pos) )
    stopifnot( all(var.nms %in% data.nms) )
    stopifnot( all(var.pos > 0), 
               all(var.pos <= var.nr) )

    ##prepare output
    out.vec <- character(var.nr)
    out.vec[var.pos] <- var.nms
    out.vec[-var.pos] <- data.nms[ !(data.nms %in% var.nms) ]
    stopifnot( length(out.vec)==var.nr )

    ##re-arrange vars by position
    data <- data[ , out.vec]
    return(data)
}
```
## BUild the geomorphology data frame for GAVI upstream of peatland

2021-07-26 9:50
```{r build df 2021-12-18}


Geomorph <- read.csv(here::here("Geomorphology/Gavilan/GAVI_Dec2021.csv"), skip = 70)
Geomorph <- Geomorph[,3:6]

#convert time in UTC to local time
Geomorph$time <- gsub("T"," ", Geomorph$time)
Geomorph$time <- gsub("Z","", Geomorph$time)

Geomorph$time <- as.POSIXct(Geomorph$time, format = "%Y-%m-%d %H:%M:%S", tz = "UTC" )
Geomorph$time <-Geomorph$time - 5*60*60 
#round to nearest half second
Geomorph$time <- round_date(Geomorph$time, unit = "30 second")

# 2021-12-18 START: 10:33:00  

#downstream to outlet 11:39
Geomorph_1 <- subset(Geomorph,
      time > as.POSIXct('2021-12-18 10:33:00', tz="UTC") & time < as.POSIXct('2021-12-18 11:39:00', tz="UTC"))
#start at GAVI inlet
Geomorph_2 <- subset(Geomorph,
      time > as.POSIXct('2021-12-18 11:53:00', tz="UTC") & time < as.POSIXct('2021-12-18 13:15:00', tz="UTC"))

Geomorph <- rbind(Geomorph_1,Geomorph_2)

#just downstream of gavi
Geomorph <- Geomorph %>% filter(lat > -.328)


```

It's not a bad thing, per se, but I really made things complicated when I started taking measurmenets of streams in addition to the mainstem of GAVI. I blame Diego, frankly. But I also blame myself from listening to Diego. Have confidence in you're game plan, Kriddie, for goodness Sake.

So let's try to just select the mainstem samples, for starters.

```{r add synop to df}
#synop <- read.csv(here::here("Synoptic/GAVI.csv"))
#synop <- read.csv(here::here("Synoptic/GAVI_2022-01-27.csv"))
#synop <- read.csv(here::here("Synoptic/GAVI_2022-03-24.csv"))
#synop <- read.csv(here::here("Synoptic/GAVI_2022-04-19.csv"))
synop <- read.csv(here::here("Synoptic/GAVI_2022-06-04.csv"))

synop$X <- NULL

colnames(synop) <- c("lon","lat","Date","EOS_no","Flux_ave", "Tract","Point","VaisalaType","CO2_ppm_ave","WaterTemp_c","BaroPress_kpa","AirTemp_c","Total_hPa","adjusted_ppm","DateTime","SampleID", "DOC","TDN","ID","Notes")
synop <- synop[,c("lat","lon","Date","DateTime","EOS_no","Flux_ave", "Tract","Point","VaisalaType","CO2_ppm_ave","WaterTemp_c","BaroPress_kpa","AirTemp_c","Total_hPa","adjusted_ppm","DOC","TDN")]

Synopjune18 <- synop %>% filter(Date == "2021-06-18")
Synopjune22 <- synop %>% filter(Date == "2021-06-22" & EOS_no == "EOS1" & Tract == 1)
Synopjune29 <- synop %>% filter(Date == "2021-06-29" & EOS_no == "EOS2" & Tract == 7)
Synopjune30 <- synop %>% filter(Date == "2021-06-30" & EOS_no == "EOS2")

synop_mainstem <- rbind(#Synopjune18,Synopjune22,
                        Synopjune29,Synopjune30
                        )
rm(Synopjune18,Synopjune22,Synopjune29,Synopjune30)
```



##Plot the geomorphology data in 3-d

```{r 3d plot no synop, echo=FALSE}


fig <- plot_ly(Geomorph, x = ~lat, y = ~lon, z = ~ele, size = 1
)
fig <- fig %>% add_markers()
#fig <- fig %>% add_trace(x = ~lat, y = ~lon, z = ~ele, #color = ~EOS_no#, colors = c('Blue','Yellow'),
#                         mode = 'markers')
fig <- fig %>% layout(scene = list(xaxis = list(title = 'lat'), yaxis = list(title = 'lon'), zaxis = list(title = 'elevation')))

fig


```

## Now Plot data in 3D including synoptic points


```{r 3d plot and synop, echo=FALSE}

df <- full_join(synop_mainstem,Geomorph, by=c("lat","lon")) 


fig <- plot_ly(df, x = ~lat, y = ~lon, z = ~ele, size = 1,
               marker = list(color = ~CO2_ppm_ave, colorscale = c('#FFE1A1', '#683531'), showscale = TRUE))

#FFE1A1 #683531

fig <- fig %>% add_markers()
#fig <- fig %>% add_trace(x = ~lat, y = ~lon, z = ~ele, #color = ~EOS_no#, colors = c('Blue','Yellow'),
#                         mode = 'markers')
fig <- fig %>% layout(scene = list(xaxis = list(title = 'lat'),yaxis = list(title = 'lon'),zaxis = list(title = 'elevation')))

fig

```
#are you seeing the problem? 
This is worse then both Colmillo and Antenas. below the main wetland its not so bad, but above is kinda a mess. I think I should re-do this when I am back at the site, but for now, let us proceed.

#working with 3-D is hard.
In this code chunk, we start by smooting a line to the lat lon data, which appears to be more accurate than the elevation

We will do this in parts though, be cause the relationship between lat lon can not be described as a function


```{r upstream of gavi spline, echo=FALSE}

#Cut up lat long into peices, and then fit spline

model <- lm(lon~bs(lat, degree = 10), data=Geomorph)

latlims <- range(Geomorph$lat)
lat.grid <- seq(from=latlims[1],to=latlims[2], by=.000001)
pred <-predict(model,newdata=list(lat=lat.grid),se=T)

plot(Geomorph$lat,Geomorph$lon,main="regressionSplinePLot")
lines(lat.grid,pred$fit,col='red',lwd=3)

fig<-plot_ly(data = Geomorph, x = ~lat, y = ~lon)

#this looks pretty good! So we will save the data in a data frame

lat <- lat.grid
lon <- pred$fit
df2<-as.data.frame(lat)
df2$lon <- lon
df2$num <- '2'
```


```{r bind dataframes, echo=FALSE}

#now we need to make a dataframe that discribes this relationship between lat lon
df_prediction <- df2


plot(df_prediction$lon~df_prediction$lat,col=df_prediction$num)


```

now we have a smooth data frame of lat/lon data, we calculate the distance between each point

```{r calc dist}

###create a loop and calculate distance along the river from the predict_df. Then we can bind in the GEOMORPH!
df_prediction <- df2 %>% drop_na(lat)
df_prediction$num <- NULL

colnames(df_prediction) <- c("lat_fit","lon_fit")
df_prediction$lon_dist <- NA
df_prediction$lat_dist <- NA
i <- 2
for(i in 1:nrow(df_prediction)) {
  if (i == 1) {

      df_prediction$dist <- 0
      
    } else {
      df_prediction[i,"lon_dist"] <- df_prediction[i-1,"lon_fit"]
      df_prediction[i,"lat_dist"] <- df_prediction[i-1,"lat_fit"]
      df_prediction[i,"dist"] <- df_prediction[i-1,"dist"] + distHaversine(
        c(df_prediction[i,"lon_fit"], df_prediction[i,"lat_fit"]), 
        c(df_prediction[i,"lon_dist"], df_prediction[i,"lat_dist"]))
      }
}
```

snap the points in our origional dama frame to bring in the elevation data


```{r snap points to lat lon}

x <- SpatialPoints(Geomorph[,c(1:2)])
y <- SpatialPoints(df_prediction[,c(1:2)]) 
plot(y, col = "red")
points(y, col = "green")
snap = apply(spDists(x, y), 1, which.min)
points(y[snap,], pch = 3)


snap_df <- y[snap,]
coords_df <- snap_df@coords
pred <- as.data.frame(coords_df)
Geomorph$lon_fit <- pred$lon
Geomorph$lat_fit <- pred$lat


df_prediction <- full_join(df_prediction,Geomorph,by=c("lon_fit","lat_fit"))

```
first I need to make sure that what I have done really worked

```{r testing snap to line, echo=FALSE}


fig <- plot_ly(Geomorph, x = ~lat, y = ~lon, z = ~ele, size = 1)
fig <- fig %>% add_markers()
fig <- fig %>% add_trace(x = ~lat_fit, y = ~lon_fit, z = ~ele, colors = c('Yellow'),
                         mode = 'markers')
fig <- fig %>% layout(scene = list(xaxis = list(title = 'lat'),
                                   yaxis = list(title = 'lon'),
                                   zaxis = list(title = 'elevation')))

fig


```

ok sweet that looks really good

We also need to snap the synoptic df (for later)
```{r snap synop pts}

x <- SpatialPoints(synop_mainstem[,c(1:2)])
y <- SpatialPoints(df_prediction[,c(1:2)]) 
plot(x, col = "red")
points(y, col = "green")
snap = apply(spDists(x, y), 1, which.min)
points(y[snap,], pch = 3)


snap_df <- y[snap,]
coords_df <- snap_df@coords
pred <- as.data.frame(coords_df)
synop_mainstem$lon_fit <- pred$lon
synop_mainstem$lat_fit <- pred$lat

synop_mainstem <- synop_mainstem[,c("lon_fit","lat_fit","Date","EOS_no","Flux_ave","Point","VaisalaType","CO2_ppm_ave","WaterTemp_c","BaroPress_kpa","AirTemp_c","Total_hPa","adjusted_ppm","DOC","TDN")]


df_prediction <- full_join(df_prediction,synop_mainstem,by=c("lon_fit","lat_fit"))
check <- df_prediction%>%drop_na(Date)


```



##calculate distance between each coordinate.
Here's the deal. We need to calcualte the distance between each coordinate 

First, lets find the most western lat point



now we have created a distance column that we can plot the elevation data against. lets see how that looks

```{r plot dist v ele, echo = FALSE}
fig <- plot_ly(df_prediction, x = ~dist, y = ~ele, size = 1)
fig
```


I think it would be better if we did two different prediction above and below gavi


##loess spline
i think loess might be a little better for this? IT IS NOT
But maybe just because data is not great. please revisit

ok i did revisit, and I think this is better now


```{r diff 1 way}

distlims <- range(df_prediction$dist)
fit <- loess(ele ~ dist, degree=2, span = 0.20, data=df_prediction)
pred1 <- predict(fit, data.frame(dist = df_prediction$dist), se = TRUE)
df_prediction$ele_fit <- pred1$fit

df_prediction %>% 
  drop_na(ele) %>%
  mutate(smooth = fit$fitted) %>%
  ggplot(aes(dist, ele)) +
  geom_point(size = 3, alpha = .5, color = "grey") +
  geom_line(aes(dist, smooth), color="red")

fig <- plot_ly(df_prediction, x = ~dist, y = ~ele_fit, size = 1)
fig

check <- df_prediction%>%drop_na(Date)


```

There really no point in adding slope this way. so let's skip


#reverse order
unfortunately gavi is going from downstream to up, and we want upstream to down. so reverse this order
you can't just reverse order the distance column because they are not collected at even intervals.

#loops below switch order of distance


```{r reverse, echo=FALSE}

df_prediction <- df_prediction[order(df_prediction$dist),]
df_prediction$dist_diff <- NA

for(i in 1:nrow(df_prediction)) {       # for-loop over rows
  if (i == 1) {
    df_prediction$dist_diff[i] <- max(df_prediction$dist)
  } else {
    df_prediction$dist_diff[i] <-   max(df_prediction$dist) - df_prediction[i,"dist"]
  }
}

ggplot(data=df_prediction%>%drop_na(Date), aes(dist_diff, ele_fit, color=log10(CO2_ppm_ave)),size=5) +
  geom_point(size=5)

ggplot(data=df_prediction%>%drop_na(Date), aes(lon_fit, lat_fit, color=log10(CO2_ppm_ave)),size=5) +
  geom_point(size=5)


```

#read out
I'm really hoping this finaly product looks good


```{r write, echo=FALSE}
df_prediction <- df_prediction%>%select(lat_fit,lon_fit,ele_fit,dist_diff,Date,Point,Flux_ave,CO2_ppm_ave,adjusted_ppm,DOC,TDN,WaterTemp_c,BaroPress_kpa,AirTemp_c,Total_hPa,VaisalaType,EOS_no)%>%rename(dist=dist_diff)
df_prediction <- unique(df_prediction)

##check should have 23 synop points 
check <- df_prediction%>%drop_na(Date)

#write.csv(df_prediction, here::here("ProcessedData/GAVI_UP_synoptic_2024-09-03.csv"))
#write.csv(check, here::here("ProcessedData/GAVI_UP_synopticpoints_arcpro_2024-09-03.csv"))

```

##now we add in width and depth data

#read in x, w, d data frame
and also df_prediction for trouble shooting purposes

```{r x and w and d, echo=FALSE}

df_prediction <- read.csv(here::here("ProcessedData/GAVI_UP_synoptic_2024-09-03.csv"))
df_prediction$X <- NULL

XWD <- read.csv(here::here("Geomorphology/Gavilan/GAVI-UPmainstem_Geomorph_2024-09-04.csv"))
XWD <- XWD%>%select(lon,lat,x_new,d,w,ele,notes)%>%rename(x=x_new)

XWD_save <- XWD[order(XWD$x),]

```

now we snap XWD data to prediction

```{r snap XDW, echo=FALSE}

df_prediction_arrange <- arrange.vars(df_prediction, c("lon_fit"=1))

XWD_1 <- XWD_save %>%drop_na(lon)
XWD_2 <- XWD_save

x <- SpatialPoints(XWD_1[,c(1:2)])
y <- SpatialPoints(df_prediction_arrange[,c(1:2)]) 
plot(x, col = "red")
points(y, col = "green")
snap = apply(spDists(x, y), 1, which.min)
points(y[snap,], pch = 3)

snap_df <- y[snap,]
coords_df <- snap_df@coords
pred <- as.data.frame(coords_df)
XWD_1$lon_fit <- pred$lon
XWD_1$lat_fit <- pred$lat

XWD_1 <- full_join(XWD[,c("x","d","w","notes")],XWD_1[,c("lon_fit","lat_fit","x","d","w","notes")],by=c("x","d","w","notes"))

df_prediction_1 <- full_join(df_prediction_arrange,XWD_1,by=c("lon_fit","lat_fit"))
#df_prediction_1 <- df_prediction_1%>%drop_na(x) 
df_prediction_1 <- df_prediction_1[,c("lon_fit","lat_fit","dist","x","d","w","notes")]
df_prediction_1 <- unique(df_prediction_1)

# there is a point with no associated x, and it causes probelms later

df_prediction_1 <- df_prediction_1%>%filter(notes!="starting at large stream upsteam of last measurement (I think?)")

saveit <- df_prediction_1
```

We've snapped in the waypoints collected while sampling x/width/depth, but there are many points in between don't have corresponding lat/lon/ele. So how to fix these gaps?


Our tools are dist (modeled) and x (measured). Some x are already associated with dist we need to associate all xs with distance. 

If we can identify the xs assiciated with distance, we can then calcualte the difference between each each one. Then calcualte the ratio of x inbetween and total difference


##do this:
if pt1 and pt2 are known values of x, and pt-btw is known dist but unknown x, then:

(Dist[pt-btw] - Dist[pt1])/(Dist[pt2] - Dist[pt1]) = (unknown - x[pt1])/(x[pt2] - x[pt1])

unknown = (Dist[pt-btw] - Dist[pt1])/(Dist[pt2] - Dist[pt1])*(x[pt2] - x[pt1]) + x[pt1]

##but how do that in a loop?
key to this is being able idntify the next known x in between NAs.

the code below realtes x as measured in the field to distance as calculated with way points. The ancors are waypoints collected every 50 meters in the field 

```{r dist and x, echo=FALSE}
df_prediction_1 <- saveit

df_prediction_1 <- df_prediction_1[order(df_prediction_1$x),]
pred_df <- na.omit(df_prediction_1[,c("x","dist")])


for(i in 1:nrow(df_prediction_1)) {       # for-loop over rows
  pred_df <- na.omit(df_prediction_1[,c("x","dist")])
  
  if (is.na(df_prediction_1[i,"dist"]) == FALSE) {
    df_prediction_1$x_pred[i] <- df_prediction_1$dist[i]

  } else if (is.na(df_prediction_1[i,"dist"]) == TRUE) { 
    #i want to select the two "x" values that are the closest to the x[i] and have associated distance measurements
    #first select closest x and associated dist
    index <- match.closest(df_prediction_1$x[i], pred_df$x,tolerance='Inf')
    dist1 <- pred_df$dist[index]
    x1 <- pred_df$x[index]
    #now find the second closest number - well no. I don't want the second closest. I want the number on the other side. so I don't want to just remove the first x value, I want to remove that value and everythign above or everythign below that value -- depending on weather it is higher or lower
    if (x1 < df_prediction_1$x[i]) {
    pred_df_closestremoved <- pred_df%>%filter(x > df_prediction_1$x[i])
    index <- match.closest(df_prediction_1$x[i], pred_df_closestremoved$x,tolerance='Inf')
    dist2 <- pred_df_closestremoved$dist[index]
    x2 <- pred_df_closestremoved$x[index]
    } else {
    pred_df_closestremoved <- pred_df%>%filter(x < df_prediction_1$x[i])
    index <- match.closest(df_prediction_1$x[i], pred_df_closestremoved$x,tolerance='Inf')
    dist2 <- pred_df_closestremoved$dist[index]
    x2 <- pred_df_closestremoved$x[index]
    }
        #sort out max and mins 
    dist_min = min(dist1,dist2)
    dist_max = max(dist1,dist2)
    x_min = min(x1,x2)
    x_max = max(x1,x2)
    
    df_prediction_1$x_pred[i] <- (df_prediction_1$x[i]-x_min)/(x_max-x_min) * (dist_max-dist_min) + dist_min
    
  }
}
```

Now we have a data frame with x predicted and associated with distance. Now we associate the closest actual x measurments, depth and width with the predicted x  


```{r width loop, echo=FALSE}

latlon_df <- df_prediction%>%select(lat_fit,lon_fit,ele_fit,dist,Flux_ave,adjusted_ppm,DOC,TDN)%>%rename(x_pred=dist)
XWD_df <- df_prediction_1

setDT(latlon_df)
setDT(XWD_df)

#XWD_fit <- XWD_1[,c("x","w","d","notes")]
#colnames(XWD_fit) <- c("x_pred","w","d","notes")

#setDT(df_prediction_2)
#setDT(XWD_fit)

df_prediction_4 <- latlon_df[XWD_df, roll = "nearest", on = "x_pred"]

df_prediction_5 <- df_prediction_4%>%select(lat_fit,lon_fit,ele_fit,x_pred,x,d,w,Flux_ave,adjusted_ppm,DOC,TDN,notes)

#write.csv(df_prediction_5, here::here("ProcessedData/GaviUP_XWD.csv"))

```

#trapazoid method 


```{r trap method, echo=FALSE}
# now we calculate surface area of each width measurment using trapazoid method


df <- df_prediction_3%>%drop_na(w)
df$midpoint <- NA
df$length <- NA
df$area <- NA

#run this 2x for some reason (but no more than 2x!) make sure area column is filled in and reasonable

for(i in 1:nrow(df)) {       # for-loop over rows
  if (i==1) {
    df$midpoint[i] <- 0
    df$length[i] <- (df$dist[i+1] + (df$dist[i] - df$dist[i+1])/2) - 0
    df$area[i] <- df$length[i] * df$w[i]/100
  } else {
    df$midpoint[i] <- df$dist[i-1] + (df$dist[i] - df$dist[i-1])/2
    df$length[i-1] <- df$midpoint[i] - df$midpoint[i-1]
    df$area[i] <- df$length[i] * df$w[i]/100
  }
}

for(i in 1:nrow(df)) {       # for-loop over rows
  if (i==1) {
    df$midpoint[i] <- 0
    df$length[i] <- (df$dist[i+1] + (df$dist[i] - df$dist[i+1])/2) - 0
    df$area[i] <- df$length[i] * df$w[i]/100
  } else {
    df$midpoint[i] <- df$dist[i-1] + (df$dist[i] - df$dist[i-1])/2
    df$length[i-1] <- df$midpoint[i] - df$midpoint[i-1]
    df$area[i] <- df$length[i] * df$w[i]/100
  }
}

df_prediction_3 <- df

#write.csv(df_prediction_3, here::here("ProcessedData/Gavi_XWD_2.csv"))

```

AHHHH i can't believe that wooooorrrrkkkkeedddddddddddd!!!!!!


So now we need to associate this data frame with actual measurments from the synoptic data

we need to get synop data back in here. deep breath. here we go

```{r synop, echo=FALSE}

##find midpoint distance between synop measurments. Then add up all areas that fall between way points
synop <- df_prediction[,c("lon_fit","lat_fit","dist","Flux_ave")]%>%drop_na(Flux_ave)
synop <- synop[order(synop$dist),]

for(i in 1:nrow(synop)) {       # for-loop over rows
  if (i==50) {
        synop$midpoint[i] <- 0
  } else {
synop$midpoint[i] <- (synop$dist[i+1] - synop$dist[i])/2 + synop$dist[i]
  }
}

## now we add up all of 

#
synop <- synop[order(synop$dist),]

synop$surface_area <- NULL

for(i in 1:nrow(synop)) { 
  if (i==1){
      synop$surface_area[i] <- sum(df_prediction_3$area[ df_prediction_3$dist < synop$midpoint[i]], na.rm = TRUE)
  }else if (i==which(synop$dist==max(synop$dist))){
       synop$surface_area[i] <- sum(df_prediction_3$area[ df_prediction_3$dist > synop$midpoint[i-1]], na.rm = TRUE)
      }
  else{
  synop$surface_area[i] <- sum(df_prediction_3$area[df_prediction_3$dist > synop$midpoint[i-1] & df_prediction_3$dist < synop$midpoint[i]], na.rm = TRUE)
  }
}

synop$flux_umolpers <- synop$Flux_ave*synop$surface_area
#synop <- synop[,-c(3,4,6:12)]



synop <- synop%>%drop_na(flux_umolpers)
synop <- synop[order(synop$dist),]

for(i in 1:nrow(synop)) {       # for-loop over rows
    if (i == 1) {
      synop$Totalflux_umolpers[i] <- synop$flux_umolpers[1]
    } else {
      synop[i,"Totalflux_umolpers"] <- synop[i-1,"Totalflux_umolpers"] + synop[i,"flux_umolpers"]
    }
  }
  

df_prediction_4 <- left_join(df_prediction,synop[,c("lon_fit","lat_fit","dist","Flux_ave","midpoint","surface_area","flux_umolpers","Totalflux_umolpers")], by=c("lon_fit","lat_fit","dist","Flux_ave"))


df_prediction_4 <- df_prediction_4[, !(colnames(df_prediction_4) %in% c("lon_dist","lat_dist","lat","lon","ele","time"))]


```

I guess what I want is a column associated with each CO2 measurment that gives me surface area associated with the measurment.

I now have some cra


```{r plot and write, echo=FALSE}
#df_prediction_4$flux_umolpers
ggplot(data=df_prediction_4, aes(dist, Totalflux_umolpers),size=5) +
  geom_point(size=5)
#df_prediction_4$adjusted_ppm
ggplot(data=df_prediction_4%>%drop_na(Date), aes(dist, ele_fit, color=log10(adjusted_ppm)),size=5) +
  geom_point(size=5)

#write.csv(df_prediction_4, here::here("ProcessedData/GAVI_synopticGeom_2022-06-04.csv"))

```

