---
title: "Geomorphology_GAVI"
author: "KWhitmore"
date: "12/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(lubridate)
library(plotly)
library(dplyr)
library(tidyr)
library(zoo)
library(plot3D)
library(splines)
library(Ecdat)
library(dplyr)
library(sp)
library(geosphere)
library(ggmap)
library(MALDIquant)


#funtion
#what does this function do?

##arrange df vars by position
##'vars' must be a named vector, e.g. c("var.name"=1)
arrange.vars <- function(data, vars){
    ##stop if not a data.frame (but should work for matrices as well)
    stopifnot(is.data.frame(data))

    ##sort out inputs
    data.nms <- names(data)
    var.nr <- length(data.nms)
    var.nms <- names(vars)
    var.pos <- vars
    ##sanity checks
    stopifnot( !any(duplicated(var.nms)), 
               !any(duplicated(var.pos)) )
    stopifnot( is.character(var.nms), 
               is.numeric(var.pos) )
    stopifnot( all(var.nms %in% data.nms) )
    stopifnot( all(var.pos > 0), 
               all(var.pos <= var.nr) )

    ##prepare output
    out.vec <- character(var.nr)
    out.vec[var.pos] <- var.nms
    out.vec[-var.pos] <- data.nms[ !(data.nms %in% var.nms) ]
    stopifnot( length(out.vec)==var.nr )

    ##re-arrange vars by position
    data <- data[ , out.vec]
    return(data)
}
```

## BUild the geomorphology data frame for GAVI tributaries
this was collected near the end of the field season

```{r build df 2021-12-18}
Geomorph <- read.csv(here::here("Geomorphology/Gavilan/GAVI_2021-07-27 10_13_40 Day.csv"), skip = 42)

Geomorph <- Geomorph[,3:6]

#convert time in UTC to local time
Geomorph$time <- gsub("T"," ", Geomorph$time)
Geomorph$time <- gsub("Z","", Geomorph$time)

Geomorph$time <- as.POSIXct(Geomorph$time, format = "%Y-%m-%d %H:%M:%S", tz = "UTC" )
Geomorph$time <-Geomorph$time - 5*60*60 
#round to nearest half second
Geomorph$time <- round_date(Geomorph$time, unit = "30 second")

#Geomorph_2 <- subset(Geomorph,
#      time > as.POSIXct('2021-07-27 10:50:00', tz="UTC")&
#        time < as.POSIXct('2021-07-27 11:12:00', tz="UTC"))

Geomorph_2 <- subset(Geomorph,
      time > as.POSIXct('2021-07-27 11:16:00', tz="UTC")&
        time < as.POSIXct('2021-07-27 11:36:00', tz="UTC"))



```


Let's do the synoptic one trib at a time


```{r add synop to df}
#synop <- read.csv(here::here("Synoptic/GAVI.csv"))
#synop <- read.csv(here::here("Synoptic/GAVI_2022-01-27.csv"))
#synop <- read.csv(here::here("Synoptic/GAVI_2022-04-19.csv"))
synop <- read.csv(here::here("Synoptic/GAVI_2022-06-04.csv"))

synop$X <- NULL

colnames(synop) <- c("lon","lat","Date","EOS_no","Flux_ave", "Tract","Point","VaisalaType","CO2_ppm_ave","WaterTemp_c","BaroPress_kpa","AirTemp_c","Total_hPa","adjusted_ppm","DateTime","SampleID","DOC","TDN","ID","Notes")
synop <- synop[,c("lat","lon","Date","EOS_no","Flux_ave", "Tract","Point","VaisalaType","CO2_ppm_ave","WaterTemp_c","BaroPress_kpa","AirTemp_c","Total_hPa","adjusted_ppm","DOC","TDN")]


#stream that goes up to the refuge
Synop_2 <- synop %>% filter(Date == "6/23/21" & Tract == 1)

```

```{r look at all synop data}

df <- full_join(Synop_2,Geomorph_2, by=c("lat","lon")) 



TrackMap_geo <- qmplot(lon, lat, data = Geomorph_2, zoom = 13, maptype = "toner-background")
TrackMap_geo

```



```{r first spline, echo=FALSE}

#Cut up lat long into peices, and then fit spline

Geomorph_sub <- Geomorph_2 
model <- lm(lon~bs(lat,
                   degree = 3),
            data=Geomorph_sub)

latlims <- range(Geomorph_sub$lat)
lat.grid <- seq(from=latlims[1],to=latlims[2], by=.0000001)
pred <-predict(model,newdata=list(lat=lat.grid),se=T)

plot(Geomorph_sub$lat,Geomorph_sub$lon,main="regressionSplinePLot")
lines(lat.grid,pred$fit,col='red',lwd=3)

fig<-plot_ly(data = Geomorph_sub, x = ~lat, y = ~lon)

#this looks pretty good! So we will save the data in a data frame

lat <- lat.grid
lon <- pred$fit
df1<-as.data.frame(lat)
df1$lon <- lon
df1$num <- '1'
```
now we have a smooth data frame of lat/lon data, we calculate the distance between each point

```{r calc dist}

###create a loop and calculate distance along the river from the predict_df. THen we can bind in the GEOMORPH!
df_prediction <- df1

df_prediction$num <- NULL
colnames(df_prediction) <- c("lat_fit","lon_fit")
df_prediction$lon_dist <- NA
df_prediction$lat_dist <- NA
i <- 2
for(i in 1:nrow(df_prediction)) {
  if (i == 1) {

      df_prediction$dist <- 0
      
    } else {
      df_prediction[i,"lon_dist"] <- df_prediction[i-1,"lon_fit"]
      df_prediction[i,"lat_dist"] <- df_prediction[i-1,"lat_fit"]
      df_prediction[i,"dist"] <- df_prediction[i-1,"dist"] + distHaversine(
        c(df_prediction[i,"lon_fit"], df_prediction[i,"lat_fit"]), 
        c(df_prediction[i,"lon_dist"], df_prediction[i,"lat_dist"]))
      }
}
```

```{r snap points to lat lon}

x <- SpatialPoints(Geomorph_2[,c(1:2)])
y <- SpatialPoints(df_prediction[,c(1:2)]) 
plot(y, col = "red")
points(y, col = "green")
snap = apply(spDists(x, y), 1, which.min)
points(y[snap,], pch = 3)


snap_df <- y[snap,]
coords_df <- snap_df@coords
pred <- as.data.frame(coords_df)
Geomorph_2$lon_fit <- pred$lon
Geomorph_2$lat_fit <- pred$lat


df_prediction_2 <- full_join(df_prediction,Geomorph_2,by=c("lon_fit","lat_fit"))
```

We also need to snap the synoptic df (for later)
```{r snap synop pts}

x <- SpatialPoints(Synop_2[,c(1:2)])
y <- SpatialPoints(df_prediction_2[,c(1:2)]) 
plot(x, col = "red")
points(y, col = "green")
snap = apply(spDists(x, y), 1, which.min)
points(y[snap,], pch = 3)


snap_df <- y[snap,]
coords_df <- snap_df@coords
pred <- as.data.frame(coords_df)
Synop_2$lon_fit <- pred$lon
Synop_2$lat_fit <- pred$lat
#synop_mainstem<-synop_mainstem[,c("Date","EOS_no","Flux_ave","Point","CO2_ppm_ave","lon_fit","lat_fit")]
Synop_2 <- Synop_2[,c("lon_fit","lat_fit","Date","EOS_no","Flux_ave","Point","VaisalaType","CO2_ppm_ave","WaterTemp_c","BaroPress_kpa","AirTemp_c","Total_hPa","adjusted_ppm","DOC","TDN")]



df_prediction_2 <- full_join(df_prediction_2,Synop_2,by=c("lon_fit","lat_fit"))

```


snap the points in our origional dama frame to bring in the elevation data


first I need to make sure that what I have done really worked

```{r test it, echo=FALSE}


fig <- plot_ly(df_prediction_2, x = ~lat, y = ~lon, z = ~ele, size = 1)
fig <- fig %>% add_markers()
fig <- fig %>% add_trace(x = ~lat_fit, y = ~lon_fit, z = ~ele, colors = c('Yellow'),
                         mode = 'markers')
fig <- fig %>% layout(scene = list(xaxis = list(title = 'lat'),
                                   yaxis = list(title = 'lon'),
                                   zaxis = list(title = 'elevation')))

fig


```

ok sweet that looks really good

We also need to snap the synoptic df (for later)


##calculate distance between each coordinate.
Here's the deal. We need to calcualte the distance between each coordinate 

First, lets find the most western lat point



now we have created a distance column that we can plot the elevation data against. lets see how that looks

```{r plot dist v ele, echo = FALSE}


fig <- plot_ly(df_prediction_2, x = ~dist, y = ~ele, size = 1)
fig
```


##loess spline

```{r diff 1 way}

df_prediction_2 <- df_prediction_2 #%>% filter(dist > 3)
distlims <- range(df_prediction_2$dist)
fit <- loess(ele ~ dist, degree=2, span = 0.90, data=df_prediction_2)
pred1 <- predict(fit, data.frame(dist = df_prediction_2$dist), se = TRUE)
df_prediction_2$ele_fit <- pred1$fit

df_prediction_2 %>% 
  drop_na(ele) %>%
  mutate(smooth = fit$fitted) %>%
  ggplot(aes(dist, ele)) +
  geom_point(size = 3, alpha = .5, color = "grey") +
  geom_line(aes(dist, smooth), color="red")

fig <- plot_ly(df_prediction_2, x = ~dist, y = ~ele_fit, size = 1)
#fig


```
#reverse order
unfortunatly gavi trib is going from downstream to up, and we want upstream to down. so reverse this order
you can't just reverse order the distance column because they are not collected at even intervals.

#loops below switch order of distance


```{r reverse, echo=FALSE}
df_prediction <- df_prediction_2
df_prediction <- df_prediction[order(df_prediction$dist),]
df_prediction$dist_diff <- NA

for(i in 1:nrow(df_prediction)) {       # for-loop over rows
  if (i == 1) {
    df_prediction$dist_diff[i] <- max(df_prediction$dist)
  } else {
    df_prediction$dist_diff[i] <-   max(df_prediction$dist) - df_prediction[i,"dist"]
  }
}

ggplot(data=df_prediction%>%drop_na(Date), aes(dist_diff, ele_fit, color=log10(CO2_ppm_ave)),size=5) +
  geom_point(size=5)

ggplot(data=df_prediction%>%drop_na(Date), aes(lon_fit, lat_fit, color=log10(CO2_ppm_ave)),size=5) +
  geom_point(size=5)


```


```{r bind df , echo=FALSE}
#save <- df_prediction

ggplot(data=df_prediction%>%drop_na(Flux_ave), aes(dist, ele_fit, color=Date)) +
  geom_point()

ggplot(data=df_prediction, aes(dist, ele_fit, col="CO2_ppm_ave")) +
  geom_point(size = 3, alpha = .5, color = "blue")


fig <- plot_ly(df_prediction, x = ~dist, y = ~ele_fit, size = 1)
fig

```

#read out
I'm really hoping this finaly product looks good


```{r write, echo=FALSE}
df_prediction <- df_prediction%>%select(lat_fit,lon_fit,ele_fit,dist_diff,Date,Point,Flux_ave,CO2_ppm_ave,adjusted_ppm,AirTemp_c,Total_hPa,VaisalaType,EOS_no)%>%rename(dist=dist_diff)
df_prediction <- unique(df_prediction)

##check should have 32 synop points 
check <- df_prediction%>%drop_na(Date)

#write.csv(df_prediction, here::here("ProcessedData/gaviTrib2_synoptic_2024-09-04.csv"))
#write.csv(check, here::here("ProcessedData/gaviTrib2_synopticpoints_arcpro_2024-09-04.csv"))

```

##now we add in width and depth data

#read in x, w, d data frame
and also df_prediction for trouble shooting purposes

```{r x and w and d, echo=FALSE}

df_prediction <- read.csv(here::here("ProcessedData/gaviTrib2_synoptic_2024-09-04.csv"))
df_prediction$X <- NULL

XWD <- read.csv(here::here("Geomorphology/Gavilan/GAVItrib2_2024-09-09.csv"))
XWD <- XWD%>%select(lon,lat,x_new,d,w,ele,notes)%>%rename(x=x_new)

XWD_save <- XWD[order(XWD$x),]

```

now we snap XWD data to prediction

```{r snap XDW, echo=FALSE}

df_prediction_arrange <- arrange.vars(df_prediction, c("lon_fit"=1))

XWD_1 <- XWD_save %>%drop_na(lon)
XWD_2 <- XWD_save

x <- SpatialPoints(XWD_1[,c(1:2)])
y <- SpatialPoints(df_prediction_arrange[,c(1:2)]) 
plot(x, col = "red")
points(y, col = "green")
snap = apply(spDists(x, y), 1, which.min)
points(y[snap,], pch = 3)

snap_df <- y[snap,]
coords_df <- snap_df@coords
pred <- as.data.frame(coords_df)
XWD_1$lon_fit <- pred$lon
XWD_1$lat_fit <- pred$lat

XWD_1 <- full_join(XWD[,c("x","d","w","notes")],XWD_1[,c("lon_fit","lat_fit","x","d","w","notes")],by=c("x","d","w","notes"))

df_prediction_1 <- full_join(df_prediction_arrange,XWD_1,by=c("lon_fit","lat_fit"))
df_prediction_1 <- df_prediction_1[,c("lon_fit","lat_fit","dist","x","d","w","notes")]
df_prediction_1 <- unique(df_prediction_1)


#df_prediction_1 <- df_prediction_1%>%filter(notes!="starting at large stream upsteam of last measurement (I think?)")

saveit <- df_prediction_1
```

We've snapped in the waypoints collected while sampling x/width/depth, but there are many points in between don't have corresponding lat/lon/ele. So how to fix these gaps?


Our tools are dist (modeled) and x (measured). Some x are already associated with dist we need to associate all xs with distance. 

If we can identify the xs assiciated with distance, we can then calcualte the difference between each each one. Then calcualte the ratio of x inbetween and total difference


##do this:
if pt1 and pt2 are known values of x, and pt-btw is known dist but unknown x, then:

(Dist[pt-btw] - Dist[pt1])/(Dist[pt2] - Dist[pt1]) = (unknown - x[pt1])/(x[pt2] - x[pt1])

unknown = (Dist[pt-btw] - Dist[pt1])/(Dist[pt2] - Dist[pt1])*(x[pt2] - x[pt1]) + x[pt1]

##but how do that in a loop?
key to this is being able idntify the next known x in between NAs.

the code below realtes x as measured in the field to distance as calculated with way points. The ancors are waypoints collected every 50 meters in the field 

```{r dist and x, echo=FALSE}
df_prediction_1 <- saveit

df_prediction_1 <- df_prediction_1[order(df_prediction_1$x),]
pred_df <- na.omit(df_prediction_1[,c("x","dist")])


for(i in 1:nrow(df_prediction_1)) {       # for-loop over rows
  pred_df <- na.omit(df_prediction_1[,c("x","dist")])
  
  if (is.na(df_prediction_1[i,"dist"]) == FALSE) {
    df_prediction_1$x_pred[i] <- df_prediction_1$dist[i]

  } else if (is.na(df_prediction_1[i,"dist"]) == TRUE) { 
    #i want to select the two "x" values that are the closest to the x[i] and have associated distance measurements
    #first select closest x and associated dist
    index <- match.closest(df_prediction_1$x[i], pred_df$x,tolerance='Inf')
    dist1 <- pred_df$dist[index]
    x1 <- pred_df$x[index]
    #now find the second closest number - well no. I don't want the second closest. I want the number on the other side. so I don't want to just remove the first x value, I want to remove that value and everythign above or everythign below that value -- depending on weather it is higher or lower
    if (x1 < df_prediction_1$x[i]) {
    pred_df_closestremoved <- pred_df%>%filter(x > df_prediction_1$x[i])
    index <- match.closest(df_prediction_1$x[i], pred_df_closestremoved$x,tolerance='Inf')
    dist2 <- pred_df_closestremoved$dist[index]
    x2 <- pred_df_closestremoved$x[index]
    } else {
    pred_df_closestremoved <- pred_df%>%filter(x < df_prediction_1$x[i])
    index <- match.closest(df_prediction_1$x[i], pred_df_closestremoved$x,tolerance='Inf')
    dist2 <- pred_df_closestremoved$dist[index]
    x2 <- pred_df_closestremoved$x[index]
    }
        #sort out max and mins 
    dist_min = min(dist1,dist2)
    dist_max = max(dist1,dist2)
    x_min = min(x1,x2)
    x_max = max(x1,x2)
    
    df_prediction_1$x_pred[i] <- (df_prediction_1$x[i]-x_min)/(x_max-x_min) * (dist_max-dist_min) + dist_min
    
  }
}
```

Now we have a data frame with x predicted and associated with distance. Now we associate the closest actual x measurments, depth and width with the predicted x  


```{r width loop, echo=FALSE}

latlon_df <- df_prediction%>%select(lat_fit,lon_fit,ele_fit,dist,Flux_ave,adjusted_ppm)%>%rename(x_pred=dist)
XWD_df <- df_prediction_1

setDT(latlon_df)
setDT(XWD_df)

#XWD_fit <- XWD_1[,c("x","w","d","notes")]
#colnames(XWD_fit) <- c("x_pred","w","d","notes")

#setDT(df_prediction_2)
#setDT(XWD_fit)

df_prediction_4 <- latlon_df[XWD_df, roll = "nearest", on = "x_pred"]

df_prediction_5 <- df_prediction_4%>%select(lat_fit,lon_fit,ele_fit,x_pred,x,d,w,Flux_ave,adjusted_ppm,notes)

#write.csv(df_prediction_5, here::here("ProcessedData/GaviTrib2_XWD.csv"))

```

