---
title: "Geomorphology_GAVI"
author: "KWhitmore"
date: "12/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(lubridate)
library(plotly)
library(dplyr)
library(tidyr)
library(zoo)
library(plot3D)
library(splines)
library(Ecdat)
library(dplyr)
library(sp)
library(geosphere)
library(ggmap)


```

## BUild the geomorphology data frame for GAVI tributaries
this was collected near the end of the field season

Liz and segundo long trib

```{r build df 2021-12-18}
Geomorph <- read.csv(here::here("/Geomorphology/Gavilan/GAVI_2021-07-27 10_13_40 Day.csv"), skip = 42)

Geomorph <- Geomorph[,3:6]

#convert time in UTC to local time
Geomorph$time <- gsub("T"," ", Geomorph$time)
Geomorph$time <- gsub("Z","", Geomorph$time)

Geomorph$time <- as.POSIXct(Geomorph$time, format = "%Y-%m-%d %H:%M:%S", tz = "UTC" )
Geomorph$time <-Geomorph$time - 5*60*60 
#round to nearest half second
Geomorph$time <- round_date(Geomorph$time, unit = "30 second")

Geomorph_2 <- Geomorph%>%filter(ele > 4100)
##

Geomorph_3 <- subset(Geomorph_2,
      time > as.POSIXct('2021-07-27 14:38:30', tz="UTC")& time < as.POSIXct('2021-07-27 14:55:00', tz="UTC") )


Geomorph_4 <- subset(Geomorph_2,
      time > as.POSIXct('2021-07-27 14:38:30', tz="UTC")& time < as.POSIXct('2021-07-27 15:00:30', tz="UTC") 
      )

Geomorph_5 <- subset(Geomorph_2,
      time > as.POSIXct('2021-07-27 14:24:30', tz="UTC")& time < as.POSIXct('2021-07-27 14:32:00', tz="UTC") )

TrackMap_geo <- qmplot(lon, lat, data = Geomorph_2, zoom = 13, maptype = "toner-background")
TrackMap_geo

TrackMap_geo <- qmplot(lon, lat, data = Geomorph_5, zoom = 13, maptype = "toner-background")
TrackMap_geo


```


Let's do the synoptic one trib at a time


```{r add synop to df}
#synop <- read.csv(here::here("Synoptic/GAVI.csv"))
synop <- read.csv(here::here("Synoptic/GAVI_2022-01-27.csv"))

synop$X <- NULL

colnames(synop) <- c("lon","lat","Date","EOS_no","Flux_ave", "Tract","Point","VaisalaType","CO2_ppm_ave","WaterTemp_c","BaroPress_kpa","AirTemp_c","Total_hPa","adjusted_ppm")
synop <- synop[,c("lat","lon","Date","EOS_no","Flux_ave", "Tract","Point","VaisalaType","CO2_ppm_ave","WaterTemp_c","BaroPress_kpa","AirTemp_c","Total_hPa","adjusted_ppm")]

#stream that goes up to the refuge
Synop_2_1 <- synop %>%
  filter(EOS_no == "EOS_1") %>%
  filter(Date == "2021-06-30" | Date == "2021-06-29") %>%
  filter(Tract==2)

Synop_2_2 <- synop %>%
  filter(EOS_no == "EOS_1") %>%
  filter(Date == "2021-06-30" & Tract==1) 

Synop_2 <- rbind(Synop_2_1,Synop_2_2)
rm(Synop_2_1,Synop_2_2)

TrackMap <- qmplot(lon, lat, data = Synop_2, zoom = 13,
                   maptype = "toner-background", color=as.factor(Tract),shape = as.factor(Date))
TrackMap

TrackMap_2 <- qmplot(lon, lat, data = synop, zoom = 13,
                   maptype = "toner-background", color=EOS_no,shape = as.factor(Date))
TrackMap_2


TrackMap_geo <- qmplot(lon, lat, data = Geomorph_5, zoom = 13, maptype = "toner-background")
TrackMap_geo

```

```{r look at all synop data}

df <- full_join(Synop_2,Geomorph_5, by=c("lat","lon")) 

TrackMap <- qmplot(lon, lat, data = df, zoom = 13,
                   maptype = "toner-background", color=Point,shape = EOS_no)
TrackMap

TrackMap_geo <- qmplot(lon, lat, data = Geomorph_5, zoom = 13, maptype = "toner-background")
TrackMap_geo

```



```{r first spline, echo=FALSE}

#Cut up lat long into peices, and then fit spline

Geomorph_sub <- Geomorph_5
model <- lm(lon~bs(lat,
                   degree = 3),
            data=Geomorph_sub)

latlims <- range(Geomorph_sub$lat)
lat.grid <- seq(from=latlims[1],to=latlims[2], by=.0000001)
pred <-predict(model,newdata=list(lat=lat.grid),se=T)

plot(Geomorph_sub$lat,Geomorph_sub$lon,main="regressionSplinePLot")
lines(lat.grid,pred$fit,col='red',lwd=3)

fig<-plot_ly(data = Geomorph_sub, x = ~lat, y = ~lon)

#this looks pretty good! So we will save the data in a data frame

lat <- lat.grid
lon <- pred$fit
df1<-as.data.frame(lat)
df1$lon <- lon
df1$num <- '1'
```
now we have a smooth data frame of lat/lon data, we calculate the distance between each point

```{r calc dist}

###create a loop and calculate distance along the river from the predict_df. THen we can bind in the GEOMORPH!
df_prediction <- df1

df_prediction$num <- NULL
#df_prediction <- df_prediction[,c("lon","lat")]
colnames(df_prediction) <- c("lat_fit","lon_fit")
df_prediction$lon_dist <- NA
df_prediction$lat_dist <- NA
i <- 2
for(i in 1:nrow(df_prediction)) {
  if (i == 1) {

      df_prediction$dist <- 0
      
    } else {
      df_prediction[i,"lon_dist"] <- df_prediction[i-1,"lon_fit"]
      df_prediction[i,"lat_dist"] <- df_prediction[i-1,"lat_fit"]
      df_prediction[i,"dist"] <- df_prediction[i-1,"dist"] + distHaversine(
        c(df_prediction[i,"lon_fit"], df_prediction[i,"lat_fit"]), 
        c(df_prediction[i,"lon_dist"], df_prediction[i,"lat_dist"]))
      }
}
```

```{r snap points to lat lon}

x <- SpatialPoints(Geomorph_5[,c(1:2)])
y <- SpatialPoints(df_prediction[,c(1:2)]) 
plot(y, col = "red")
points(y, col = "green")
snap = apply(spDists(x, y), 1, which.min)
points(y[snap,], pch = 3)


snap_df <- y[snap,]
coords_df <- snap_df@coords
pred <- as.data.frame(coords_df)
Geomorph_5$lon_fit <- pred$lon
Geomorph_5$lat_fit <- pred$lat


df_prediction_2 <- full_join(df_prediction,Geomorph_5,by=c("lon_fit","lat_fit"))
```

We also need to snap the synoptic df (for later)
```{r snap synop pts}

x <- SpatialPoints(Synop_2[,c(1:2)])
y <- SpatialPoints(df_prediction_2[,c(1:2)]) 
plot(x, col = "red")
points(y, col = "green")
snap = apply(spDists(x, y), 1, which.min)
points(y[snap,], pch = 3)



snap_df <- y[snap,]
coords_df <- snap_df@coords
pred <- as.data.frame(coords_df)
Synop_2$lon_fit <- pred$lon
Synop_2$lat_fit <- pred$lat
#synop_mainstem<-synop_mainstem[,c("Date","EOS_no","Flux_ave","Point","CO2_ppm_ave","lon_fit","lat_fit")]
Synop_2 <- Synop_2[,c("lon_fit","lat_fit","Date","EOS_no","Flux_ave","Point","VaisalaType","CO2_ppm_ave","WaterTemp_c","BaroPress_kpa","AirTemp_c","Total_hPa","adjusted_ppm")]


df_prediction_2 <- full_join(df_prediction_2,Synop_2,by=c("lon_fit","lat_fit"))

```


snap the points in our origional dama frame to bring in the elevation data


first I need to make sure that what I have done really worked

```{r testing snap to line, echo=FALSE}


fig <- plot_ly(df_prediction_2, x = ~lat, y = ~lon, z = ~ele, size = 1)
fig <- fig %>% add_markers()
fig <- fig %>% add_trace(x = ~lat_fit, y = ~lon_fit, z = ~ele, colors = c('Yellow'),
                         mode = 'markers')
fig <- fig %>% layout(scene = list(xaxis = list(title = 'lat'),
                                   yaxis = list(title = 'lon'),
                                   zaxis = list(title = 'elevation')))

fig


```

ok sweet that looks really good

We also need to snap the synoptic df (for later)


##calculate distance between each coordinate.
Here's the deal. We need to calcualte the distance between each coordinate 

First, lets find the most western lat point



now we have created a distance column that we can plot the elevation data against. lets see how that looks

```{r plot dist v ele, echo = FALSE}


fig <- plot_ly(df_prediction_2, x = ~dist, y = ~ele, size = 1)
fig
```


##loess spline

```{r diff 1 way}

df_prediction_2 <- df_prediction_2 #%>% filter(dist > 3)
distlims <- range(df_prediction_2$dist)
fit <- loess(ele ~ dist, degree=2, span = 0.90, data=df_prediction_2)
pred1 <- predict(fit, data.frame(dist = df_prediction_2$dist), se = TRUE)
df_prediction_2$ele_fit <- pred1$fit

df_prediction_2 %>% 
  drop_na(ele) %>%
  mutate(smooth = fit$fitted) %>%
  ggplot(aes(dist, ele)) +
  geom_point(size = 3, alpha = .5, color = "grey") +
  geom_line(aes(dist, smooth), color="red")

fig <- plot_ly(df_prediction_2, x = ~dist, y = ~ele_fit, size = 1)
#fig


```

some slope fixing

```{r check slope, echo=FALSE}


predict <- df_prediction_2

#save <- df_prediction

###slope check

predict <- predict[order(predict$dist),]

predict$slope <- NA
for(i in 1:nrow(predict)) {       # for-loop over rows
  predict$dist_down[i] <- predict$dist[i+1]
  predict$ele_down[i] <- predict$ele_fit[i+1]
}

predict$slope <- (predict$ele_fit - predict$ele_down)/(predict$dist - predict$dist_down)
predict$dist_down <- NULL
predict$ele_down <- NULL

df_predictionblah <- predict%>%filter(slope<0)

#df_prediction_1 <- predict

###

up <- which.min(abs(predict$dist-30.49452))
down <- which.min(abs(predict$dist-11.83194))

slope <- (predict[down,"ele_fit"] - predict[up,"ele_fit"])/(predict[down,"dist"] - predict[up,"dist"])
b = predict[up,"ele_fit"] - slope*predict[up,"dist"]
predict_a <- predict %>% 
  filter(dist > predict[down,"dist"] & dist < predict[up,"dist"])
predict_b <- predict %>% 
  filter(dist > predict[up,"dist"] | dist < predict[down,"dist"])
predict_a$ele_fit <- slope*predict_a$dist + b
predict <- rbind(predict_a,predict_b)
rm(predict_a,predict_b)
##

```


#reverse order
unfortunatly gavi trib is going from downstream to up, and we want upstream to down. so reverse this order
you can't just reverse order the distance column because they are not collected at even intervals.

#loops below switch order of distance

```{r reverse, echo=FALSE}
df_prediction <- predict

df_prediction <- df_prediction[order(df_prediction$dist),]
df_prediction$dist_diff <- NA

for(i in 1:nrow(df_prediction)) {       # for-loop over rows
  if (i == 1) {
    df_prediction$dist_diff[i] <- 0
  } else {
    df_prediction[i,"dist_diff"] <-   df_prediction[i,"dist"] - df_prediction[i-1,"dist"]
  }
}

df_prediction <- df_prediction[order(-df_prediction$dist),]
df_prediction$dist_new <- NA
for(i in 1:nrow(df_prediction)) {       # for-loop over rows
  if (i == 1) {
    df_prediction$dist_new[i] <- 0
  } else {
    df_prediction[i,"dist_new"] <-   df_prediction[i,"dist_diff"] + df_prediction[i-1,"dist_new"]
  }
}


df_prediction$X <-NULL
df_prediction$dist <- NULL
names(df_prediction)[names(df_prediction)=="dist_new"] <- "dist"

check <- df_prediction%>%drop_na(Date)

#loosing a synop point in the next chunk
```


#calcualte slope
here we calculate slope from the sample point and upstream 50m

```{r calc slope, echo=FALSE}

###
df_prediction <- df_prediction[order(df_prediction$dist),]
df_prediction$slope50m <- NA
loop <- df_prediction%>%drop_na(ele_fit)
for(i in 1:nrow(loop)) {       # for-loop over rows
  x = loop$dist[i] - 50
  loop$ele_minus[i] <- loop[which.min(abs(loop$dist-x)),]$ele_fit
  loop$dist_minus[i] <- loop[which.min(abs(loop$dist-x)),]$dist
  
  y = loop$dist[i] + 0
  loop$ele_plus[i] <- loop[which.min(abs(loop$dist-y)),]$ele_fit
  loop$dist_plus[i] <- loop[which.min(abs(loop$dist-y)),]$dist
  
  loop$slope50m <- (loop$ele_minus-loop$ele_plus)/(loop$dist_minus-loop$dist_plus)
  
}
loop$dist_minus <- NULL
loop$dist_plus <- NULL
loop$ele_minus <- NULL
loop$ele_plus <- NULL

df_prediction <- loop 
check <- df_prediction%>%drop_na(Date)
```


#plot

```{r bind df , echo=FALSE}
#save <- df_prediction

ggplot(data=df_prediction%>%drop_na(Flux_ave), aes(dist, ele_fit, color=Date)) +
  geom_point()

ggplot(data=df_prediction, aes(dist, ele_fit, col="CO2_ppm_ave")) +
  geom_point(size = 3, alpha = .5, color = "blue")



```

```{r write, echo=FALSE}
check <- df_prediction%>%drop_na(Date)
write.csv(df_prediction, here::here("ProcessedData/GAVI_Trib3_synoptic_2022-04-10.csv"))
```

