---
title: "Geomorphology_GAVI"
author: "KWhitmore"
date: "12/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(lubridate)
library(plotly)
library(dplyr)
library(tidyr)
library(zoo)
library(plot3D)
library(splines)
library(Ecdat)
library(dplyr)
library(sp)
library(geosphere)
library(ggmap)


```

## BUild the geomorphology data frame for Ante mainstem

2021-07-26 9:50
```{r build df 2021-12-18}


Geomorph <- read.csv(here::here("Geomorphology/Gavilan/GAVI_Dec2021.csv"), skip = 70)


Geomorph <- Geomorph[,3:6]

#convert time in UTC to local time
Geomorph$time <- gsub("T"," ", Geomorph$time)
Geomorph$time <- gsub("Z","", Geomorph$time)

Geomorph$time <- as.POSIXct(Geomorph$time, format = "%Y-%m-%d %H:%M:%S", tz = "UTC" )
Geomorph$time <-Geomorph$time - 5*60*60 
#round to nearest half second
Geomorph$time <- round_date(Geomorph$time, unit = "30 second")

# 2021-12-18 START: 10:33:00  

#downstream to outlet 11:39
Geomorph_1 <- subset(Geomorph,
      time > as.POSIXct('2021-12-18 10:33:00', tz="UTC") & time < as.POSIXct('2021-12-18 11:39:00', tz="UTC"))
#start at GAVI inlet
Geomorph_2 <- subset(Geomorph,
      time > as.POSIXct('2021-12-18 11:53:00', tz="UTC") & time < as.POSIXct('2021-12-18 13:15:00', tz="UTC"))


Geomorph <- rbind(Geomorph_1,Geomorph_2)

```

It's not a bad thing, per se, but I really made things complicated when I started taking measurmenets of streams in addition to the mainstem of GAVI. I blame Diego, frankly. But I also blame myself from listening to Diego. Have confidence in you're game plan, Kriddie, for goodness Sake.

So let's try to just select the mainstem samples, for starters.

```{r add synop to df}
#synop <- read.csv(here::here("Synoptic/GAVI.csv"))
#synop <- read.csv(here::here("Synoptic/GAVI_2022-01-27.csv"))
#synop <- read.csv(here::here("Synoptic/GAVI_2022-03-24.csv"))
#synop <- read.csv(here::here("Synoptic/GAVI_2022-04-19.csv"))
synop <- read.csv(here::here("Synoptic/GAVI_2022-06-04.csv"))

synop$X <- NULL

colnames(synop) <- c("lon","lat","Date","EOS_no","Flux_ave", "Tract","Point","VaisalaType","CO2_ppm_ave","WaterTemp_c","BaroPress_kpa","AirTemp_c","Total_hPa","adjusted_ppm","DateTime","SampleID", "DOC","TDN","ID","Notes")
synop <- synop[,c("lat","lon","Date","DateTime","EOS_no","Flux_ave", "Tract","Point","VaisalaType","CO2_ppm_ave","WaterTemp_c","BaroPress_kpa","AirTemp_c","Total_hPa","adjusted_ppm","DOC","TDN")]

Synopjune18 <- synop %>% filter(Date == "2021-06-18")
Synopjune22 <- synop %>% filter(Date == "2021-06-22" & EOS_no == "EOS1" & Tract == 1)
Synopjune29 <- synop %>% filter(Date == "2021-06-29" & EOS_no == "EOS2" & Tract == 7)
Synopjune30 <- synop %>% filter(Date == "2021-06-30" & EOS_no == "EOS2")

synop_mainstem <- rbind(Synopjune18,Synopjune22,Synopjune29,Synopjune30)
rm(Synopjune18,Synopjune22,Synopjune29,Synopjune30)
```

```{r look at all synop data}
df <- full_join(synop_mainstem,Geomorph, by=c("lat","lon")) 


TrackMap <- qmplot(lon, lat, data = synop, zoom = 13,
                   maptype = "toner-background", color=as.factor(Date), shape = EOS_no
                   )

TrackMap_geo <- qmplot(lon, lat, data = Geomorph, zoom = 13,
                   maptype = "toner-background")
TrackMap
TrackMap_geo

```


##Plot the geomorphology data in 3-d

```{r 3d plot no synop, echo=FALSE}


fig <- plot_ly(Geomorph, x = ~lat, y = ~lon, z = ~ele, size = 1
)
fig <- fig %>% add_markers()
#fig <- fig %>% add_trace(x = ~lat, y = ~lon, z = ~ele, #color = ~EOS_no#, colors = c('Blue','Yellow'),
#                         mode = 'markers')
fig <- fig %>% layout(scene = list(xaxis = list(title = 'lat'), yaxis = list(title = 'lon'), zaxis = list(title = 'elevation')))

fig


```

## Now Plot data in 3D including synoptic points


```{r 3d plot and synop, echo=FALSE}

df <- full_join(synop_mainstem,Geomorph, by=c("lat","lon")) 


fig <- plot_ly(df, x = ~lat, y = ~lon, z = ~ele, size = 1,
               marker = list(color = ~CO2_ppm_ave, colorscale = c('#FFE1A1', '#683531'), showscale = TRUE))

#FFE1A1 #683531

fig <- fig %>% add_markers()
#fig <- fig %>% add_trace(x = ~lat, y = ~lon, z = ~ele, #color = ~EOS_no#, colors = c('Blue','Yellow'),
#                         mode = 'markers')
fig <- fig %>% layout(scene = list(xaxis = list(title = 'lat'),yaxis = list(title = 'lon'),zaxis = list(title = 'elevation')))

fig

TrackMap <- qmplot(lon, lat, data = df, zoom = 13,
                   maptype = "toner-background", color=ele)

TrackMap
```
#are you seeing the problem? 
This is worse then both Colmillo and Antenas. below the main wetland its not so bad, but above is kinda a mess. I think I should re-do this when I am back at the site, but for now, let us proceed.

#working with 3-D is hard. full stop.
In this code chunk, we start by smooting a line to the lat lon data, which appears to be more accurate than the elevation

We will do this in parts though, be cause the relationship between lat lon can not be described as a function

Colmillo is not too far off from a funtion if lat is the "x" and lon is the 'y'

```{r first spline, echo=FALSE}


df <- full_join(synop_mainstem,Geomorph, by=c("lat","lon")) 

#Cut up lat long into peices, and then fit spline


Geomorph_sub <- df %>% filter(lat <= -.32681)
model <- lm(lon~bs(lat,
              #     knots = c(-0.3164286,-0.3163748,-0.3162296,                          -0.3161252,-0.3161399,-.3156738, -0.3154703,-0.3152688,-0.3152838), 
                   degree = 10),
            data=Geomorph_sub)

latlims <- range(Geomorph_sub$lat)
lat.grid <- seq(from=latlims[1],to=latlims[2], by=.000001)
pred <-predict(model,newdata=list(lat=lat.grid),se=T)

plot(Geomorph_sub$lat,Geomorph_sub$lon,main="regressionSplinePLot")
lines(lat.grid,pred$fit,col='red',lwd=3)

fig<-plot_ly(data = Geomorph_sub, x = ~lat, y = ~lon)

#this looks pretty good! So we will save the data in a data frame

lat <- lat.grid
lon <- pred$fit
df1<-as.data.frame(lat)
df1$lon <- lon
df1$num <- '1'
```


```{r bind dataframes, echo=FALSE}

#now we need to make a dataframe that discribes this relationship between lat lon
df_prediction <- rbind(df1)


plot(df_prediction$lon~df_prediction$lat,col=df_prediction$num)

plot(Geomorph$lat,Geomorph$lon)

```

now we have a smooth data frame of lat/lon data, we calculate the distance between each point

```{r calc dist}

###create a loop and calculate distance along the river from the predict_df. Then we can bind in the GEOMORPH!
df_prediction <- rbind(df1, df2) %>% drop_na(lat)# %>% filter(lat <= -.327)

df_prediction$num <- NULL
#df_prediction <- df_prediction[,c("lon","lat")]
colnames(df_prediction) <- c("lat_fit","lon_fit")
df_prediction$lon_dist <- NA
df_prediction$lat_dist <- NA
i <- 2
for(i in 1:nrow(df_prediction)) {
  if (i == 1) {

      df_prediction$dist <- 0
#      df_prediction[i,"lon_dist"] <- 0
#      df_prediction[i,"lat_dist"] <- 0
      
    } else {
      df_prediction[i,"lon_dist"] <- df_prediction[i-1,"lon_fit"]
      df_prediction[i,"lat_dist"] <- df_prediction[i-1,"lat_fit"]
      df_prediction[i,"dist"] <- df_prediction[i-1,"dist"] + distHaversine(
        c(df_prediction[i,"lon_fit"], df_prediction[i,"lat_fit"]), 
        c(df_prediction[i,"lon_dist"], df_prediction[i,"lat_dist"]))
      }
}
```

snap the points in our origional dama frame to bring in the elevation data


```{r snap points to lat lon}

x <- SpatialPoints(Geomorph[,c(1:2)])
y <- SpatialPoints(df_prediction[,c(1:2)]) 
plot(y, col = "red")
points(y, col = "green")
snap = apply(spDists(x, y), 1, which.min)
points(y[snap,], pch = 3)


snap_df <- y[snap,]
coords_df <- snap_df@coords
pred <- as.data.frame(coords_df)
Geomorph$lon_fit <- pred$lon
Geomorph$lat_fit <- pred$lat


df_prediction <- full_join(df_prediction,Geomorph,by=c("lon_fit","lat_fit"))

```
first I need to make sure that what I have done really worked

```{r testing snap to line, echo=FALSE}


fig <- plot_ly(Geomorph, x = ~lat, y = ~lon, z = ~ele, size = 1)
fig <- fig %>% add_markers()
fig <- fig %>% add_trace(x = ~lat_fit, y = ~lon_fit, z = ~ele, colors = c('Yellow'),
                         mode = 'markers')
fig <- fig %>% layout(scene = list(xaxis = list(title = 'lat'),
                                   yaxis = list(title = 'lon'),
                                   zaxis = list(title = 'elevation')))

fig


```

ok sweet that looks really good

We also need to snap the synoptic df (for later)
```{r snap synop pts}

x <- SpatialPoints(synop_mainstem[,c(1:2)])
y <- SpatialPoints(df_prediction[,c(1:2)]) 
plot(x, col = "red")
points(y, col = "green")
snap = apply(spDists(x, y), 1, which.min)
points(y[snap,], pch = 3)


snap_df <- y[snap,]
coords_df <- snap_df@coords
pred <- as.data.frame(coords_df)
synop_mainstem$lon_fit <- pred$lon
synop_mainstem$lat_fit <- pred$lat
#synop_mainstem<-synop_mainstem[,c("Date","EOS_no","Flux_ave","Point","CO2_ppm_ave","lon_fit","lat_fit")]
synop_mainstem <- synop_mainstem[,c("lon_fit","lat_fit","Date","EOS_no","Flux_ave","Point","VaisalaType","CO2_ppm_ave","WaterTemp_c","BaroPress_kpa","AirTemp_c","Total_hPa","adjusted_ppm","DOC","TDN")]


df_prediction <- full_join(df_prediction,synop_mainstem,by=c("lon_fit","lat_fit"))
check <- df_prediction%>%drop_na(Date)
## at this point there are 39 synoptic points. there should only be 37


```



##calculate distance between each coordinate.
Here's the deal. We need to calcualte the distance between each coordinate 

First, lets find the most western lat point



now we have created a distance column that we can plot the elevation data against. lets see how that looks

```{r plot dist v ele, echo = FALSE}


fig <- plot_ly(df_prediction, x = ~dist, y = ~ele, size = 1)
fig
```


I think it would be better if we did two different prediction above and below gavi


##loess spline
i think loess might be a little better for this? IT IS NOT
But maybe just because data is not great. please revisit

ok i did revisit, and I think this is better now

but we do need to split up downstream and upstream data

```{r diff 1 way}

df_prediction_1 <- df_prediction %>% filter(dist > 770)
distlims <- range(df_prediction_1$dist)
fit <- loess(ele ~ dist, degree=2, span = 0.20, data=df_prediction_1)
pred1 <- predict(fit, data.frame(dist = df_prediction_1$dist), se = TRUE)
df_prediction_1$ele_fit <- pred1$fit

df_prediction_1 %>% 
  drop_na(ele) %>%
  mutate(smooth = fit$fitted) %>%
  ggplot(aes(dist, ele)) +
  geom_point(size = 3, alpha = .5, color = "grey") +
  geom_line(aes(dist, smooth), color="red")

fig <- plot_ly(df_prediction_1, x = ~dist, y = ~ele_fit, size = 1)
fig

check <- df_prediction%>%drop_na(Date)


```

```{r fix slope 1, echo=FALSE}
#save <- df_prediction

predict <- df_prediction_1
##fix downstream
#up <- which.min(abs(predict$dist-822))
#down <- which.min(abs(predict$dist-820.8406))

up <- which.min(abs(predict$dist-854.3283))
down <- which.min(abs(predict$dist-772.5268))

slope <- (predict[down,"ele_fit"] - predict[up,"ele_fit"])/(predict[down,"dist"] - predict[up,"dist"])
b = predict[up,"ele_fit"] - slope*predict[up,"dist"]
predict_a <- predict %>% filter(dist < predict[up,"dist"]& dist > 770)
predict_b <- predict %>% filter(dist > predict[up,"dist"])
predict_a$ele_fit <- slope*predict_a$dist + b
predict <- rbind(predict_a,predict_b)
rm(predict_a,predict_b)
##

## there are problems in the middle too. 

up <- which.min(abs(predict$dist-905.1004))
down <- which.min(abs(predict$dist-886.5401))

slope <- (predict[down,"ele_fit"] - predict[up,"ele_fit"])/(predict[down,"dist"] - predict[up,"dist"])
b = predict[up,"ele_fit"] - slope*predict[up,"dist"]
predict_a <- predict %>% 
  filter(dist > predict[down,"dist"] & dist < predict[up,"dist"])
predict_b <- predict %>% 
  filter(dist > predict[up,"dist"] | dist < predict[down,"dist"])
predict_a$ele_fit <- slope*predict_a$dist + b
predict <- rbind(predict_a,predict_b)
rm(df_prediction_a,predict_b)

## there are problems in the middle too. 

up <- which.min(abs(predict$dist-948.6438))
down <- which.min(abs(predict$dist-947.1718))

slope <- (predict[down,"ele_fit"] - predict[up,"ele_fit"])/(predict[down,"dist"] - predict[up,"dist"])
b = predict[up,"ele_fit"] - slope*predict[up,"dist"]
predict_a <- predict %>% 
  filter(dist > predict[down,"dist"] & dist < predict[up,"dist"])
predict_b <- predict %>% 
  filter(dist > predict[up,"dist"] | dist < predict[down,"dist"])
predict_a$ele_fit <- slope*predict_a$dist + b
predict <- rbind(predict_a,predict_b)
rm(df_prediction_a,predict_b)


## there are problems in the middle too. 

up <- which.min(abs(predict$dist-1052.228))
down <- which.min(abs(predict$dist-1015.883))

slope <- (predict[down,"ele_fit"] - predict[up,"ele_fit"])/(predict[down,"dist"] - predict[up,"dist"])
b = predict[up,"ele_fit"] - slope*predict[up,"dist"]
predict_a <- predict %>% 
  filter(dist > predict[down,"dist"] & dist < predict[up,"dist"])
predict_b <- predict %>% 
  filter(dist > predict[up,"dist"] | dist < predict[down,"dist"])
predict_a$ele_fit <- slope*predict_a$dist + b
predict <- rbind(predict_a,predict_b)
rm(df_prediction_a,predict_b)

###slope check

predict <- predict[order(predict$dist),]

predict$slope <- NA
for(i in 1:nrow(predict)) {       # for-loop over rows
  predict$dist_down[i] <- predict$dist[i+1]
  predict$ele_down[i] <- predict$ele_fit[i+1]
}

predict$slope <- (predict$ele_fit - predict$ele_down)/(predict$dist - predict$dist_down)
predict$dist_down <- NULL
predict$ele_down <- NULL

df_prediction_1 <- predict

fig <- plot_ly(predict%>%drop_na(Date), x = ~dist, y = ~ele_fit, size = 1)
fig


```

```{r diff 2 way}

df_prediction_2 <- df_prediction %>% 
  filter(dist < 600 & dist > 24)#%>%
#  filter(ele > 4096.3 | dist < 476.4)
check <- df_prediction%>%drop_na(Date)

distlims <- range(df_prediction_2$dist)
fit <- loess(ele ~ dist, degree=2, span = 0.20, data=df_prediction_2)
pred1 <- predict(fit, data.frame(dist = df_prediction_2$dist), se = TRUE)
df_prediction_2$ele_fit <- pred1$fit

df_prediction_2 %>% 
  drop_na(ele) %>%
  mutate(smooth = fit$fitted) %>%
  ggplot(aes(dist, ele)) +
  geom_point(size = 3, alpha = .5, color = "grey") +
  geom_line(aes(dist, smooth), color="red")

fig <- plot_ly(df_prediction_2%>%drop_na(Date), x = ~dist, y = ~ele_fit, size = 1)
fig


check <- df_prediction_2%>%drop_na(Date)

```


```{r fix slope 2, echo=FALSE}
#save <- df_prediction

predict <- df_prediction_2


## there are problems in the middle too. 

up <- which.min(abs(predict$dist-119.15346))
down <- which.min(abs(predict$dist-79.28031))

slope <- (predict[down,"ele_fit"] - predict[up,"ele_fit"])/(predict[down,"dist"] - predict[up,"dist"])
b = predict[up,"ele_fit"] - slope*predict[up,"dist"]
predict_a <- predict %>% 
  filter(dist > predict[down,"dist"] & dist < predict[up,"dist"])
predict_b <- predict %>% 
  filter(dist > predict[up,"dist"] | dist < predict[down,"dist"])
predict_a$ele_fit <- slope*predict_a$dist + b
predict <- rbind(predict_a,predict_b)
rm(df_prediction_a,predict_b)


## there are problems in the middle too. 

up <- which.min(abs(predict$dist-333.8035))
down <- which.min(abs(predict$dist-274.2532))

slope <- (predict[down,"ele_fit"] - predict[up,"ele_fit"])/(predict[down,"dist"] - predict[up,"dist"])
b = predict[up,"ele_fit"] - slope*predict[up,"dist"]
predict_a <- predict %>% 
  filter(dist > predict[down,"dist"] & dist < predict[up,"dist"])
predict_b <- predict %>% 
  filter(dist > predict[up,"dist"] | dist < predict[down,"dist"])
predict_a$ele_fit <- slope*predict_a$dist + b
predict <- rbind(predict_a,predict_b)
rm(predict_a,predict_b)


## there are problems in the middle too. 

up <- which.min(abs(predict$dist-433.8057))
down <- which.min(abs(predict$dist-424.8035))

slope <- (predict[down,"ele_fit"] - predict[up,"ele_fit"])/(predict[down,"dist"] - predict[up,"dist"])
b = predict[up,"ele_fit"] - slope*predict[up,"dist"]
predict_a <- predict %>% 
  filter(dist > predict[down,"dist"] & dist < predict[up,"dist"])
predict_b <- predict %>% 
  filter(dist > predict[up,"dist"] | dist < predict[down,"dist"])
predict_a$ele_fit <- slope*predict_a$dist + b
predict <- rbind(predict_a,predict_b)
rm(predict_a,predict_b)


## there are problems in the middle too. 

up <- which.min(abs(predict$dist-4103.701))
down <- which.min(abs(predict$dist-512.9065))

slope <- (predict[down,"ele_fit"] - predict[up,"ele_fit"])/(predict[down,"dist"] - predict[up,"dist"])
b = predict[up,"ele_fit"] - slope*predict[up,"dist"]
predict_a <- predict %>% 
  filter(dist > predict[down,"dist"] & dist < predict[up,"dist"])
predict_b <- predict %>% 
  filter(dist > predict[up,"dist"] | dist < predict[down,"dist"])
predict_a$ele_fit <- slope*predict_a$dist + b
predict <- rbind(predict_a,predict_b)
rm(predict_a,predict_b)

###slope check

predict <- predict[order(predict$dist),]

predict$slope <- NA
for(i in 1:nrow(predict)) {       # for-loop over rows
  predict$dist_down[i] <- predict$dist[i+1]
  predict$ele_down[i] <- predict$ele_fit[i+1]
}

predict$slope <- (predict$ele_fit - predict$ele_down)/(predict$dist - predict$dist_down)
predict$dist_down <- NULL
predict$ele_down <- NULL

df_predictionblah <- predict%>%filter(slope<0)


df_prediction_2 <- predict

check <- predict%>%drop_na(Date)

fig <- plot_ly(predict, x = ~dist, y = ~ele_fit, size = 1)
fig

```
take the loess spline and make a data frame that interpolates these data points

```{r bind df , echo=FALSE}
#save <- df_prediction

df_prediction <- rbind(df_prediction_1, df_prediction_2)
df_prediction$slope <- NULL

ggplot(data=df_prediction%>%drop_na(Flux_ave), aes(dist, ele_fit, color=Date)) +
  geom_point()

ggplot(data=df_prediction, aes(dist, ele_fit, col="CO2_ppm_ave")) +
  geom_point(size = 3, alpha = .5, color = "blue")

#df_prediction_2 <- predict

fig <- plot_ly(df_prediction, x = ~dist, y = ~ele_fit, size = 1)
fig

check <- df_prediction%>%drop_na(Date)

```

#reverse order
unfortunately gavi is going from downstream to up, and we want upstream to down. so reverse this order
you can't just reverse order the distance column because they are not collected at even intervals.

#loops below switch order of distance

```{r reverse, echo=FALSE}


df_prediction <- df_prediction[order(df_prediction$dist),]
df_prediction$dist_diff <- NA

for(i in 1:nrow(df_prediction)) {       # for-loop over rows
  if (i == 1) {
    df_prediction$dist_diff[i] <- 0
  } else {
    df_prediction[i,"dist_diff"] <-   df_prediction[i,"dist"] - df_prediction[i-1,"dist"]
  }
}

df_prediction <- df_prediction[order(-df_prediction$dist),]
df_prediction$dist_new <- NA
for(i in 1:nrow(df_prediction)) {       # for-loop over rows
  if (i == 1) {
    df_prediction$dist_new[i] <- 0
  } else {
    df_prediction[i,"dist_new"] <-   df_prediction[i,"dist_diff"] + df_prediction[i-1,"dist_new"]
  }
}

df_prediction <- df_prediction%>%filter(dist_new<350|dist_new>507.38)
df_prediction$X <-NULL
df_prediction$dist <- NULL
names(df_prediction)[names(df_prediction)=="dist_new"] <- "dist"

check <- df_prediction%>%drop_na(Date)

#loosing a synop point in the next chunk
```

#calcualte slope
here we calculate slope from the sample point and upstream 50m

```{r calc slope, echo=FALSE}

###
df_prediction <- df_prediction[order(df_prediction$dist),]
df_prediction$slope50m <- NA
loop <- df_prediction%>%drop_na(ele_fit)
for(i in 1:nrow(loop)) {       # for-loop over rows
  x = loop$dist[i] - 50
  loop$ele_minus[i] <- loop[which.min(abs(loop$dist-x)),]$ele_fit
  loop$dist_minus[i] <- loop[which.min(abs(loop$dist-x)),]$dist
  
  y = loop$dist[i] + 0
  loop$ele_plus[i] <- loop[which.min(abs(loop$dist-y)),]$ele_fit
  loop$dist_plus[i] <- loop[which.min(abs(loop$dist-y)),]$dist
  
  loop$slope50m <- (loop$ele_minus-loop$ele_plus)/(loop$dist_minus-loop$dist_plus)
  
}
loop$dist_minus <- NULL
loop$dist_plus <- NULL
loop$ele_minus <- NULL
loop$ele_plus <- NULL

df_prediction <- loop 
check <- df_prediction%>%drop_na(Date)
```
#plot

```{r write, echo=FALSE}
fig <- plot_ly(df_prediction%>%drop_na(Date), x = ~dist, y = ~ele_fit, size = 1)
fig
fig <- plot_ly(df_prediction%>%drop_na(Date), x = ~dist, y = ~slope50m, size = 1)
fig
```

```{r write, echo=FALSE}
check <- df_prediction%>%drop_na(Date)
df_prediction <- df_prediction%>%filter(dist_diff!=0)
check <- df_prediction%>%drop_na(Date)
##check should have 37 points again
#write.csv(df_prediction, here::here("ProcessedData/GAVI_synoptic_2022-06-04.csv"))
```

