---
title: "SynopFigures_2022-04-20"
author: "Kriddie"
date: '2024-02-10'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(readr)
library(tidyr) # for `gather`
library(ggplot2)
library(cowplot)
library(tidyverse)
library(rstatix)
library(ggpubr)
library(plotly)
library(gridExtra)
library(grid)
library(ggmap)
library(dplyr)
library(scales)
library(olsrr)
library(lme4)
library(viridis)

#register_stadiamaps(key = "4c9564bd-71e6-4396-8cef-e76e893129ce", write = TRUE)

#new api
register_stadiamaps("e723ef39-9560-41be-969c-36870f7b7f84", write = TRUE)

library(scales)


```

## Description
This file is to generate figures for my synoptic paper

*Objective:*
The objective of this study is to identify high resolution spatial patterns in pCO2, CO2 flux and geomorphology within a Paramo river network.

Hypothesis 1: Off-gassing from upstream reaches and decreased connection with groundwater will result in decreasing pCO2 within a river reach from upstream to downstream and within a river network from smaller to larger streams. 

Hypothesis: 2: Higher turbulence in larger streams will yield flux rates than smaller streams




#read in data


```{r read in data}


synop_allsites <- read.csv(here::here("ProcessedData/synop_allsites_slope.csv"))

synop_allsites_nowetland <- read.csv(here::here("ProcessedData/synop_allsites_nowetland_slope.csv"))

XWD_allsites <- read.csv(here::here("ProcessedData/xwd_allsites_slope.csv"))
XWD_allsites[XWD_allsites$site=="GaviTrib1", "site_2"] <- "GaviTribs"
XWD_allsites[XWD_allsites$site=="GaviTrib2", "site_2"] <- "GaviTribs"
XWD_allsites[XWD_allsites$site=="GaviTrib3", "site_2"] <- "GaviTribs"


Q_df <- read.csv(here::here("ProcessedData/Q_synop.csv"))

#k600_df_1 <- read.csv(here::here("ProcessedData/AllSynoptic_raymondk600_Oct5.csv"))%>%drop_na(k600_eq1_final)%>%filter(site!="GaviTrib3")

k600_df <- read.csv(here::here("ProcessedData/AllSynoptic_raymondk600_Oct8.csv"))%>%drop_na(k600_eq1_final)%>%filter(site!="GaviTrib3")

```

#random analysis for use in discussion

```{r random data}

#result 71% evaded in 100m antenas
ante_test <- synop_allsites%>%filter(site=="Ante")
(5341.6114-1578.6861)/5341.6114
#result 80% evaded in 100m gavi trib1
GaviTrib1_test <- synop_allsites%>%filter(site=="GaviTrib1")
(11098.654-1924.716)/11098.654

#result 69$in 50m
GaviTrib3_test <- synop_allsites%>%filter(site=="GaviTrib3")
(5841.548-1814.662)/5841.548
```

#i need to address slope v k600

```{r some stats}
stat_explore <- k600_df%>%drop_na(slope_mid)

min(stat_explore$slope_mid)/max(stat_explore$slope_mid)*100
min(stat_explore$v_ms)/max(stat_explore$v_ms)*100
min(stat_explore$depth)/max(stat_explore$depth)*100

V<-1
S<-1
D<-1
#all 1
all_1 <- (V*S)^0.89*D^0.54*5037
#V is 2
V<-2
V_2 <- (V*S)^0.89*D^0.54*5037
V_effect <- (V_2 -all_1 )/V_2

#S is 2
V<-1
S <- 2
S_2 <- (V*S)^0.89*D^0.54*5037
S_effect <- (S_2 - all_1 )/S_2

#D is 2
S<-1
D <- 2
D_2 <- (V*S)^0.89*D^0.54*5037
D_effect <- (D_2 - all_1 )/D_2

#model

model3 <- lm(log1p(catchment_ha)~ log1p(slope_mid), data = k600_df)
summary(model3)


# plot slope v k600
 
p <- ggplot(k600_df,aes(x=catchment_ha,y=slope_mid)) +
  geom_point(fill="orange",shape=21,size=3)  +
 # geom_smooth(method='lm',color="black")+ 
  scale_x_continuous(transform = "log1p",breaks=c(3,10,30,100,300))+ scale_y_continuous(transform = "log1p") +
  annotate("text", x=10, y=.4, label= expression(atop("p-value < 0.0001",paste(r^{2}," = 0.10"))),size=4) + xlab("Catchment size [ha]") + ylab("Slope [m/m]")


figure <- ggarrange(p, p2, ncol = 2)

```

#make a table that summerises CO2, k600 and flux

```{r table}
#use synop_allsites for CO2 because the other dataframe containes interpolates CO2 values
CO2_sum_table <- synop_allsites%>%drop_na(adjusted_ppm)%>%
  group_by(site)%>%
  summarise(
    mean_co2 = mean(adjusted_ppm,na.rm=TRUE),
    std_co2 = sd(adjusted_ppm,na.rm=TRUE),
    median_co2 = median(adjusted_ppm,na.rm=TRUE),
    min_co2 = min(adjusted_ppm,na.rm=TRUE),
    max_co2 = max(adjusted_ppm,na.rm=TRUE),
    Count = n()
  )

#use k600_df
k600_sum_table <- k600_df%>%
  group_by(site)%>%
  summarise(
    mean_k600 = mean(k600_eq1_final,na.rm=TRUE),
    std_k600 = sd(k600_eq1_final,na.rm=TRUE),
    median_k600 = median(k600_eq1_final,na.rm=TRUE),
    min_k600 = min(k600_eq1_final,na.rm=TRUE),
    max_k600 = max(k600_eq1_final,na.rm=TRUE),
    Count = n()
  )


#use k600_df
flux_sum_table <- k600_df%>%
  group_by(site)%>%
  summarise(
    mean_F = mean(F_mol_m2_d_eq1,na.rm=TRUE),
    std_F = sd(F_mol_m2_d_eq1,na.rm=TRUE),
    median_F = median(F_mol_m2_d_eq1,na.rm=TRUE),
    min_F = min(F_mol_m2_d_eq1,na.rm=TRUE),
    max_F = max(F_mol_m2_d_eq1,na.rm=TRUE),
    Count = n()
  )

```


#fig 1
this is a site map generated using arcpro, not included here

#fig 2
Show general downward trend in co2
river network and reach

#Stats

```{r Stats for fig 2a, echo=FALSE}


model_df <- synop_allsites%>%drop_na(adjusted_ppm)

#gavitrib1 is missing some x_pred
model_df[model_df$site=="GaviTrib1"& model_df$X==480, "x_pred"] <- 11.54219 - 3
model_df[model_df$site=="GaviTrib1"& model_df$X==481, "x_pred"] <- 11.54219
#gavitrib3 highest point is in the wrong location I think
model_df[model_df$site=="GaviTrib3"& model_df$X==528, "x_pred"] <- -17.68


#gavi rivernetwork vs catchment size

#antenas  cos v dist
model1 <- lm(log(adjusted_ppm)~ x_pred, data = model_df %>%filter(site=="Ante"))
summary(model1)

#gavi outlet cos v dist
model1 <- lm(log(adjusted_ppm) ~ x_pred, data = model_df %>%filter(site=="GaviDown"))
summary(model1)

#gavi trib 1  cos v dist
model1 <- lm(log(adjusted_ppm)~ x_pred, data = model_df %>%filter(site=="GaviTrib1"))
summary(model1)

#gavi trib 2  cos v dist
model1 <- lm(log(adjusted_ppm)~ x_pred, data = model_df %>%filter(site=="GaviTrib2"))
summary(model1)

#gavi trib 3  cos v dist
model1 <- lm(log(adjusted_ppm)~ x_pred, data = model_df %>%filter(site=="GaviTrib3"))
summary(model1)

#colm  co2 v dist
model1 <- lm(log(adjusted_ppm)~ x_pred, data = model_df %>%filter(site=="Colm"))
summary(model1)

#gavi inlet cos v dist
model1 <- lm(log(adjusted_ppm)~ x_pred, 
             data = model_df %>%filter(site=="GaviUp"))
summary(model1)


```



#stats to report:

*co2 v distance*
Gavi outlet p-value= 0.000001103, r2 = 0.6525  *
Gavi trib1 p-value= 0.0252, r2 = 0.3223 *
Gavi trib2 p-value= 0.1135, r2 = 0.6789 
Gavi trib3 p-value= 0.05204, r2 = 0.565 .
ANTE p-value = 0.0113, r2 = 0.2817 *

Gavi inlet p-value= 0.885, r2 = -0.08875
colm p-value = 0.5208, r2 = -0.02103

pannel 2c got really complicated. Below is code for all the different componenets, and then I brought it into a power point to finish it up

```{r fig 2a, echo=FALSE}

model_df_original<- read_csv(here::here("ProcessedData/ALLSYNOPDATA_FINAL_2024-05-07.csv"))%>%rename(adjusted_ppm=pCO2_ppm)%>%drop_na(adjusted_ppm)

model_df <- model_df[order(model_df$adjusted_ppm),]
#?get_stadiamap()

#stadium maps

gaviplot_1 <- qmplot(lon_fit, lat_fit, data = model_df_original%>%
                   filter(Wetland_3=="Gavilan River Network")%>%
    drop_na(adjusted_ppm),size= 6, maptype = "stamen_terrain", color = log10(adjusted_ppm)) +
  scale_color_gradient(low="blue", high="red",
                       breaks=c(log10(300),log10(1000), log10(3000), log10(10000)), labels=c("300","1,000","3,000","10,000"))+
    guides(size = "none") +
  theme(legend.text=element_text(size=14)) + 
  labs(color=expression(paste(italic('p'),"CO"[2] ," [ppm]"))) + theme(legend.title=element_text(size=16), 
    legend.text=element_text(size=14)) 


gaviplot_2 <- qmplot(lon_fit, lat_fit, data = df_original%>%
                   filter(Wetland_2!="Gavilan Tributaries")%>%
    drop_na(adjusted_ppm),size= 1, maptype = "stamen_terrain", color = log10(adjusted_ppm)) +
  scale_color_gradient(low="blue", high="red", breaks=c(log10(300),log10(1000), log10(3000), log10(10000)), labels=c("300","1,000","3,000","10,000"))+
    guides(size = "none") +
  theme(legend.text=element_text(size=14)) + 
  labs(color=expression(paste(italic('p'),"CO"[2] ," [ppm]"))) + theme(legend.title=element_text(size=16), 
    legend.text=element_text(size=14)) 


### c.
#make it so that every reach starts at 1
model_df[model_df$site == 'GaviTrib3',]$x_pred <- 
  model_df[model_df$site == 'GaviTrib3',]$x_pred + 17.680000
model_df[model_df$site == 'GaviTrib2',]$x_pred <- 
  model_df[model_df$site == 'GaviTrib2',]$x_pred-1.293002
model_df[model_df$site == 'GaviTrib1',]$x_pred <- 
  model_df[model_df$site == 'GaviTrib1',]$x_pred-8.542190000
model_df[model_df$site == 'GaviDown',]$x_pred <- 
  model_df[model_df$site == 'GaviDown',]$x_pred-1.579386786
model_df[model_df$site == 'Colm',]$x_pred <- 
  model_df[model_df$site == 'Colm',]$x_pred-2.774599164
model_df[model_df$site == 'GaviUp',]$x_pred <- 
  model_df[model_df$site == 'GaviUp',]$x_pred-3.128488862
model_df[model_df$site == 'Ante',]$x_pred <- 
  model_df[model_df$site == 'Ante',]$x_pred-17.184206210


#annotate text 
dat_text <- data.frame(
  label = c("p-value = 0.011", "p-value < 0.0001", 
            "p-value = 0.025","p-value = 0.11","p-value = 0.05"),
  site   = c("Ante", "GaviDown", "GaviTrib1", "GaviTrib2", "GaviTrib3"))

site_names <- c("Ante" = "Antenas",
                "GaviDown" = "Gavil\u00e1n Outlet",
                "GaviTrib1" = "Tributary 1",
                "GaviTrib2" = "Tributary 2",
                "GaviTrib3" = "Tributary 3")

p2 <- ggplot(model_df%>%filter(site!="GaviUp")%>%filter(site!="Colm")#%>%filter(Wetland!="GAVItrib3")
             , aes(x = x_pred, y = adjusted_ppm)) +
  geom_point(size=3) +  
  facet_grid(site~.,labeller = as_labeller(site_names)) + geom_smooth(method='lm')+
  ylab(expression(paste(italic('p'),"CO"[2] ," [ppm]"))) + xlab("Distance downstream [m]") +
  theme_bw() +
  scale_y_continuous(trans = "log10", breaks=c(300,1000,3000,10000), labels=c("300","1,000","3,000","10,000")) +  theme(text = element_text(size = 14)) 

p3 <- p2 + geom_text(
  data    = dat_text,
  mapping = aes(x = 400, y = 9000, label = label))




df1 <- model_df%>%filter(site=="Ante"|site=="GaviDown"|site=="GaviTrib1"|site=="GaviUp"|site=="Colm")

df1$adjusted_ppm[df1$site == "Ante"] <- NA
df1$adjusted_ppm[df1$site == "GaviDown"] <- NA
df1$adjusted_ppm[df1$site == "GaviTrib1"] <- NA


site_names <- c("Ante" = "Antenas",
                      "GaviDown" = "Gavil\u00e1n Outlet",
                "GaviTrib1" = "gavitrib1",
                      "GaviUp" = "Gavil\u00e1n Intlet",
                      "Colm" = "Colmillo")


p4 <- ggplot(df1, aes(x = x_pred, y = adjusted_ppm)) +
  geom_point(size=3) + 
  facet_grid(site~.,labeller = as_labeller(site_names)) +
  ylab(expression(paste(italic('p'),"CO"[2] ," [ppm]"))) + xlab("Distance downstream [m]") +
  theme_bw() +
  scale_y_continuous(trans = "log10", breaks=c(300,1000,3000), labels=c("300","1,000","3,000")) +
  expand_limits(y = c(200, 4000)) + 
  theme(text = element_text(size = 14))


#annotate text 
dat_text2 <- data.frame(
  label = c("", "", "" ,
            "p-value = 0.89","p-value = 0.52"),
  site   = c("Ante", "GaviDown", "GaviTrib1", "GaviUp","Colm"))

p5 <- p4 + geom_text(
  data    = dat_text2,
  mapping = aes(x = 900, y = 3000, label = label),
)


figure1 <- ggarrange(gaviplot_1, gaviplot_2, ncol = 2)
figure2 <- ggarrange(p3, p5, ncol = 2)

```


Box plots
```{r fig 4 boxplots, echo=FALSE}

k600_df <- read.csv(here::here("ProcessedData/AllSynoptic_raymondk600_Oct8.csv"))%>%drop_na(k600_eq1_final)%>%filter(site!="GaviTrib3")

synop_allsites$site_2 <- synop_allsites$site
synop_allsites[synop_allsites$site=="GaviTrib1", "site_2"] <- "GaviTribs"
synop_allsites[synop_allsites$site=="GaviTrib2", "site_2"] <- "GaviTribs"
synop_allsites[synop_allsites$site=="GaviTrib3", "site_2"] <- "GaviTribs"

synop_allsites_sub <- synop_allsites%>%dplyr::select(site_2,adjusted_ppm)%>%rename(value=adjusted_ppm)%>%drop_na(value)
synop_allsites_sub$variable <- "co2"

k600_df$site_2 <- k600_df$site
k600_df[k600_df$site=="GaviTrib1", "site_2"] <- "GaviTribs"
k600_df[k600_df$site=="GaviTrib2", "site_2"] <- "GaviTribs"
k600_df[k600_df$site=="GaviTrib3", "site_2"] <- "GaviTribs"

k600_df_sub1 <- k600_df%>%dplyr::select(site_2,k600_eq1_final)%>%rename(value=k600_eq1_final)%>%drop_na(value)
k600_df_sub1$variable <- "k600_eq1_final"
k600_df_sub2 <- k600_df%>%dplyr::select(site_2,F_mol_m2_d_eq1)%>%rename(value=F_mol_m2_d_eq1)%>%drop_na(value)
k600_df_sub2$variable <- "F_mol_m2_d_eq1"

df_sub <- rbind(synop_allsites_sub,k600_df_sub1,k600_df_sub2)

df_sub$variable = factor(df_sub$variable, levels=c('co2','k600_eq1_final','F_mol_m2_d_eq1'))

#create labels

#specify labels for plot
df_sub$site_3 <- factor(df_sub$site_2,levels = c("GaviTribs","Ante", "GaviUp", "GaviDown", "Colm"))
df_sub$site_3 <- factor(df_sub$site_2,levels = c("GaviTribs","Ante", "GaviUp", "GaviDown", "Colm"))

my_labels <- c('Tribs', 'Antenas', 'Gavil\u00e1n Inlet', 'Gavil\u00e1n Outlet','Colmillo')

# Basic scatter plot

f_names <- list(co2 = expression(paste(italic('p'),"CO"[2]," [ppm]")), 
                k600_eq1_final = expression(paste(italic('k')[600]," [m ", d^-1,"]")), 
                F_mol_m2_d_eq1 = expression(paste(" Evasion [ mol ", m^-2, d^-1,"]"))
              )
f_labeller <- function(variable, value){return(f_names[value])}

#annotate for significance

ann_text <- read.csv(here::here("KriddieFolder/annotation_boxplots_letters.csv"))
ann_text$site_3 <- as.factor(ann_text$site_2)
ann_text$variable <- as.factor(ann_text$variable)
ann_text$Label <- as.factor(ann_text$Label)
ann_text$value <- as.numeric(ann_text$value)


##plots

p <- ggplot(df_sub,
            aes(x=site_3, y=value)) 

air_ppm <- mean(k600_df$pCO2_air_atm)*1000000
p1 <- p +  facet_grid(rows = vars(variable),labeller = f_labeller,scales = "free")  +
#  geom_hline(yintercept=1.0, linetype="dotdash", color = "black", size=1) +
  geom_boxplot(outlier.shape = NA,fill="grey") +
  geom_jitter(shape=18,position=position_jitter(0.1)) +
  geom_hline(data = df_sub %>% filter(variable == "co2"),
             aes(yintercept = air_ppm), col = "red", linetype = 2, linewidth=1) +
  theme_bw(base_size = 16) +
  stat_summary(fun = "mean", geom = "point", shape = 23, size = 3,fill="red") +
  scale_y_continuous(name="",
                     transform="log1p", 
                     breaks=c(1,3,10,30,100,300,1000,3000,10000), 
                     labels=c("1","3","10","30","100","300","1,000","3,000","10,000"))+
  scale_x_discrete(labels=my_labels) + xlab("")+ theme(axis.text.x = element_text(angle = 25, vjust = 1, hjust=1))


p2 <- p1 + 
  geom_text(aes(x=site_2, y=value, label=Label, group=NULL),data=ann_text)  
  
#stats
anova.co2 <- aov(log(adjusted_ppm) ~ site_2, data = synop_allsites)
summary(anova.co2)
tukey.co2<-TukeyHSD(anova.co2)
tukey.co2

anova.k600 <- aov(log(k600_eq1_final) ~ site_2, data = k600_df)
summary(anova.k600)
tukey.k600<-TukeyHSD(anova.k600)
tukey.k600

anova.flux <- aov(log1p(F_mol_m2_d_eq1) ~ site_2, data = k600_df)
summary(anova.flux)
tukey.flux<-TukeyHSD(anova.flux)
tukey.flux

anova.flux2 <- aov(log1p(F_CO2_molperd_eq1) ~ site_2, data = k600_df)
summary(anova.flux2)
tukey.flux2<-TukeyHSD(anova.flux2)
tukey.flux2

```

#hydraulic geometry plots

```{r hydro geometry plots}
#first plot w v catchment
XWD_allsites$legend_item <- "black"
options(scipen = 999)

model_Q <- lm(log(Q_m3s) ~ log(catchment_ha), data = Q_df)
summ_model_Q <- summary(model_Q)

p_Q <- ggplot(Q_df,aes(x=catchment_ha,y=Q_m3s*1000,color="black")) + geom_point(size=3) + scale_y_log10() + scale_x_log10() +
  geom_smooth(method='lm', formula= y~x,color="black") +
  ylab(expression(paste("Discharge [L ",s^-1, "]"))) + xlab("Catchment size [ha]") +
    scale_color_manual(values = c("black")) +
  annotate("text", x=5, y=50, label= expression(atop("p-value = < 0.0001",paste(r^{2}," = 0.7"))),size=4) +
  theme_bw(base_size = 16)

model_w <- lm(log(w) ~ log(catchment_ha)  , data = XWD_allsites)
summ_model_w <- summary(model_w)

p_width <- ggplot(XWD_allsites,aes(x=catchment_ha,y=w,color=legend_item)) + geom_point(size=3) +
  geom_smooth(method='lm', formula= y~x,color="black") + 
  ylab("Width [cm]") + xlab("Catchment size [ha]") +
   scale_y_continuous(trans = "log10", 
                      breaks=c(10,100,1000), 
                      labels=c("10","100","1,000")) +
  scale_x_continuous(trans = "log10", limits = c(.1,200)) +
  scale_color_manual(values = c("black")) +
  annotate("text", x=1, y=700, label= expression(atop("p-value = < 0.0001",paste(r^{2}," = 0.34"))),size=4) + 
  theme_bw(base_size = 16)

model_d <- lm(log(d) ~ log(catchment_ha) + log1p(slope_mid), data = XWD_allsites)
summ_model_d <-summary(model_d)

p_depth <- ggplot(XWD_allsites%>%drop_na(slope_mid),aes(x=catchment_ha,y=d,fill=log1p(slope_mid))) + geom_point(size=3,shape=21) +
  scale_y_log10() + scale_x_continuous(trans = "log10", limits = c(.1,200)) +
  geom_smooth(method='lm', formula= y~x,color="black")+ 
  ylab("Depth [cm]") + xlab("Catchment size [ha]") + 
  annotate("text", x=1, y=100, label= expression(atop("p-value = < 0.0001",paste(r^{2}," = 0.50"))),size=4) +
 # scale_fill_gradient(low = "yellow", high = "darkgreen", na.value = NA) +
  theme_bw(base_size = 16)+ scale_fill_continuous(low = "yellow", high = "darkgreen", na.value = NA,name="Slope [m/m]", labels=c(0,.1,.2,.3,.4),  breaks=c(0,log1p(.1),log1p(.2),log1p(.3),log1p(.4)))
  labs(fill="Slope \n (log1p)")


p_full <- ggarrange(p_Q, p_width, ncol = 2, nrow = 1)



model_co2 <- lm(log(adjusted_ppm) ~ log(catchment_ha) + log1p(slope_up), data = synop_allsites%>%drop_na(slope_up))
summ_model_co2 <- summary(model_co2)

p_co2 <- ggplot(synop_allsites%>%drop_na(slope_up),aes(x=catchment_ha,y=adjusted_ppm,fill=slope_up)) + 
  geom_point(size=3,shape=21) + scale_y_log10() + scale_x_log10()+ 
  geom_smooth(method='lm', formula= y~x,color="black")+
  scale_fill_continuous(low = "yellow", high = "darkgreen", na.value = NA,name="Slope [m/m]", labels=c(0,.3,.6,1),  breaks=c(0,log1p(.3),log1p(.6),log1p(1))) +  annotate("text", x=8, y=10000, label= expression(atop("p-value = < 0.0001",""#paste(r^{2}," = 0.27")
                                                                                                    )),size=4) +
  ylab(expression(italic(p)~CO[2] ~'[ppm]')) + xlab("") + xlab("Catchment size [ha]") + 
  theme_bw(base_size = 16)+
  labs(fill="Slope \n (log1p)")

model_co2_nowetland <- lm(log(adjusted_ppm) ~ log(catchment_ha) + log1p(slope_up), data = synop_allsites_nowetland%>%drop_na(slope_up))
summ_model_co2_nowetland <- summary(model_co2_nowetland)

summ_model_co2_nowetland <-summary(model_co2_nowetland)
p_co2_nowetland <- ggplot(synop_allsites_nowetland%>%drop_na(slope_up),aes(x=catchment_ha,y=adjusted_ppm,fill=slope_up)) + 
  geom_point(size=3,shape=21) + scale_y_log10() + scale_x_log10()+ 
  geom_smooth(method='lm', formula= y~x,color="black")+
  scale_fill_gradient(low = "yellow", high = "darkgreen", na.value = NA) +
  annotate("text", x=1, y=10000, label= expression(atop("p-value = < 0.001",paste(r^{2}," = 0.42"))),size=4) +
  ylab(expression(italic(p)~CO[2] ~'(ppm)')) + xlab("") + xlab("Catchment size (ha)") +
  theme_bw(base_size = 16)



```




#plot


```{r bball fig, echo=FALSE}
#df1 <- read.csv(here::here("ProcessedData/raymond_data_allsites_2024-09-16.csv"))

df <- read.csv(here::here("ProcessedData/CumulativeFlux_raymondk600_Oct8.csv"))

df$name <- factor(df$name, levels=c("Ante", "Colm","GaviUp", "GaviDown","GaviTrib1","GaviTrib2","GaviTrib3"))

bball <- ggplot(df, aes(x=x, y=flux_sum, group=name)) +
  geom_line(aes(color=name), linewidth=3) +
  geom_point(aes(fill=name), size=1,shape=1)+
    ylab(expression(paste("Cumulative CO"[2]," evasion [mol ", day^-1,"]"))) +
  xlab("Distance [m]") + 
  scale_color_discrete(name = "Stream Reach", labels = c("Antenas", "Colmillo", 'Gavil\u00e1n Inlet', "Gavil\u00e1n Outlet", "Gavil\u00e1n Tributary 1", "Gavil\u00e1n Tributary 2"))+ 
  scale_fill_discrete(name = "Stream Reach", labels = c("Antenas", "Colmillo", 'Gavil\u00e1n Inlet', "Gavil\u00e1n Outlet", "Gavil\u00e1n Tributary 1", "Gavil\u00e1n Tributary 2")) +
  theme_bw(base_size = 20) + theme(legend.position="none")

bball

#zoom in
bball_zoom <- ggplot(df, 
                     aes(x=x, y=flux_sum, group=name)) +
  geom_line(aes(color=name), linewidth=3) +
  geom_point(aes(fill=name), size=1,shape=1)+
    ylab(expression(paste("Cumulative CO"[2]," evasion [mol ", day^-1,"]"))) +
  xlab("Distance [m]")  +
    guides(fill=FALSE) +
  scale_color_discrete(name = "Stream Reach", labels = c("Antenas", "Colmillo", 'Gavil\u00e1n Inlet', "Gavil\u00e1n Outlet", "Gavil\u00e1n Tributary 1", "Gavil\u00e1n Tributary 2"))+ 
  scale_fill_discrete(name = "Stream Reach", labels = c("Antenas", "Colmillo", 'Gavil\u00e1n Inlet', "Gavil\u00e1n Outlet", "Gavil\u00e1n Tributary 1", "Gavil\u00e1n Tributary 2")) +
  xlim(-10, 300) +
  ylim(-20, 500) +
   theme_bw(base_size = 16) 


#ggarrange(bball_zoom,legend = "none")

#write.csv(df_test,here::here("ProcessedData/bball_dataframe.csv"))

```



```{r upscale flux bin, echo=FALSE}
#make some plots right quick, bin data
df <- read.csv(here::here("ProcessedData/upscaleFlux_allwatersheds_oct18.csv"))
df_justtomakesure <- df%>%filter(catchment_ha>=1) 


df_bin5 <- df_justtomakesure%>% mutate(new_bin = cut(log(catchment_ha), breaks=5))
df_bin5$cathment_name <- factor(df_bin5$cathment_name, levels = c("ante", "gavi", "colm"))

z_score_break <- 500

df_bin5$z_score <- (df_bin5$F_CO2_molperd_eq1-mean(df_bin5$F_CO2_molperd_eq1))/sd(df_bin5$F_CO2_molperd_eq1)
z_score_toremove <- df_bin5%>%filter(z_score>=z_score_break|z_score<=-z_score_break)

bin5_summ <- df_bin5%>%group_by(new_bin)%>%
  summarise(co2_mean=mean(co2),
            k600_mean = mean(k600_eq1_final),
            flux_m2d = mean(F_mol_m2_d_eq1),
            flux_d = mean(F_CO2_molperd_eq1))

air_ppm <- mean(df_bin5$pCO2_air_atm*10^6)

p1 <-ggplot(data=df_bin5%>%filter(z_score<z_score_break&z_score>-z_score_break), aes(x=new_bin, y=co2,fill=cathment_name)) +
    geom_boxplot(outlier.shape=21,outlier.size = 1.25,outlier.alpha = .5#outlier.shape = NA
    ) + 
   geom_hline(yintercept=air_ppm, color="red",linetype="dashed") +
     stat_summary(fun = "mean", geom = "point", shape = 23, size = 3, color = "black",fill="red") + 

  scale_y_continuous(transform ="log",breaks=c(1,3,10,30,100,300,1000,3000)) +
  scale_x_discrete(name="Catchment size [ha]", labels = c('[1.0 - 2.9]','[2.9 - 8.4]','[8.4 - 24.0]','[24.0 - 69.2]','[107 - 202]')) +
  scale_fill_manual(name = "Catchment", labels = c("Antenas", 'Gavil\u00e1n',"Colmillo"),values=c("#efedf5", "#bcbddc", "#756bb1")) +
  ylab(expression(italic(p)~CO[2] ~'[ppm]')) +
  theme_bw(base_size = 16)+ theme(axis.text.x = element_text(angle = 25, vjust = 1, hjust=1))


p2 <-ggplot(data=df_bin5%>%filter(z_score<z_score_break & z_score>-z_score_break), aes(x=new_bin, y=k600_eq1_final,fill=cathment_name)) + 
  scale_y_continuous(transform ="log",breaks=c(3,10,30,100,300,1000)) +
  geom_boxplot(outlier.shape=21, outlier.size = 1.25, outlier.alpha = .5
    ) + 
       stat_summary(fun = "mean", geom = "point", shape = 23, size = 3, color = "black",fill="red") +
  scale_x_discrete(name="Catchment size [ha]", labels = c('[1.0 - 2.9]','[2.9 - 8.4]','[8.4 - 24.0]','[24.0 - 69.2]','[107 - 202]')) +    scale_fill_manual(name = "Catchment", labels = c("Antenas", 'Gavil\u00e1n',"Colmillo"),values=c("#efedf5", "#bcbddc", "#756bb1")) +
  ylab(expression(paste(italic('k')[600]," [m ", d^-1,"]"))) +
  theme_bw(base_size = 16)+ theme(axis.text.x = element_text(angle = 25, vjust = 1, hjust=1))


p3 <-ggplot(data=df_bin5%>%filter(z_score<z_score_break & z_score>-z_score_break), aes(x=new_bin, y=F_mol_m2_d_eq1,fill=cathment_name)) +
   geom_boxplot(outlier.shape=21,outlier.size = 1.25,outlier.alpha = .5
    ) +   
  stat_summary(fun = "mean", geom = "point", shape = 23, size = 3, color = "black",fill="red") +
  scale_x_discrete(name="Catchment size [ha]", labels = c('[1.0 - 2.9]','[2.9 - 8.4]','[8.4 - 24.0]','[24.0 - 69.2]','[107 - 202]')) +
    scale_fill_manual(name = "Catchment", labels = c("Antenas", 'Gavil\u00e1n',"Colmillo"),values=c("#efedf5", "#bcbddc", "#756bb1")) +
    ylab(expression(paste(CO[2]," Evasion [mol ",m^-2," ", d^-1,"]"))) + scale_y_continuous(transform="log1p",breaks = c(1,3,10),limits =c(0,20)
      ) +
  theme_bw(base_size = 16)+ theme(axis.text.x = element_text(angle = 25, vjust = 1, hjust=1))


p4 <-ggplot(data=df_bin5%>%filter(z_score<z_score_break & z_score>-z_score_break), aes(x=new_bin, y=F_CO2_molperd_eq1,fill=cathment_name)) +
   geom_boxplot(outlier.shape=21,outlier.size = 1.25,outlier.alpha = .5) +
  stat_summary(fun = "mean", geom = "point", shape = 23, size = 3, color = "black",fill="red") +
  scale_x_discrete(name="Catchment size [ha]", labels = c('[1.0 - 2.9]','[2.9 - 8.4]','[8.4 - 24.0]','[24.0 - 69.2]','[107 - 202]')) +
    scale_fill_manual(name = "Catchment", labels = c("Antenas", 'Gavil\u00e1n',"Colmillo"),values=c("#efedf5", "#bcbddc", "#756bb1")) + scale_y_continuous(transform="log1p",breaks = c(1,3,10,30,100),limits = c(0,30)
      ) +
    ylab(expression(paste(CO[2]," Evasion [mol ", d^-1,"]"))) +
  theme_bw(base_size = 16)+ theme(axis.text.x = element_text(angle = 25, vjust = 1, hjust=1))


p_full <- ggarrange(p1, p2, p3,p4,  common.legend = TRUE, legend="top")

p_full_1 <- ggarrange(p1+ rremove("xlab")+ rremove("x.text"), p2+ rremove("xlab")+ rremove("x.text"),  common.legend = TRUE, legend="top")

p_full_2 <- ggarrange(p3,p4,  common.legend = TRUE, legend="none")

figure <- ggarrange(
  p1 + rremove("xlab")+ rremove("x.text"),
  p2 + rremove("xlab") + rremove("x.text"),
  p3,
  p4, # remove axis labels from plots
                    labels = NULL,
                    ncol = 2, nrow = 2,
                    common.legend = TRUE, legend = "top",
                    align = "hv", 
                    font.label = list(size = 10, color = "black", face = "bold", family = NULL, position = "top"))

annotate_figure(figure, left = textGrob("Common y-axis", rot = 90, vjust = 1, gp = gpar(cex = 1.3)),
                    bottom = textGrob("Common x-axis", gp = gpar(cex = 1.3)))

```


```{r upscale flux map, echo=FALSE}

df <- read.csv(here::here("ProcessedData/upscaleFlux_allwatersheds_oct18.csv"))
#df <- read.csv(here::here("ProcessedData/upscaleFlux_allwatersheds_oct8.csv"))
df$cathment_name <- factor(df$cathment_name, levels = c("ante", "gavi", "colm"))

df_bin5 <- df%>%filter(catchment_ha>=1) %>% mutate(new_bin = cut(log10(catchment_ha), breaks=5))
df_bin5$cathment_name <- factor(df_bin5$cathment_name, levels = c("ante", "gavi", "colm"))


z_score_break <- 100

df_bin5$z_score <- (df_bin5$F_CO2_molperd_eq1-mean(df_bin5$F_CO2_molperd_eq1))/sd(df_bin5$F_CO2_molperd_eq1)
z_score_toremove <- df_bin5%>%filter(z_score>=z_score_break|z_score<=-z_score_break)


df_bin5$z_score <- (df_bin5$F_CO2_molperd_eq1-mean(df_bin5$F_CO2_molperd_eq1))/sd(df_bin5$F_CO2_molperd_eq1)

histogram <- df_bin5%>%filter(catchment_ha>=1)%>%
  ggplot( aes(x=catchment_ha, fill=cathment_name)) +
    geom_histogram( color="black", position = 'identity',bins = 10) +
    theme_classic(base_size = 14) +
    labs(fill="")+ xlab("Catchment size [ha]") + #scale_y_continuous(breaks=c(0,2000,4000)) +
  scale_x_continuous(transform = "log",breaks=c(1,3, 10,30,100,300)) +
  scale_fill_manual(name = "Catchment", labels = c("Antenas", 'Gavil\u00e1n',"Colmillo"),values=c("#efedf5", "#bcbddc", "#756bb1")) +
  facet_grid(rows=vars(cathment_name))+ 
theme(strip.background = element_blank(),
  strip.text.y = element_blank()) + 
  #theme(legend.position="right")+ 
  guides(fill="none")



df_bin5_summary <- df_bin5%>%
  filter(z_score<z_score_break & z_score>-z_score_break)%>%
  group_by(new_bin,cathment_name)%>%filter(catchment_ha>=1)%>%
  summarise(
    co2_mean = mean(co2,na.rm =TRUE),
    co2_sd = sd(co2,na.rm =TRUE),
    slope_mid_mean = mean(slope_mid,na.rm =TRUE),
    slope_mid_sd = sd(slope_mid,na.rm =TRUE),
    k600_eq1_mean = mean(k600_eq1_final,na.rm =TRUE),
    k600_eq1_sd = sd(k600_eq1_final,na.rm =TRUE),
    F_mol_m2_d_eq1_mean = mean(F_mol_m2_d_eq1,na.rm =TRUE),
        F_mol_m2_d_eq1_sd = sd(F_mol_m2_d_eq1,na.rm =TRUE),
    F_CO2_molperd_eq1_mean = mean(F_CO2_molperd_eq1,na.rm =TRUE),
        F_CO2_molperd_eq1_sd = sd(F_CO2_molperd_eq1,na.rm =TRUE),
    F_CO2_molperd_eq1_sum = sum(F_CO2_molperd_eq1,na.rm =TRUE))

barplot <-ggplot(data=df_bin5_summary, aes(x=new_bin, y=F_CO2_molperd_eq1_sum,fill=cathment_name)) +
geom_bar(stat="identity", color="black", position=position_dodge())+
    scale_x_discrete(name="Catchment size [ha]", labels = c('[9.0 - 16.6]','[16.6 - 40.0]','[40.0 - 57.5]','[57.5 - 107]','[107 - 199]')) +
  scale_fill_manual(name = "Catchment", labels = c("Antenas", 'Gavil\u00e1n',"Colmillo"),values=c("#efedf5", "#bcbddc", "#756bb1")) +
#   scale_fill_discrete(name = "", labels = c("Antenas", 'Gavil\u00e1n',"Colmillo")) +
    ylab(expression(paste("Total CO"[2]," evasion [mol ", day^-1,"]"))) +
  theme_minimal(base_size = 16)+ theme(axis.text.x = element_text(angle = 25, vjust = 1, hjust=1)) + 
  
    theme(legend.position="top")


df$code_names <- NA
df[df$F_CO2_molperd_eq1 <= 0,]$code_names <- "< 0"
df[df$F_CO2_molperd_eq1 > 1.12,]$code_names <- "> 1.12"
  



full <- ggarrange(histogram,barplot,ncol = 2,widths=c(.75,2),common.legend = TRUE,legend = "bottom")



```


```{r test plot, echo=FALSE}

ggplot(df_bin5, aes(x=catchment_ha, y= F_CO2_molperd_eq1, color=new_bin))  +geom_point() +scale_x_log10()

```



