---
title: "SynopFigures_2022-04-20"
author: "Kriddie"
date: '2024-02-10'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(readr)
library(tidyr) # for `gather`
library(ggplot2)
library(cowplot)
library(tidyverse)
library(rstatix)
library(ggpubr)
library(plotly)
library(gridExtra)
library(grid)
library(ggmap)
library(dplyr)
library(scales)

#register_stadiamaps(key = "4c9564bd-71e6-4396-8cef-e76e893129ce", write = TRUE)

#new api
register_stadiamaps("e723ef39-9560-41be-969c-36870f7b7f84", write = TRUE)

library(scales)

#extract hex color codes for a plot with three elements in ggplot2 
hex1 <- hue_pal()(1)
hex3 <- hue_pal()(3)
hex6 <- hue_pal()(6)
hex8 <- hue_pal()(8)

#display hex color codes


#antenas - 
antens <- hex1[1]
#gavilan
gavi <- hex3[3]
#gavilan inlet
gavi_in <- hex6[4]
#gavilan outlet
gavi_out <- hex6[5]
#gavilan trib1
gavitrib1 <- hex8[2]
#gavilan trib2
gavitrib2 <- hex8[3]
#gavilan trib3
gavitrib3 <- hex8[4]
#gavi tribs
gavitribs <- hex3[2]

#colmillo
colmillo <- hex8[8]
```

## Description
This file is to generate figures for my synoptic paper

*Objective:*
The objective of this study is to identify high resolution spatial patterns in pCO2, CO2 flux and geomorphology within a Paramo river network.

Hypothesis 1: Off-gassing from upstream reaches and decreased connection with groundwater will result in decreasing pCO2 within a river reach from upstream to downstream and within a river network from smaller to larger streams. 

Hypothesis: 2: Higher turbulence in larger streams will yield flux rates than smaller streams




#read in data


```{r read in data}
df<- read_csv(here::here("ProcessedData/ALLSYNOPDATA_FINAL_2024-02-10.csv"))

#total flux for gavi tribs to add to bball plota
Trib1 <- read.csv(here::here("ProcessedData/GAVItrib1_synopticGeom_2022-08-30.csv"))
Trib2 <- read.csv(here::here("ProcessedData/GAVItrib2_synopticGeom_2022-08-30.csv"))

#tribstuff
Trib1$Wetland <- "Tributary 1"
Trib2$Wetland <- "Tributary 2"
Tribs <- rbind(Trib1,Trib2)

```

#fig 1
this is a site map generated using arcpro, not included here

#fig 2
Show general downward trend in co2
river network and reach

#Stats

```{r Stats for fig 2a, echo=FALSE}

#gavi rivernetwork vs catchment size
model1 <- lm(log(adjusted_ppm)~ CatchmentSize_ha, 
             data = df %>%filter(Wetland_3=="Gavilan River Network"))
summary(model1)

#antenas  cos v dist
model1 <- lm(log(adjusted_ppm)~ dist, 
             data = df %>%filter(Wetland_2=="Antenas"))
summary(model1)
#gavi inlet cos v dist
model1 <- lm(log10(adjusted_ppm)~ dist, 
             data = df %>%filter(Wetland_4=="Gavilan Inlet"))
summary(model1)
#gavi outlet cos v dist
model1 <- lm(log10(adjusted_ppm)~ dist, 
             data = df %>%filter(Wetland_4=="Gavilan Outlet"))
summary(model1)

#gavi trib 1  cos v dist
model2 <- lm(log10(adjusted_ppm)~ dist, 
             data = df %>%filter(Wetland=="GAVItrib1"))
summary(model2)
#gavi trib 2  cos v dist
model3 <- lm(log10(adjusted_ppm)~ dist, 
             data = df %>%filter(Wetland=="GAVItrib2"))
summary(model3)

#gavi trib 3  cos v dist
model4 <- lm(log10(adjusted_ppm)~ dist, 
             data = df %>%filter(Wetland=="GAVItrib3"))
summary(model4)


```

#stats to report:
*Gavi river network v log c02*
pvalue = 2.875e-06, r2 = 0.3139 

*co2 v distance*
Gavi inlet p-value= 0.8892, r2 = -0.0889  
Gavi outlet p-value= 6.573e-06, r2 = 0.6102 * 
Gavi trib1 p-value= 0.02733, r2 = 0.313 *
Gavi trib2 p-value= 0.1107, r2 = 0.6862 
Gavi trib3 p-value= 0.097253, r2 = 0.5394 .
ANTE p-value = 0.0109, r2 = 0.2847 *

```{r fig 2a, echo=FALSE}


MyTheme <-  theme_bw() + 
  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=16)) +
  theme(legend.text=element_text(size=16))+
  theme(aspect.ratio=1)

rivernetwork <- ggplot(df %>%filter(Wetland_3=="Gavilan River Network"), aes(x = CatchmentSize_ha, y = log10(adjusted_ppm))) + 
  geom_point(size=3) +
  theme_bw() + 
  ylab(expression(paste(italic('p'),"CO"[2] ," [ppm]")))+
  xlab("Catchment Size [Hectares]") +
  scale_y_continuous(breaks=c(log10(300),log10(1000), log10(3000), log10(10000)), labels=c("300","1,000","3,000","10,000")) +
  geom_smooth(method='lm') +
  MyTheme + 
  annotate("text", x = 95, y = log10(10000), label  = expression("p-value < .0001\n", r^2 ~ "=" ~ .314), size = 4)

df <- df[order(df$adjusted_ppm),]
#?get_stadiamap()

gaviplot <- qmplot(lon_fit, lat_fit, data = df %>%filter(Wetland_3=="Gavilan River Network")%>%drop_na(adjusted_ppm),size= 6, maptype = "stamen_terrain", color = log10(adjusted_ppm)) +
  scale_color_gradient(low="blue", high="red",
                       breaks=c(log10(300),log10(1000), log10(3000), log10(10000)), labels=c("300","1,000","3,000","10,000"))+
    guides(size = "none") +
  theme(legend.text=element_text(size=14)) + 
  labs(color=expression(paste(italic('p'),"CO"[2] ," [ppm]"))) +
  theme(legend.title=element_text(size=16), 
    legend.text=element_text(size=14)) 


### c.

#annotate text 
dat_text <- data.frame(
  label = c("p-value = 0.011", "p-value < .0001", 
            "p-value = 0.027","p-value = 0.11"),
  Wetland_4   = c("ANTE", "Gavilan Outlet", "GAVItrib1", "GAVItrib2"),
  Wetland = c("ANTE","Gavi-mainstem","GAVItrib1","GAVItrib2"))


#subtract 523m from outlet
df[df$Wetland_4 == 'Gavilan Outlet',]$dist <- df[df$Wetland_4 == 'Gavilan Outlet',]$dist - 523

p2 <- ggplot(df%>%drop_na(Wetland)
             %>%filter(Wetland_4!="Gavilan Inlet")
             %>%filter(Wetland!="COLM")%>%filter(Wetland!="GAVItrib3")
       , aes(x = dist, y = log10(adjusted_ppm), color=Wetland)) +
  facet_grid(rows = vars(Wetland_4)) +
  geom_point(size=3) +
  ylab(expression(paste(italic('p'),"CO"[2] ," [ppm]"))) +
  xlab("Distance downstream [m]") +
  geom_smooth(method='lm')+
  theme(axis.text=element_text(size=10),
  axis.title=element_text(size=18,face="bold")) +
 theme_bw() +
  scale_color_manual(
    name=NULL,
    values = c(antens,gavi_out, gavitrib1,gavitrib2),
    labels=c("Antenas", "Gavil\u00e1n Outlet","Gavil\u00e1n Tributary 1","Gavil\u00e1n Tributary 2"))+
  scale_y_continuous(breaks=c(log10(300),log10(1000), log10(3000), log10(10000)), labels=c("300","1,000","3,000","10,000")) +
  theme(panel.spacing = unit(.05, "lines"),
        panel.border = element_rect(color = "black", fill = NA, linewidth = 1), 
  strip.background = element_rect(color = "black", linewidth = 1))+
  theme(legend.text=element_text(size=14),
        legend.key.size = unit(1, 'cm')) +
  theme(axis.title=element_text(size=16),
         axis.text=element_text(size=14))+ 
  theme(
  strip.background = element_blank(),
  strip.text.x = element_blank(),
  strip.text.y = element_blank())

p3 <- p2 + geom_text(
  data    = dat_text,
  mapping = aes(x = 400, y = log10(9000), label = label),
#  hjust   = -0.1,
#  vjust   = -11
)


figure1 <- ggarrange(rivernetwork, gaviplot,
                    labels = c("A","B"),
                    ncol = 1, nrow = 2,
               #    align = "hv",
                    widths = c(1, .8),
              #    heights = c(.6,.4),
                  font.label = list(size = 25, color = "black", face = "bold", family = NULL, position = "top"))

figure2 <- ggarrange(figure1, p3,
                    labels = c("","C"),
                    ncol = 2, nrow = 1,
              #     align = "hv",
               #     widths = c(1, .8),
              #    heights = c(.6,.4),
                  font.label = list(size = 25, color = "black", face = "bold", family = NULL, position = "top"))


```

# trends in flux 

#fig 3

Box plots
```{r fig 3, echo=FALSE}
###box and wisker####
anova.co2 <- aov(log(adjusted_ppm) ~ Wetland_5, data = df)
summary(anova.co2)

anova.flux <- aov(Flux_ave ~ Wetland_5, data = df)
summary(anova.flux)

anova.k600 <- aov(K600.effective ~ Wetland_5, data = df%>%filter(K600.effective>-30) )
summary(anova.k600)

tukey.co2<-TukeyHSD(anova.co2)
tukey.co2

tukey.flux<-TukeyHSD(anova.flux)
tukey.flux

tukey.k600<-TukeyHSD(anova.k600)
tukey.k600

MyTheme <-  theme_bw() + 
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.x = element_blank()) +
  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14)) +
  theme(legend.text=element_text(size=16))


CO2 <- ggplot(df, aes(x = Wetland_5, y = log10(adjusted_ppm), fill = Wetland_5)) +
  geom_boxplot() +
  geom_jitter(shape=18,position=position_jitter(0.1)) +
   stat_summary(fun = "mean", geom = "point", shape = 23, size = 3, color = "black",fill="white")+
  MyTheme +
  scale_fill_manual(
    name=NULL,
    values = c(antens,colmillo, gavi_in,gavi_out,gavitribs),
    labels=c("Antenas", "Colmillo","Gavil\u00e1n Inlet", "Gavil\u00e1n Outlet","Gavil\u00e1n Tributaries"))+
  ylab(expression(paste(italic('p'),"CO"[2]," [ppm]"))) +
  scale_y_continuous(breaks=c(log10(300),log10(1000), log10(3000), log10(10000)), labels=c("300","1,000","3,000","10,000"))  +
    annotate("text", x="ANTE", y= log10(18000),label="A", size = 4) +
  annotate("text", x="COLM", y= log10(18000),label="A", size = 4) +
  annotate("text", x="Gavilan Inlet", y= log10(18000),label="A", size = 4) +
   annotate("text", x="Gavilan Outlet", y= log10(18000),label="AB", size = 4) +
    annotate("text", x="GavilanTribs", y= log10(18000),label="B", size = 4)



flux <- ggplot(df, aes(x = Wetland_5, y = Flux_ave, fill = Wetland_5)) + 
  geom_boxplot() +
  geom_jitter(shape=18,position=position_jitter(0.1)) +
   stat_summary(fun = "mean", geom = "point", shape = 23, size = 3, color = "black",fill="white")+
  MyTheme +
  scale_fill_manual(
    name=NULL,
    values = c(antens,colmillo, gavi_in,gavi_out,gavitribs),
    labels=c("Antenas", "Colmillo","Gavil\u00e1n Inlet", "Gavil\u00e1n Outlet","Gavil\u00e1n Tributaries")) +
    ylab(expression(paste(" Evasion [",mu,"mol ", m^-2, s^-1,"]"))) +
    annotate("text", x="ANTE", y= 5,label="A", size = 4) +
    annotate("text", x="COLM", y= 5,label="B", size = 4) +
  annotate("text", x="Gavilan Inlet", y= 5,label="AB", size = 4) +
  annotate("text", x="Gavilan Outlet", y= 5,label="AC", size = 4) +
    annotate("text", x="GavilanTribs", y= 5,label="BC", size = 4) 


k600 <- ggplot(df%>%filter(K600.effective>-30)
               , aes(x = Wetland_5, y = K600.effective, fill = Wetland_5)) + 
  geom_boxplot() +
  geom_jitter(shape=18,position=position_jitter(0.1)) +
   stat_summary(fun = "mean", geom = "point", shape = 23, size = 3, color = "black",fill="white") +
  scale_fill_manual(
    name=NULL,
    values = c(antens,colmillo, gavi_in,gavi_out,gavitribs),
    labels=c("Antenas", "Colmillo","Gavil\u00e1n Inlet", "Gavil\u00e1n Outlet","Gavil\u00e1n Tributaries"))+
  MyTheme +
    ylab(expression(paste(italic('k')[600]," [m ", d^-1,"]"))) +
  annotate("text", x="ANTE", y= 155,label="A", size = 4) +
  annotate("text", x="COLM", y= 155,label="B", size = 4) +
  annotate("text", x="Gavilan Inlet", y= 155,label="A", size = 4) +
  annotate("text", x="Gavilan Outlet", y= 155,label="A", size = 4) +
  annotate("text", x="GavilanTribs", y= 155,label="A", size = 4)

require(grid)  



figure <- ggarrange(CO2 , flux,  k600,
                  #  labels = c("A","B","C"),
                    ncol = 1, nrow = 3,
                    common.legend = TRUE, legend = "right",
                    align = "hv", 
                  #  hjust   = -0.5,
                    font.label = list(size = 20, color = "black", face = "bold", family = NULL, position = "top"))

figure



```


#fig 4

for < 12.5 hectars, watershed size is not significant, co2 is significant
r2 = 0.5247, pvalue =2.43e-07
for > 20 ha, co2 is not significant, but watershed size is. pvalue = 0.00395 r2 = 0.1057

```{r fig 4, echo=FALSE}

df_sats <- df
df_sats$co2_scale <-scale(df_sats$adjusted_ppm)
df_sats$WS_scale <- scale(df_sats$CatchmentSize_ha)

model1_1 <- lm(Flux_ave ~ co2_scale, 
             data = df_sats%>%filter(Flux_ave>-1)%>%filter(CatchmentSize_ha<12.5))
summary(model1_1)
#
model2_2 <- lm(Flux_ave ~  WS_scale, 
             data = df_sats%>%filter(CatchmentSize_ha>20))
summary(model2_2)
#
model1_3 <- lm(Flux_ave ~ co2_scale + WS_scale, 
             data = df_sats%>%filter(Flux_ave>-1))
summary(model1_3)
#
p <- ggplot(df_sats%>%filter(Flux_ave>-.3)
       , aes(x=co2_scale + WS_scale, y=Flux_ave)) + geom_point() + 
  geom_smooth(method='lm') 
p1 <- ggplot(df_sats%>%filter(Flux_ave>-1)#%>%filter(CatchmentSize_ha<20)
       , aes(x=co2_scale + WS_scale, y=scale(Flux_ave))) + geom_point() + 
  geom_smooth(method='lm') 
p2 <- ggplot(df_sats%>%filter(Flux_ave>0)#%>%filter(CatchmentSize_ha<20)
       , aes(x=co2_scale + WS_scale, y=Flux_ave)) + geom_point() + 
  geom_smooth(method='lm') 
#####################
MyTheme <-  theme_bw() + 
  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=16)) +
  theme(legend.title = element_text(size=18),
    legend.text=element_text(size=16))

hex <- hue_pal()


A <- ggplot(df%>%filter(CatchmentSize_ha<12.5),
        aes(x=log10(adjusted_ppm), y=Flux_ave)) +
  geom_point(aes(fill=Wetland), 
       color="black",pch=21, size=4) + 
  geom_smooth(method='lm') +
  xlab("CO2 ppm") + 
  ylab(expression(paste("CO"[2]," Flux [",mu,"mol ", m^-2, s^-1,"]"))) +
  labs(linetype="LEGEND", color="LEGEND") +
  scale_fill_manual(name="Stream Reach",labels=c("Antenas", "Gavil\u00e1n Tributary 1","Gavil\u00e1n Tributary 3"), values = c(antens, gavitrib1, gavitrib3)) +
   scale_x_continuous(breaks=c(log10(300),log10(1000), log10(3000), log10(10000)), labels=c("300","1,000","3,000","10,000")) + 
  annotate("text", x = log10(6000), y = 2.2, label  = expression("p-value < .0001\n", r^2 ~ "=" ~ .52), size = 4) +
   theme_bw()  + MyTheme 



B <- ggplot(df_sats #%>%filter(Flux_ave>.05)
            %>%filter(CatchmentSize_ha>20)
  #           %>%filter(Wetland!="GAVItrib2")
  ,
        aes(x=CatchmentSize_ha, y=Flux_ave)) +
  geom_point(aes(fill=Wetland), 
       color="black",pch=21, size=4) + 
  geom_smooth(method='lm') +
  xlab("Catchment Size [ha]") + 
  ylab(expression(paste("CO"[2]," Flux [",mu,"mol ", m^-2, s^-1,"]"))) + 
  labs(linetype="LEGEND", color="LEGEND") +
  scale_fill_manual(
    name="Stream Reach",
    labels=c( "Colmillo","Gavil\u00e1n","Gavil\u00e1n Tributary 2"),values = c(colmillo, gavi,gavitrib2))+
  annotate("text", x = 180, y = 3.4, label  = expression("p-value = .0004\n", r^2 ~ "=" ~ .11), size = 4) +
   theme_bw()  + MyTheme



figure <- ggarrange(A , B,  
                #    labels = c("A","B"),
                    ncol = 1, nrow = 2,
                    #common.legend = TRUE, 
                    legend = "right",
                    align = "hv", 
                    font.label = list(size = 25, color = "black", face = "bold", family = NULL, position = "top"))

figure
ggsave("fig5.png", plot = figure, device = NULL, path = NULL,
       scale = 1, width = 20, height = 20, dpi = 360, limitsize = TRUE,
       units = c("cm"))


```


```{r fig 5, echo=TRUE}

### bins
df_bins <- df
df_bins$CatchmentSize_ha_log <- log(df_bins$CatchmentSize_ha)
df_bins <- df_bins%>%select(CatchmentSize_ha_log,K600.effective) %>%
  filter(K600.effective > -30) %>%
  mutate(Catchment_bin = cut(CatchmentSize_ha_log, breaks=5)) %>% 
  group_by(Catchment_bin) %>%
  summarise(
    k600_mean = mean(K600.effective, na.rm = TRUE),
    k600_stdev = sd(K600.effective, na.rm = TRUE),
    k600_median = median(K600.effective, na.rm = TRUE),
    k600_max = max(K600.effective, na.rm = TRUE),
    k600_min = min(K600.effective, na.rm = TRUE),
    n()
  )

df_bins$Catchment_bin2 <- as.character(df_bins$Catchment_bin)
df_bins$Catchment_bin3 <- gsub("]", "", df_bins$Catchment_bin2) 
df_bins$Catchment_bin4 <- sub('.', '', df_bins$Catchment_bin3)
df_bins[c('min_log', 'max_log')] <- str_split_fixed(df_bins$Catchment_bin4, ',', 2)
df_bins$min_log <- as.numeric(df_bins$min_log )
df_bins$max_log <- as.numeric(df_bins$max_log )

df_bins$min <- signif(exp(df_bins$min_log),digits =2)
df_bins$max <- signif(exp(df_bins$max_log),digits =2)

df_bins$bins_true  <- paste(df_bins$min, "-", df_bins$max)

df_bins$bins_true <- factor(df_bins$bins_true, levels = df_bins$bins_true[order(df_bins$min)])

p1<-ggplot(data=df_bins, aes(x=bins_true, y=k600_stdev)) +
  geom_bar(stat="identity", color="black",fill="grey", width=1)+ 
    ylab(expression(paste("standard deviation"))) + xlab("Catchment size (Hectar)") +
  theme_bw(base_size = 16)
    
p1


p2<-ggplot(data=df_bins, aes(x=Catchment_bin, y=k600_mean)) +
  geom_bar(stat="identity", color="black",fill="grey", width=1) +
  geom_point(aes(x=Catchment_bin,y=k600_median),shape=23,size=4,color="black",fill="black") + 
    ylab(expression(paste("mean ",italic('k')[600]," [m ", d^-1,"]"))) +
  theme_bw(base_size = 16) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) 
p2

full <- ggarrange(p2, p1, nrow = 2, common.legend = TRUE)

```

bring in gavi tribs 1 and 2 data



 calculated mid row for plotting of sample points

```{r add mid row ANTE, echo=FALSE}
#add wetlands_4 column for future plotting
df$Wetland_4 <- df$Wetland
Tribs$Wetland_4 <- Tribs$Wetland
df$Remove <- NA
Tribs$Remove <- NA

#ANTE

ANTE <- df%>%filter(Wetland=="ANTE")
ANTE <- ANTE[order(ANTE$dist),] 
for (row in 1:nrow(ANTE)) {
  ANTE$dist_mid[row] <- (ANTE$dist[row+1] - ANTE$dist[row])/2 + ANTE$dist[row]
  ANTE$TotalFlux_mid[row] <- (ANTE$Totalflux_umolpers[row+1] - ANTE$Totalflux_umolpers[row])/2 + ANTE$Totalflux_umolpers[row]
  }

ANTE$dist_mid <- NA
ANTE$TotalFlux_mid <- NA


for (row in 1:nrow(ANTE)) { 
  if(row==1){
    ANTE$dist_mid[row] <-  0
     ANTE$TotalFlux_mid[row] <- 0
    } else{
  ANTE$dist_mid[row] <- (ANTE$dist[row] - ANTE$dist[row-1])/2 + ANTE$dist[row-1]
  ANTE$TotalFlux_mid[row] <- (ANTE$Totalflux_umolpers[row] - ANTE$Totalflux_umolpers[row-1])/2 + ANTE$Totalflux_umolpers[row-1]
  }
}

```

```{r add mid row GAVI, echo=FALSE}
#GAVI-mainstem
df_trash <- df%>%filter(Wetland=="Gavi-mainstem")
df_trash <- df_trash[order(df_trash$dist),] 
for (row in 1:nrow(df_trash)) {
  df_trash$dist_mid[row] <- (df_trash$dist[row+1] - df_trash$dist[row])/2 + df_trash$dist[row]
  df_trash$TotalFlux_mid[row] <- (df_trash$Totalflux_umolpers[row+1] - df_trash$Totalflux_umolpers[row])/2 + df_trash$Totalflux_umolpers[row]
  }

df_trash$dist_mid <- NA
df_trash$TotalFlux_mid <- NA

for (row in 1:nrow(df_trash)) { 
  if(row==1){
    df_trash$dist_mid[row] <-  0
     df_trash$TotalFlux_mid[row] <- 0
    } else{
  df_trash$dist_mid[row] <- (df_trash$dist[row] - df_trash$dist[row-1])/2 + df_trash$dist[row-1]
  df_trash$TotalFlux_mid[row] <- (df_trash$Totalflux_umolpers[row] - df_trash$Totalflux_umolpers[row-1])/2 + df_trash$Totalflux_umolpers[row-1]
  }
}
GAVI <- df_trash

GAVI <- GAVI%>%filter(dist_mid < 300 | dist_mid > 400)

#GAVI$dist_mid<-replace(GAVI$dist_mid, GAVI$dist_mid>300&GAVI$dist_mid<400, NA)
  
#GAVI%>%filter(dist_mid < 300 | dist_mid > 400)

GAVI_up <- df_trash%>%filter(dist_mid < 300)
GAVI_up$Wetland_4 <- "Gavilan Inlet"
GAVI_down <- df_trash%>%filter(dist_mid > 400)

GAVI_down$Wetland_4 <- "Gavilan Outlet"
GAVI_down$dist_mid <- GAVI_down$dist_mid - GAVI_down$dist[1]
GAVI_down$TotalFlux_mid <- GAVI_down$TotalFlux_mid - GAVI_down$Totalflux_umolpers[1]
GAVI_down$dist <- GAVI_down$dist - GAVI_down$dist[1]
GAVI_down$Totalflux_umolpers <- GAVI_down$Totalflux_umolpers - GAVI_down$Totalflux_umolpers[1]
GAVI_down$Remove <- "Remove"

GAVI <- rbind(GAVI,GAVI_down,GAVI_up)

```

```{r add mid row COLM, echo=FALSE}
#	COLMILLO
df_trash <- df%>%filter(Wetland=="COLM")
df_trash <- df_trash[order(df_trash$dist),] 

df_trash$Totalflux_umolpers <- df_trash$Totalflux_umolpers - df_trash$Totalflux_umolpers[1]
df_trash$dist <- df_trash$dist - df_trash$dist[1]
df_trash <- df_trash[-1,]


df_trash <- df_trash[order(df_trash$dist),] 

for (row in 1:nrow(df_trash)) {
  df_trash$dist_mid[row] <- (df_trash$dist[row+1] - df_trash$dist[row])/2 + df_trash$dist[row]
  df_trash$TotalFlux_mid[row] <- (df_trash$Totalflux_umolpers[row+1] - df_trash$Totalflux_umolpers[row])/2 + df_trash$Totalflux_umolpers[row]
  }

df_trash$dist_mid <- NA
df_trash$TotalFlux_mid <- NA

for (row in 1:nrow(df_trash)) { 
  if(row==1){
    df_trash$dist_mid[row] <-  0
     df_trash$TotalFlux_mid[row] <- 0
    } else{
  df_trash$dist_mid[row] <- (df_trash$dist[row] - df_trash$dist[row-1])/2 + df_trash$dist[row-1]
  df_trash$TotalFlux_mid[row] <- (df_trash$Totalflux_umolpers[row] - df_trash$Totalflux_umolpers[row-1])/2 + df_trash$Totalflux_umolpers[row-1]
  }
}
COLM <- df_trash

```

```{r add mid row tribs, echo=FALSE}

#	GAVI Trib 1
df_trash <- Tribs%>%filter(Wetland=="Tributary 1")%>%drop_na(Flux_ave)
df_trash <- df_trash[order(df_trash$dist),] 
for (row in 1:nrow(df_trash)) {
  df_trash$dist_mid[row] <- (df_trash$dist[row+1] - df_trash$dist[row])/2 + df_trash$dist[row]
  df_trash$TotalFlux_mid[row] <- (df_trash$Totalflux_umolpers[row+1] - df_trash$Totalflux_umolpers[row])/2 + df_trash$Totalflux_umolpers[row]
  }

df_trash$dist_mid <- NA
df_trash$TotalFlux_mid <- NA


for (row in 1:nrow(df_trash)) { 
  if(row==1){
    df_trash$dist_mid[row] <-  0
     df_trash$TotalFlux_mid[row] <- 0
    } else{
  df_trash$dist_mid[row] <- (df_trash$dist[row] - df_trash$dist[row-1])/2 + df_trash$dist[row-1]
  df_trash$TotalFlux_mid[row] <- (df_trash$Totalflux_umolpers[row] - df_trash$Totalflux_umolpers[row-1])/2 + df_trash$Totalflux_umolpers[row-1]
  }
}
Trib1 <- df_trash

#	GAVI Trib 2
df_trash <- Tribs%>%filter(Wetland=="Tributary 2")%>%drop_na(Flux_ave)
df_trash <- df_trash[order(df_trash$dist),] 
for (row in 1:nrow(df_trash)) {
  df_trash$dist_mid[row] <- (df_trash$dist[row+1] - df_trash$dist[row])/2 + df_trash$dist[row]
  df_trash$TotalFlux_mid[row] <- (df_trash$Totalflux_umolpers[row+1] - df_trash$Totalflux_umolpers[row])/2 + df_trash$Totalflux_umolpers[row]
  }

df_trash$dist_mid <- NA
df_trash$TotalFlux_mid <- NA

for (row in 1:nrow(df_trash)) { 
  if(row==1){
    df_trash$dist_mid[row] <-  0
     df_trash$TotalFlux_mid[row] <- 0
    } else{
  df_trash$dist_mid[row] <- (df_trash$dist[row] - df_trash$dist[row-1])/2 + df_trash$dist[row-1]
  df_trash$TotalFlux_mid[row] <- (df_trash$Totalflux_umolpers[row] - df_trash$Totalflux_umolpers[row-1])/2 + df_trash$Totalflux_umolpers[row-1]
  }
}

Trib2 <- df_trash

```

##bind together

```{r bind df, echo=FALSE}
df1_1 <- df%>%filter(Wetland=="COLM")
df1_1 <- df1_1[order(df1_1$dist),] 
df1_1$Totalflux_umolpers <- df1_1$Totalflux_umolpers - df1_1$Totalflux_umolpers[1]
df1_1$dist <- df1_1$dist - df1_1$dist[1]
df1_1 <- df1_1[-1,]

df1_2 <- df%>%filter(Wetland != "COLM")

df1 <- rbind(df1_1,df1_2)

df1$shape <- NA
df1$dist_mid <- NA
df1$TotalFlux_mid <- NA

df1 <- df1[,c("dist","adjusted_ppm","Totalflux_umolpers","Wetland","Wetland_4","shape","Remove")]

df2 <- rbind(ANTE,COLM,GAVI)
df2$Totalflux_umolpers <- df2$TotalFlux_mid
df2$dist <- df2$dist_mid
df2$shape <- "shape"

df3 <- rbind(Trib1,Trib2)
df3$Totalflux_umolpers <- df3$TotalFlux_mid
df3$dist <- df3$dist_mid
df3$shape <- "shape"

df2 <- df2[,c("dist","adjusted_ppm","Totalflux_umolpers","Wetland","Wetland_4","shape","Remove")]
df3 <- df3[,c("dist","adjusted_ppm","Totalflux_umolpers","Wetland","Wetland_4","shape","Remove")]

df1 <- rbind(df1,df2,df3)

df_test<- df1%>%filter(Wetland!="GAVItrib1")%>%filter(Wetland!="GAVItrib2")%>%filter(Wetland!="GAVItrib3")
df_test$Totalfux_gpers <- df_test$Totalflux_umolpers /1000000 *44
write.csv(df_test%>%filter(Wetland_4 != "Gavilan Outlet")%>%filter(Wetland_4 != "Gavilan Inlet")%>%filter(Wetland_4 != "	
Tributary 1")%>%filter(Wetland_4 != "	
Tributary 2"), file=here::here('new_file.csv'), row.names=FALSE)
```

#plot


```{r bball fig, echo=FALSE}

MyTheme <-  theme_bw() + 
  theme(axis.text=element_text(size=18),
        axis.title=element_text(size=24)) +
  theme(legend.title = element_text(size=24),
    legend.text=element_text(size=18))+
  theme(aspect.ratio=1)


bball <- ggplot(df_test%>%filter(Wetland_4 != "Gavilan Outlet")%>%filter(Wetland_4 != "Gavilan Inlet"),
                aes(x=dist, y=Totalflux_umolpers, group=Wetland_4)) +
  geom_line(aes(color=Wetland), size=3) +
  geom_point(aes(shape = shape,fill=Wetland), size=2) +
  ylab(expression(paste(""))) +
  xlab("") +
  scale_color_manual(name="Stream Reach",labels=c("Antenas", "Colmillo","Gavilan-mainstem","Tributary 1","Tributary 2"), values=c(antens, colmillo, gavi,gavitrib1, gavitrib2)) +
  scale_fill_manual(name="Stream Reach",labels=c("Antenas", "Colmillo","Gavilan-mainstem","Tributary 1","Tributary 2"), values=c(antens, colmillo, gavi,gavitrib1, gavitrib2)) +
  scale_linetype_discrete(name="Stream Reach",labels=c("Antenas", "Colmillo","Gavilan-mainstem","Tributary 1","Tributary 2")) +
  scale_shape_manual(name="Sample Point", labels=c("",""), values = 21) +
  guides(fill=FALSE,color=FALSE,shape=FALSE) +
  MyTheme


bball


#"#F8766D" "#C49A00" "#53B400" "#00C094" "#00B6EB" "#A58AFF" "#FB61D7"

#zoom in
bball_zoom <- ggplot(df_test%>%filter(Wetland_4 != "Gavi-mainstem"), 
                     aes(x=dist, y=Totalflux_umolpers, group=Wetland_4)) +
  geom_line(aes(color=Wetland_4), size=3) +
  geom_point(aes(shape = shape,fill=Wetland_4), size=2)+
    ylab(expression(paste("Cumulative CO"[2]," Flux [",mu,"mol ", s^-1,"]"))) + 
  xlab("Distance [m]") +
  scale_color_manual(name="Stream Reach",
                     labels=c("Antenas", "Colmillo","Gavilan Inlet","Gavilan Outlet","Tributary 1","Tributary 2"), 
                     values=c(antens, colmillo, gavi_in,gavi_out,gavitrib1, gavitrib2)) +
  scale_linetype_discrete(name="Stream Reach",
                          labels=c("Antenas", "Colmillo","Gavilan Inlet","Gavilan Outlet","Tributary 1","Tributary 2")) +
  scale_shape_manual(name="Sample Point", labels=c("",""), values = 21) +
  scale_fill_manual(values=c(antens, colmillo, gavi_in,gavi_out,gavitrib1, gavitrib2)) +
    guides(fill=FALSE) +
  xlim(-10, 350) +
  ylim(-20, 300) +
  MyTheme 


bball_zoom

```

that worked! now I'm going to fiddle around to prefct it more

```{r bball fig 2, echo=FALSE}

bball_annotate <- bball + 
  annotate("rect", xmin = -10, xmax = 350, ymin = -20, ymax = 300,
  colour = "blue",alpha = .2)


#zoom in
bball_zoom_nolegend <- 
  ggplot(df_test%>%filter(Wetland_4 != "Gavi-mainstem")
       , aes(x=dist, y=Totalflux_umolpers, group=Wetland_4)) +
  geom_line(aes(#linetype=Wetland_4,
    color=Wetland_4),
    size=3) +
  geom_point(aes(shape = shape,fill=Wetland_4), size=2) +
  ylab(expression(paste("Cumulative CO"[2]," Flux [",mu,"mol ", s^-1,"]"))) + 
  xlab("Distance [m]") +
  scale_color_manual(
    name="Stream Reach",
    labels=c("Antenas", "Colmillo","Gavilan Inlet","Gavilan Outlet","Tributary 1","Tributary 2"),
    values=c(antens, colmillo, gavi_in,gavi_out,gavitrib1, gavitrib2)) +
  scale_linetype_discrete(
    name="Stream Reach",
    labels=c("Antenas", "Colmillo","Gavilan Inlet","Gavilan Outlet","Tributary 1","Tributary 2")) +
  scale_shape_manual(
    name="Sample Point", 
    labels=c("",""), values = 21) +
  scale_fill_manual(
values=c(antens, colmillo, gavi_in,gavi_out,gavitrib1, gavitrib2)) +
    guides(fill=FALSE) +
  xlim(-10, 350) +
  ylim(-20, 300) +
  MyTheme +
  theme(legend.position = "none") 

bball_zoom_nolegend


#p <- bball + annotation_custom(ggplotGrob(bball_zoom_nolegend), xmin = 1, xmax = 400, 
#                       ymin = 1000, ymax = 1500)




# Extract the legend. Returns a gtable
leg <- get_legend(bball)
leg2 <- get_legend(bball_zoom)


# Convert to a ggplot and print
as_ggplot(leg)
as_ggplot(leg2)


ggsave("testing123.png",plot = bball, dpi = 360, units = "cm")

ggsave("testing123.png", plot = bball, device = NULL, path = NULL,
       scale = 1, width = 25, height = 20, dpi = 360, limitsize = TRUE,
       units = c("cm"))


#0-500 m
#0- 400
#filled circle sample color as ln but outer in black

```

#the last one will be conceptual!!!! 
include k600, co2, flux rate AND conceptual for total flux bom baby


```{r stats, echo=FALSE}


model <- lm(Flux_ave ~ log10(adjusted_ppm) + WatershedSize_ha, 
             data = df%>%filter(WatershedSize_ha<12.5)
)
summary(model)

model <- lm(Flux_ave ~ log10(adjusted_ppm) + WatershedSize_ha, 
             data = df%>%filter(WatershedSize_ha>20)
)
summary(model)


MyTheme <-  theme_bw() + 
  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=16)) +
  theme(legend.title = element_text(size=18),
    legend.text=element_text(size=16))


ggplot(df%>%filter(WatershedSize_ha>12.5),
       #%>%drop_na(adjusted_ppm) #%>% filter(dist<250)
        aes(x=WatershedSize_ha, y=Flux_ave)) +
  geom_point(aes(fill=Wetland), 
       color="black",pch=21, size=5) + 
  geom_smooth(method='lm') +
  xlab("CO2 ppm") + ylab("CO2 Flux (umol per m2 per s)") +labs(linetype="LEGEND", color="LEGEND") +
 # scale_fill_discrete(name="Stream Reach",labels=c("Antenas", "Gavilan Tributary 1","Gavilan Tributary 2")) +
   scale_x_continuous(breaks=c(log10(300),log10(1000), log10(3000), log10(10000)), labels=c(300,"1,000","3,000","10,000")) +
   theme_bw()  + MyTheme


```

```{r fig 2, echo=TRUE}


ggplot(df
       , aes(x = dist, y = Flux_ave, color=Wetland_2)) +
  facet_wrap(~Wetland, scales = "free")+
  geom_point(size=3) +
  theme_bw() + 
  ylab("CO2 flux (umol/m2/s)") + 
  xlab("Catchment Size (Hectares)") +
    geom_smooth(method='lm')+
  theme(axis.text=element_text(size=10),
  axis.title=element_text(size=18,face="bold"))




```







##fig 3


```{r test figs, echo=FALSE}
####

ggplot(df%>% filter(RASTERVALU>2000),
       #%>%drop_na(adjusted_ppm) #%>% filter(dist<250)
       aes(x=log10(adjusted_ppm), y=Flux_ave)) +
  geom_point(aes(color=Wetland)) + 
#  geom_smooth(method='lm') +
  xlab("CO2 ppm") + ylab("CO2 Flux (umol per m2 per s)") +labs(linetype="LEGEND", color="LEGEND") +
  scale_color_discrete(name="LEGEND",labels=c("Colmillo", "Gavilan Mainstem","Gavilan Tributary")) +
  scale_x_continuous(breaks=c(log10(300),log10(1000), log10(3000), log10(10000)), labels=c(300,1000,3000,10000)) +
  #  scale_color_manual(name="LEGEND",labels=c("blah", "GAVItrib2","GAVItrib3_1","GAVItrib3_2")) +
  theme_bw() 


ggplot(df #%>% filter(adjusted_ppm>2000)
       ,
       #%>%drop_na(adjusted_ppm) #%>% filter(dist<250)
       aes(x=log10(adjusted_ppm), y=Flux_ave)) +
  geom_point(aes(color=Wetland)) + 
#  geom_smooth(method='lm') +
  xlab("CO2 ppm") + ylab("CO2 Flux (umol per m2 per s)") +labs(linetype="LEGEND", color="LEGEND") +
 # scale_color_discrete(name="LEGEND",labels=c("Colmillo", "Gavilan Mainstem","Gavilan Tributary")) +
  scale_x_continuous(breaks=c(log10(300),log10(1000), log10(3000), log10(10000)), labels=c(300,1000,3000,10000)) +
  #  scale_color_manual(name="LEGEND",labels=c("blah", "GAVItrib2","GAVItrib3_1","GAVItrib3_2")) +
  theme_bw() 

ggplot(df #%>% filter(adjusted_ppm>2000)
       %>%filter(Wetland=="ANTE")%>%filter(dist>0)
       ,
       aes(x=dist, y=log10(adjusted_ppm))) +
  geom_point(aes(color=Wetland)) + 
  theme_bw() 

# Extract the legend. Returns a gtable
leg <- get_legend(p1)

# Convert to a ggplot and print
as_ggplot(leg)


p2 <- ggplot(df %>%filter(Wetland=="ANTE")
       , aes(x = dist, y = adjusted_ppm))+
  geom_point(size=3,color="#F8766D") +
  ylab(expression(paste(italic('p'),"CO"[2] ," [ppm]"))) + xlab("Distance downstream [m]") +
      geom_smooth(method='lm', color="#F8766D")+
  theme(axis.text=element_text(size=10), axis.title=element_text(size=18,face="bold")) +
  theme_classic() +
  theme(panel.spacing = unit(.05, "lines"),
        panel.border = element_rect(color = "black", fill = NA, size = 1), 
        strip.background = element_rect(color = "black", size = 1))+ 
  theme( strip.text.x = element_blank() )+ 
  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=16)) +
  theme(legend.text=element_text(size=16))+
  theme(aspect.ratio=1)+
  theme(legend.position = "none") 


p3 <- ggplot(df %>%filter(Wetland=="GAVItrib1")
       , aes(x = dist, y = adjusted_ppm))+
#  facet_grid(.~Wetland, scales = "free") +
#  ylim(-1000,15000)+
  geom_point(size=3,color="#00BA38") +
  ylab(expression(paste(italic('p'),"CO"[2] ," [ppm]"))) +
  xlab("Distance downstream [m]") +
      geom_smooth(method='lm',color="#00BA38")+
  theme(axis.text=element_text(size=10),
  axis.title=element_text(size=18,face="bold")) +
  theme_classic() +
  theme(panel.spacing = unit(.05, "lines"),
        panel.border = element_rect(color = "black", fill = NA, size = 1), 
        strip.background = element_rect(color = "black", size = 1))+ 
  theme( strip.text.x = element_blank() )+ 
  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=16)) +
  theme(legend.text=element_text(size=16))+
  theme(aspect.ratio=1)+
  theme(legend.position = "none") 

p4 <- ggplot(df %>%filter(Wetland=="GAVItrib2")
       , aes(x = dist, y = adjusted_ppm))+
#  facet_grid(.~Wetland, scales = "free") +
#  ylim(-1000,15000)+
  geom_point(size=3,color="#619CFF") +
  ylab(expression(paste(italic('p'),"CO"[2] ," [ppm]"))) +
  xlab("Distance downstream [m]") +
      geom_smooth(method='lm',color="#619CFF")+
  theme(axis.text=element_text(size=10),
  axis.title=element_text(size=18,face="bold")) +
  theme_classic() +
  theme(panel.spacing = unit(.05, "lines"),
        panel.border = element_rect(color = "black", fill = NA, size = 1), 
        strip.background = element_rect(color = "black", size = 1))+ 
  theme( strip.text.x = element_blank() )+ 
  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=16)) +
  theme(legend.text=element_text(size=16))+
  theme(aspect.ratio=1)+
  theme(legend.position = "none") 

p1 <- as_ggplot(leg)
p2
p3
p4
```


Just  little bit of data cleaning needed. I don't like the 
```{r clean  data}

```

#stream profiles

```{r profiles, echo=FALSE}
GAVI <- df%>%filter(Wetland_2=="Gavi-mainstem")
ANTE <- df%>%filter(Wetland_2=="ANTE")
COLM <- df%>%filter(Wetland_2=="COLM")

ANTE$dist_ANTE <- ANTE$dist
ANTE$dist_COLM <- NA
ANTE$dist_GAVI <- NA

COLM$dist_COLM <- COLM$dist
COLM$dist_ANTE <- NA
COLM$dist_GAVI <- NA

GAVI$dist_GAVI <- GAVI$dist
GAVI$dist_ANTE <- NA
GAVI$dist_COLM <- NA
GAVI <- GAVI%>%drop_na(Date)

GAVI_sub <- GAVI%>%filter(dist > 462 & dist < 570)

df <- rbind(ANTE,COLM,GAVI)

###

hex <- hue_pal()

Profile <- ggplot(data=df ) +
  geom_line(aes(dist_ANTE, ele_fit), size = 4, color="grey") +
  geom_line(aes(dist_GAVI, ele_fit), size = 4, color="grey") +
  geom_line(aes(dist_COLM, ele_fit), size = 4, color="grey") +
  geom_point(aes(dist_ANTE, ele_fit), size = 4, shape=21, fill=hex(3)[1],color="black") +
  geom_point(aes(dist_GAVI, ele_fit), size = 4, shape=21, fill=hex(3)[3],color="black") +
  geom_point(aes(dist_COLM, ele_fit), size = 4, shape=21, fill=hex(3)[2],color="black") +
  labs(y="Elevation [m]", x = "Distance [m]")  +
  theme_classic() + My_Theme 


Profile
ggsave("streamprofil_2.png", plot = Profile, device = NULL, path = NULL,
       scale = 1, width = 10, height = 10, dpi = 360, limitsize = TRUE,
       units = c("cm"))

####

Profile <- ggplot(data=df ) +
  geom_line(aes(dist_ANTE, ele_fit), size = 2, alpha=.25) +
  geom_line(aes(dist_GAVI, ele_fit), size = 2, alpha=.5) +
  geom_line(aes(dist_COLM, ele_fit), size = 2,alpha=.5) +
#  geom_point(data=df%>%drop_na(Flux_ave), aes(dist, ele_fit, color= Flux_ave),size=3)+
#  scale_color_gradient(
#  low = "blue", high = "red",
#    space = "Lab",
#    na.value = "grey50",
#    guide = "colourbar",
#    aesthetics = "colour",
#    name = "Flux umol m^2 s^-1"
#  )+  
  labs(y="elevation", x = "distance")  +

  theme_classic() + My_Theme + theme(legend.position = c(0.8, 0.9))


```

##doc plot

```{r water chem, echo=FALSE}


DOC <- ggplot(df, aes(x = Wetland_2, y = DOC, fill = Wetland_2)) + 
  geom_boxplot() +
  geom_jitter(shape=1,position=position_jitter(0.1)) +
   stat_summary(fun = "mean", geom = "point", shape = 23, size = 3, color = "black",fill="white")+
  MyTheme +
    ylab(expression(paste("DOC [ mg", L^-1,"]"))) +
  scale_fill_discrete(name=NULL) #+
#  annotate("text", x="Gavilan Tributaries", y= 5,label="BC", size = 5) +
#  annotate("text", x="Antenas", y= 5,label="A", size = 5) +
#  annotate("text", x="Gavilan Mainstem", y= 5,label="AC", size = 5) +
#  annotate("text", x="Colmillo", y= 5,label="B", size = 5)

```
