---
title: "Correcting CO2"
author: "KWhitmore"
date: "1/3/2022"
output: html_document


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggpubr)
library(gridExtra)
```


Adjust Viasala readings for pressure and temperature

viasala readings need to be corrected for pressure and temperature:
 Temperature dependence: -0.3% of reading / celcius (reference 25c/77F)
 Pressure dependence: +0.15% of reading / hPa (reference 1013hPa)
 
check method section in -

Johnson, M. S., Billett, M. F., Dinsmore, K. J., Wallin, M., Dyson, K. E., & Jassal, R. S. (2010). Direct and continuous measurement of dissolved carbon dioxide in freshwater aquatic systems—method and applications. Ecohydrology: Ecosystems, Land and Water Process Interactions, Ecohydrogeomorphology, 3(1), 68-78.
 

# correct for WL
run script WaterLevel_Dischage.Rmd
run script CO2_Corrected.Rmd

```{r merge data, echo=FALSE}
# first run script WaterLevel_Dischage.Rmd
WL_df <- rbind(WL_01,WL_02,WL_03,WL_04,All_Well)
WL_df$Station <- gsub('WL', 'stn', WL_df$Station)

CO2_df <- rbind(stations,wells)
CO2_df$Station <- gsub('CO2', 'stn', CO2_df$Station)

df <- full_join(WL_df,CO2_df, by=c("DateTime","Station"))


```

convert unit of in baro data

```{r baro, echo=FALSE}
#convert baro to hpa
#1 kPa = 10 hPa
#1 kPa = 0.101972 m
df$Total_hPa <- df$Total_kpa * 10

```

##Create Station Dataframes
we two different models of vaisala

```{r stations, echo=FALSE}


#old:
#Temperature dependence: -0.3% of reading / celcius (reference 25c/77F)
#Pressure dependence: +0.15% of reading / hPa (reference 1013hPa)


#Station 1 and 4 are old
df_old <- df %>% filter(Station == "stn_01"|Station == "stn_04")

df_old$adjusted_ppm <- df_old$ppm * (1 + (1013 - df_old$Total_hPa) * 0.0015) * (1 - (25 - df_old$WLTemp_c) * 0.003)

#df_old$TempDif <- (df_old$WLTemp_c - 25)
#df_old$PressDif <- (1013 - df_old$Total_hPa)
#df_old$adjusted_ppm_2 <- df_old$ppm * (1 + df_old$PressDif * 0.0015) * (1 + df_old$TempDif * 0.003)

#new

#The new viasalas are set to 700hPa and 6.7c

#Station 2, 3 and Well 1 and 2 are new V
df_new <- df %>% filter(Station != "stn_01" & Station != "stn_04")

df_new$adjusted_ppm <- df_new$ppm * (1 + (700 - df_new$Total_hPa) * 0.0015) * (1 - (6.7 - df_new$WLTemp_c) * 0.003)


```

```{r plot, echo=FALSE}
df_corrected <- rbind(df_old,df_new)

co2 <- ggplot(data = df_corrected %>% filter(Station=='stn_04')
         , aes(DateTime, adjusted_ppm)) +
  geom_point(color = "steelblue") +
  labs(#title = "CO2  stations",
       y = "CO2 ppm", x = "") 
  
Q <- ggplot(data = df_corrected %>% filter(Station=='stn_04')
         , aes(DateTime, Q_m3s)) +
  geom_point(color = "steelblue") +
  labs(#title = "Q  stations",
       y = "Q", x = "") 

grid.arrange(co2, Q, ncol=1)

all.figs <- ggarrange(NULL,co2, NULL,Q, ncol = 1,
               heights = c(0.2,1,0.2,1),
               labels = c("A","","B",""),
               font.label = list(size = 24, color = "black", face = "bold"),
              # label.x = .1,
              # label.y = .1,
               align="h", common.legend = FALSE
               )



#ggplot(data = wells%>%filter(ppm < 15000), aes(DateTime, ppm)) +
#  geom_point(color = "steelblue") +
  #  geom_point(color="steelblue") + 
#  labs(#title = "CO2  stations",
#    y = "CO2 ppm", x = "") + 
#  facet_wrap(~ Station)

fig <- plot_ly(df_corrected%>%filter(Station=='stn_01')%>%
  filter(DateTime < as.POSIXct("2021-07-30 07:27:00", tz = "UTC")),x = ~DateTime, y= ~ppm, type = 'scatter', mode = 'markers')
fig <- fig %>% add_trace(y = ~Q_m3s*100000, name = 'Q',mode = 'markers')

fig



#plot pressure


plot_ly(df_all %>%filter(Station=='stn_02')%>%
  filter(DateTime < as.POSIXct("2021-7-31 07:27:00", tz = "UTC")),x = ~DateTime, y= ~WL_m, type = 'scatter', mode = 'markers')
plot_ly(df_all%>%filter(Station=='stn_02')%>%
  filter(DateTime < as.POSIXct("2021-7-31 07:27:00", tz = "UTC")),x = ~DateTime, y= ~adjusted_ppm, type = 'scatter', mode = 'markers')
plot_ly(df_all%>%filter(Station=='stn_03')%>%
  filter(DateTime < as.POSIXct("2021-7-31 07:27:00", tz = "UTC")),x = ~DateTime, y= ~adjusted_ppm, type = 'scatter', mode = 'markers')
plot_ly(df_all%>%filter(Station=='stn_04')%>%
  filter(DateTime < as.POSIXct("2021-7-31 07:27:00", tz = "UTC")),x = ~DateTime, y= ~adjusted_ppm, type = 'scatter', mode = 'markers')
plot_ly(df_all%>%filter(Station=='well_01')%>%
  filter(DateTime < as.POSIXct("2021-7-31 07:27:00", tz = "UTC")),x = ~DateTime, y= ~adjusted_ppm, type = 'scatter', mode = 'markers')
plot_ly(df_all%>%filter(Station=='well_02')%>%
  filter(DateTime < as.POSIXct("2021-7-31 07:27:00", tz = "UTC")),x = ~DateTime, y= ~adjusted_ppm, type = 'scatter', mode = 'markers')


```
