---
title: "k600_calculation_2024"
author: "Kriddie"
date: "2024-05-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(dplyr) 
library(tidyr) 
library(ggplot2)
library(cowplot)
library(tidyverse)
library(rstatix)
library(ggpubr)
library(dplyr)
library(lubridate)
```

## gas transfer velocity calculation

we need to figure this shit out

# Read in data


```{r read in data}

#read in df 
synoptic.df <- read.csv(here::here("ProcessedData/ALL_synoptic_2022-06-08.csv"))
synoptic.df <- synoptic.df%>%drop_na(Date)%>%rename(air_pressure_hpa = Total_hPa)%>%select(
  lon_fit,lat_fit,ele_fit,dist,Date,Flux_ave,adjusted_ppm,AirTemp_c,WaterTemp_c,air_pressure_hpa,surface_area,
  flux_umolpers,Totalflux_umolpers,DOC,TDN,Wetland,dist_ANTE,dist_GAVI,dist_COLM,dist_GAVItrib1,dist_GAVItrib2,dist_GAVItrib3,
)
synoptic.df <- synoptic.df%>%rename(pCO2_ppm=adjusted_ppm)
```

# Try Mcdowell way first

### Calculate concentration CO2 in water (gCO2-C per Liter) using Henry's law ###

concentration of air from www.esrl.noaa.gov
mean of 2021: 416.45 ppm


*we have problems*
1. Mcdowell says that henrys constant is in mol/L, but it should be (mol/(kg*bar))
      > for now let's use all the values just as mcdowell says they are
2. multiply by kH 2x
3. flux is in m-2 and so is k, but Concnetration is in L
  

```{r the mcdowell way, echo=FALSE}

#constants
R=0.08205736608096
gCO2asC <- 12

#adjust henry to temp: KH = KH(STP) x exp(D(1/T-1/T(STP)))
kH_STP_mol.L = .035
D_K = 2400 
T_STP_K = 298.15


#air pressure
synoptic.df$pCO2_air_ppm <- 416.45
synoptic.df$pCO2_air_atm <- 416.45*10^-6

#henry's constant adjust for temp (though I think this is wrong?)
synoptic.df$KH_mol.L <- kH_STP_mol.L * exp(D_K*(1/(synoptic.df$WaterTemp_c+273.15) - 1/T_STP_K))

#calc concntration for CO2 in water
synoptic.df$CO2_CO2asC_gperL <- synoptic.df$pCO2_ppm*synoptic.df$KH_mol.L*12*10^-6

#calc deltaCO2
synoptic.df$deltaCO2 <- synoptic.df$KH_mol.L*(synoptic.df$CO2_CO2asC_gperL - synoptic.df$pCO2_air_atm)

#change units of flux (umol/m2/s - > g C m−2 d−1)
#86400 seconds in a day
synoptic.df$Flux_gC_m2_s <- synoptic.df$Flux_ave * 10^-6 * 12 * 86400

#now calculate k in m/d
synoptic.df$k_m_d_mcdowell <- synoptic.df$Flux_gC_m2_s / synoptic.df$deltaCO2


```


#now let's do it again the way I think it should be

i so hope this works. so nervous right now

*check vaisala to see if it is uatm/atm or if this is by volume or what the heck*


1. fix henry's constant -- actualy bar is aproximatly = to atm, and kg is equal to l in water


```{r the kriddie's brain way, echo=FALSE}

#PV=nRt -> n/V=P/Rt
R = 8.31446261815324*9.86923e-6*1000 # L·atm·K-1·mol-1

#adjust henry to temp: KH = KH(STP) x exp(D(1/T-1/T(STP)))
#use constants in  	Burkholder et al. (2019) and convert to desired units
#  k°H (mol/(kg*bar) = mol/l/atm
#d(ln(kH))/d(1/T) (K)
kH_STP_mol.l.atm = 3.5*1/0.986923
D_K = 2400 
T_STP_K = 298.15


#convert air pressure to atm
synoptic.df$air_pressure_atm <- synoptic.df$air_pressure_hpa * 0.0009869233
synoptic.df$water_pressure_atm <- synoptic.df$air_pressure_hpa * 0.0009869233 + 0.000967841

synoptic.df$pCO2_air_ppm <- 416.45

synoptic.df$pCO2_air_mol.L <- synoptic.df$pCO2_air_ppm * 10^-6 * synoptic.df$air_pressure_atm / R / (synoptic.df$AirTemp_c + 273.15)

synoptic.df$pCO2_w_mol.L <- synoptic.df$pCO2_ppm * 10^-6 * synoptic.df$water_pressure_atm / R/ (synoptic.df$WaterTemp_c + 273.15)


#henry's constant adjust for temp
synoptic.df$KH_mol.l.atm <- kH_STP_mol.l.atm * exp(D_K*(1/(synoptic.df$WaterTemp_c+273.15) - 1/T_STP_K))
synoptic.df$KH_mol.m3.atm <- synoptic.df$KH_mol.l.atm * 0.001


#change units of flux (umol/m2/s - > mol/m2/d)
#86400 seconds in a day
synoptic.df$Flux_mol_m2_d <- synoptic.df$Flux_ave * 10^-6 * 86400

#now calculate k in m/d
#synoptic.df$k_m_d_kriddie <- synoptic.df$Flux_mol_m2_d / (synoptic.df$KH_mol.l.atm * (synoptic.df$pCO2_w_mol.L - synoptic.df$pCO2_air_mol.L )) #*1000

synoptic.df$k_m_d_kriddie <- synoptic.df$Flux_mol_m2_d / (.05 * (synoptic.df$pCO2_w_atm - synoptic.df$pCO2_air_atm )) #*1000



```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
