---
title: "Geomorphology_COLM"
author: "KWhitmore"
date: "12/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(lubridate)
library(plotly)
library(dplyr)
library(tidyr)
library(zoo)
library(plot3D)
library(splines)
library(Ecdat)
library(dplyr)
library(sp)
library(geosphere)


```

## BUild the geomorphology data frame for Colmillo

```{r build df 2021-07-09}

Geomorph <- read.csv(here::here("/Geomorphology/Colmillo/2021-07-09 11_20_03 CANINE Stream Profile.csv"), skip = 42)


Geomorph <- Geomorph[,3:6]

#convert time in UTC to local time
Geomorph$time <- gsub("T"," ", Geomorph$time)
Geomorph$time <- gsub("Z","", Geomorph$time)

Geomorph$time <- as.POSIXct(Geomorph$time, format = "%Y-%m-%d %H:%M:%S", tz = "UTC" )
Geomorph$time <-Geomorph$time - 5*60*60 
#round to nearest half second
Geomorph$time <- round_date(Geomorph$time, unit = "30 second")

# 2021-07-16 START: 11:29:03  END:  15:24:37
Geomorph <- subset(Geomorph,
      time > as.POSIXct('2021-07-09 11:29:03', tz="UTC") & 
        time < as.POSIXct('2021-07-09 15:24:37', tz="UTC"))

Geomorph_July9 <- Geomorph

```

```{r build df 2021-07-16}


Geomorph <- read.csv(here::here("/Geomorphology/Colmillo/COLMILLO 2021-07-16.csv"), skip = 42)
Geomorph <- Geomorph[,3:6]

#convert time in UTC to local time
Geomorph$time <- gsub("T"," ", Geomorph$time)
Geomorph$time <- gsub("Z","", Geomorph$time)

Geomorph$time <- as.POSIXct(Geomorph$time, format = "%Y-%m-%d %H:%M:%S", tz = "UTC" )
Geomorph$time <-Geomorph$time - 5*60*60 
#round to nearest half second
Geomorph$time <- round_date(Geomorph$time, unit = "30 second")

# 2021-07-16 START: 09:45:00  END:  13:49:17
Geomorph <- subset(Geomorph,
      time < as.POSIXct('2021-07-16 13:49:17', tz="UTC") & 
        time > as.POSIXct('2021-07-16 09:44:00', tz="UTC"))


Geomorph <- rbind(Geomorph_July9,Geomorph)

```

```{r add synop to df}
synop <- read.csv(here::here("Synoptic/COLMILLO_2021-08-30.csv"))
synop$X <- NULL

```

##Plot the geomorphology data in 3-d

```{r 3d plot no synop, echo=FALSE}


fig <- plot_ly(Geomorph, x = ~lat, y = ~lon, z = ~ele, size = 1
)
fig <- fig %>% add_markers()
#fig <- fig %>% add_trace(x = ~lat, y = ~lon, z = ~ele, #color = ~EOS_no#, colors = c('Blue','Yellow'),
#                         mode = 'markers')
fig <- fig %>% layout(scene = list(xaxis = list(title = 'lat'),
                                   yaxis = list(title = 'lon'),
                                   zaxis = list(title = 'elevation')))

fig


```

## Now Plot data in 3D including synoptic points


```{r 3d plot and synop, echo=FALSE}

df <- full_join(synop,Geomorph, by=c("lat","lon","ele")) 

fig <- plot_ly(df, x = ~lat, y = ~lon, z = ~ele, size = 1,
               marker = list(color = ~log10(CO2_ppm_ave), colorscale = c('#FFE1A1', '#683531'), showscale = TRUE)
            )
fig <- fig %>% add_markers()
#fig <- fig %>% add_trace(x = ~lat, y = ~lon, z = ~ele, #color = ~EOS_no#, colors = c('Blue','Yellow'),
#                         mode = 'markers')
fig <- fig %>% layout(scene = list(xaxis = list(title = 'lat'),
                                   yaxis = list(title = 'lon'),
                                   zaxis = list(title = 'elevation')))

fig
```
#are you seeing the problem? 
The synoptic data points seem to be fairly well geolocated for lat long, but not for elevation. 
So we need to build a smoothinf 

We need to 

#working with 3-D is hard. full stop.
In this code chunk, we start by smooting a line to the lat long data, which appears to be more accurate than the elevation

We will do this in parts though, be cause the relationship between lat lon can not be described as a function
```{r first spline, echo=FALSE}

#Cut up lat long into peices, and then fit spline


Geomorph_sub <-Geomorph %>% filter(lon >= -78.19302)
model <- lm(lon~bs(lat,
                   knots = c(-0.3164286,-0.3163748,-0.3162296,                          -0.3161252,-0.3161399,-.3156738,
   -0.3154703,-0.3152688,-0.3152838), 
                   degree = 3),
            data=Geomorph_sub)

latlims <- range(Geomorph_sub$lat)
lat.grid <- seq(from=latlims[1],to=latlims[2], by=.00001)
pred <-predict(model,newdata=list(lat=lat.grid),se=T)

plot(Geomorph_sub$lat,Geomorph_sub$lon,main="regressionSplinePLot")
lines(lat.grid,pred$fit,col='red',lwd=3)

fig<-plot_ly(data = Geomorph, x = ~lat, y = ~lon)

#this looks pretty good! So we will save the data in a data frame

lat <- lat.grid
lon <- pred$fit
df1<-as.data.frame(lat)
df1$lon <- lon
df1$num <- '1'
```
#next section is very small
```{r second spline, echo=FALSE}
Geomorph_sub <-Geomorph %>% filter(lon <= -78.19310 &
                                     lon >= -78.19333)

model <- lm(lon~bs(lat,
                   knots = c(0), 
                   degree = 3),
            data=Geomorph_sub)

latlims <- range(Geomorph_sub$lat)
lat.grid <- seq(from=latlims[1],to=latlims[2], by=.00001)
pred <-predict(model,newdata=list(lat=lat.grid),se=T)

plot(Geomorph$lat,Geomorph$lon,main="regressionSplinePLot")
lines(lat.grid,pred$fit,col='red',lwd=3)

lat <- lat.grid
lon <- pred$fit
df2<-as.data.frame(lat)
df2$lon <- lon
df2$num <- '2'
df2 <- df2[order(-lat),]

```
third section, here we go!

```{r third spline, echo=FALSE}

#Geomorph_sub <-Geomorph %>% filter(lon <= -78.19340)
Geomorph_sub <-Geomorph %>% filter(lon <= -78.19336)


model <- lm(lon~bs(lat,
                   knots = c(0), 
                   degree = 3),
            data=Geomorph_sub)

latlims <- range(Geomorph_sub$lat)
lat.grid <- seq(from=latlims[1],to=latlims[2], by=.00001)
pred <-predict(model,newdata=list(lat=lat.grid),se=T)

plot(Geomorph$lat,Geomorph$lon,main="regressionSplinePLot")
lines(lat.grid,pred$fit,col='red',lwd=3)

##dataframe 3
lat <- lat.grid
lon <- pred$fit
df3<-as.data.frame(lat)
df3$lon <- lon
df3$num <- '3'
##
```
good job! now lets bind all the dataframes together
```{r bind dataframes, echo=FALSE}

#now we need to make a dataframe that discribes this relationship between lat lon
df_prediction <- rbind(df1,df2,df3)


plot(df_prediction$lon~df_prediction$lat,col=df_prediction$num)

plot(Geomorph$lat,Geomorph$lon)

```

This is looking pretty darn good. But there is a gap in the lon data that we need to deal with. It's proving hard to deal with because this is not a function!

So we will add some data to the dataframe  to fill the gap.
Just a simple linear regression between the df1 and df3
```{r manual add dataframes}
#

# point1	-0.3152741	-78.19294	1
# point 2	-0.3152553	-78.19312 2

m = (-78.19312	- (-78.19294))/(-0.3152553 - (-0.3152741))

#slope = 3.597122
b = -78.19294 - m*(-0.3152741)

latlims <- range(Geomorph_sub$lat)
lat.grid <- seq(from=-0.3152741,to=-0.3152553, by=.000001)

##dataframe 4
lat <- lat.grid
df4<-as.data.frame(lat)
df4$lon <- m*df4$lat + b

df4 <-df4 %>% filter(lon <= -78.19302)

df4$num <- '4'
df4 <- df4[order(lat),]

```

ok, lets bind in that last dataframe

```{r bind dataframes, echo=FALSE}

#now we need to make a dataframe that discribes this relationship between lat lon
df_prediction <- rbind(df1,df4,df2,df3)

plot(df_prediction$lon~df_prediction$lat,col=df_prediction$num)

plot(Geomorph$lat,Geomorph$lon)

```
now we have a smooth data frame of lat/lon data, we calculate the distance between each point
```{r calc dist}

###create a loop and calculate distance along the river from the predict_df. THen we can bind in the GEOMORPH!
df_prediction <- rbind(df1,df4,df2,df3) %>% drop_na(lat)

df_prediction$num <- NULL
df_prediction <- df_prediction[,c("lon","lat")]
colnames(df_prediction) <- c("lon_fit","lat_fit")
df_prediction$lon_dist <- NA
df_prediction$lat_dist <- NA
i <- 2
for(i in 1:nrow(df_prediction)) {
  if (i == 1) {

      df_prediction$dist <- 0
#      df_prediction[i,"lon_dist"] <- 0
#      df_prediction[i,"lat_dist"] <- 0
      
    } else {
      df_prediction[i,"lon_dist"] <- df_prediction[i-1,"lon_fit"]
      df_prediction[i,"lat_dist"] <- df_prediction[i-1,"lat_fit"]
      df_prediction[i,"dist"] <- df_prediction[i-1,"dist"] + distHaversine(
        c(df_prediction[i,"lon_fit"], df_prediction[i,"lat_fit"]), 
        c(df_prediction[i,"lon_dist"], df_prediction[i,"lat_dist"]))
      }
}
```

snap the points in our origional dama frame to bring in the elevation data


```{r snap points to lat lon}


#df_prediction <- df_prediction[,c("lon","lat","num")] 
x <- SpatialPoints(Geomorph[,c(1:2)])
y <- SpatialPoints(df_prediction[,c(1:2)]) 
plot(x, col = "red")
points(y, col = "green")
snap = apply(spDists(x, y), 1, which.min)
points(y[snap,], pch = 3)


snap_df <- y[snap,]
coords_df <- snap_df@coords
pred <- as.data.frame(coords_df)
Geomorph$lon_fit <- pred$lon
Geomorph$lat_fit <- pred$lat


df_prediction <- full_join(df_prediction,Geomorph,by=c("lon_fit","lat_fit"))
```
first I need to make sure that what I have done really worked

```{r testing snap to line, echo=FALSE}


fig <- plot_ly(Geomorph, x = ~lat, y = ~lon, z = ~ele, size = 1)
fig <- fig %>% add_markers()
fig <- fig %>% add_trace(x = ~lat_fit, y = ~lon_fit, z = ~ele, colors = c('Yellow'),
                         mode = 'markers')
fig <- fig %>% layout(scene = list(xaxis = list(title = 'lat'),
                                   yaxis = list(title = 'lon'),
                                   zaxis = list(title = 'elevation')))

fig


```

ok sweet that looks really good

We also need to snap the synoptic df (for later)
```{r snap synop pts}

#df_prediction <- rbind(df1,df2,df3,df4)

#df_prediction <- df_prediction[,c("lon","lat","num")] 
x <- SpatialPoints(synop[,c(1:2)])
y <- SpatialPoints(df_prediction[,c(1:2)]) 
plot(x, col = "red")
points(y, col = "green")
snap = apply(spDists(x, y), 1, which.min)
points(y[snap,], pch = 3)


snap_df <- y[snap,]
coords_df <- snap_df@coords
pred <- as.data.frame(coords_df)
synop$lon_fit <- pred$lon
synop$lat_fit <- pred$lat
synop <- synop[,c("Date","EOS_no","Flux_ave","Tract","Point","CO2_ppm_ave","lon_fit","lat_fit")]


df_prediction <- full_join(df_prediction,synop,by=c("lon_fit","lat_fit"))
#Geomorph <- full_join(Geomorph,synop_2, by = c("lon_fit","lat_fit"))

```

##calculate distance between each coordinate.
Here's the deal. We need to calcualte the distance between each coordinate 

First, lets find the most western lat point



now we have created a distance column that we can plot the elevation data against. lets see how that looks

```{r plot dist v ele, echo = FALSE}

fig <- plot_ly(df_prediction, x = ~dist, y = ~ele, size = 1)
fig
```

kriddie, you are doing so good!
Okay, now lets fit another spline to this puppy

```{r another spline, echo=FALSE}


model <- lm(ele~bs(dist,
                   knots = c(0), 
                   degree = 10),
            data=df_prediction)

distlims <- range(df_prediction$dist)
dist.grid <- seq(from=distlims[1],to=distlims[2], by=.1)
pred <-predict(model,newdata=list(dist=dist.grid),se=T)

plot(df_prediction$dist,df_prediction$ele)
lines(dist.grid,pred$fit,col='red',lwd=3)

dist <- dist.grid
ele <- pred$fit
ele_fit<-as.data.frame(dist)
ele_fit$ele <- ele

```
##loess spline
i think loess might be a little better for this?

```{r diff way}

fit <- loess(ele ~ dist, degree=2, span = 0.30, data=df_prediction)

df_prediction %>% 
  drop_na(ele) %>%
  mutate(smooth = fit$fitted) %>%
  ggplot(aes(dist, ele)) +
  geom_point(size = 3, alpha = .5, color = "grey") +
  geom_line(aes(dist, smooth), color="red")


```

take the loess spline and make a data frame that interpolates these data points

```{r interpolate loess, echo=FALSE}

fit <- loess(ele ~ dist, degree=2, span = 0.30, data=df_prediction)
distlims <- range(df_prediction$dist)


pred1 <- predict(fit, data.frame(dist = df_prediction$dist), se = TRUE)

df_prediction$ele_fit <- pred1$fit

ggplot(data=df_prediction%>%drop_na(Flux_ave), aes(dist, ele_fit, color=CO2_ppm_ave)) +
  geom_point()

#ggplot(data=df_prediction, aes(dist, ele_fit, col="CO2_ppm_ave")) +
 # geom_point(size = 3, alpha = .5, color = "blue")



```




i said plot it!
```{r plot that fucker, echo=FALSE}


fit <- loess(ele ~ dist, degree=2, span = 0.30, data=df_prediction)

df_prediction %>% 
  drop_na(Flux_ave) %>%
  mutate(smooth = fit$fitted) %>%
  ggplot(aes(dist, ele_fit, color = CO2_ppm_ave)) +
  geom_point(size = 3, alpha = .5) +
  scale_color_continuous(low="thistle2", high="darkred", 
                       guide="colorbar",na.value="") +
  geom_line(aes(dist, smooth), color="blue")



df_prediction %>% 
  drop_na(Flux_ave) %>%
  mutate(smooth = fit$fitted) %>%
  ggplot(aes(dist, ele_fit, color = Flux_ave)) +
  geom_point(size = 3, alpha = .5) +
  scale_color_continuous(low="green", high="darkred", 
                       guide="colorbar",na.value="") +
  geom_line(aes(dist, smooth), color="blue")


#ggplot(data=df_prediction%>%drop_na(Flux_ave), aes(dist, ele_fit, color=CO2_ppm_ave)) +
#  geom_point()



```


```
