---
title: "Geomorphology_COLM"
author: "KWhitmore"
date: "12/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(lubridate)
library(plotly)
library(dplyr)
library(tidyr)
library(zoo)
library(plot3D)
library(splines)
library(Ecdat)
library(dplyr)
library(sp)
library(geosphere)
library("gridExtra")  

```

## BUild the geomorphology data frame for Colmillo

```{r build df 2021-07-09}

Geomorph <- read.csv(here::here("/Geomorphology/Colmillo/2021-07-09 11_20_03 CANINE Stream Profile.csv"), skip = 42)


Geomorph <- Geomorph[,3:6]

#convert time in UTC to local time
Geomorph$time <- gsub("T"," ", Geomorph$time)
Geomorph$time <- gsub("Z","", Geomorph$time)

Geomorph$time <- as.POSIXct(Geomorph$time, format = "%Y-%m-%d %H:%M:%S", tz = "UTC" )
Geomorph$time <-Geomorph$time - 5*60*60 
#round to nearest half second
Geomorph$time <- round_date(Geomorph$time, unit = "30 second")

# 2021-07-16 START: 11:29:03  END:  15:24:37
Geomorph <- subset(Geomorph,
      time > as.POSIXct('2021-07-09 11:29:03', tz="UTC") & 
        time < as.POSIXct('2021-07-09 15:24:37', tz="UTC"))

Geomorph_July9 <- Geomorph

```

```{r build df 2021-07-16}


Geomorph <- read.csv(here::here("/Geomorphology/Colmillo/COLMILLO 2021-07-16.csv"), skip = 42)
Geomorph <- Geomorph[,3:6]

#convert time in UTC to local time
Geomorph$time <- gsub("T"," ", Geomorph$time)
Geomorph$time <- gsub("Z","", Geomorph$time)

Geomorph$time <- as.POSIXct(Geomorph$time, format = "%Y-%m-%d %H:%M:%S", tz = "UTC" )
Geomorph$time <-Geomorph$time - 5*60*60 
#round to nearest half second
Geomorph$time <- round_date(Geomorph$time, unit = "30 second")

# 2021-07-16 START: 09:45:00  END:  13:49:17
Geomorph <- subset(Geomorph,
      time < as.POSIXct('2021-07-16 13:49:17', tz="UTC") & 
        time > as.POSIXct('2021-07-16 09:44:00', tz="UTC"))


Geomorph <- rbind(Geomorph_July9,Geomorph)

```



##Plot the geomorphology data in 3-d

```{r 3d plot no synop, echo=FALSE}


fig <- plot_ly(Geomorph, x = ~lat, y = ~lon, z = ~ele, size = 1
)
fig <- fig %>% add_markers()
#fig <- fig %>% add_trace(x = ~lat, y = ~lon, z = ~ele, #color = ~EOS_no#, colors = c('Blue','Yellow'),
#                         mode = 'markers')
fig <- fig %>% layout(scene = list(xaxis = list(title = 'lat'),
                                   yaxis = list(title = 'lon'),
                                   zaxis = list(title = 'elevation')))

fig


```

## Now Plot data in 3D including synoptic points



#are you seeing the problem? 
The synoptic data points seem to be fairly well geolocated for lat long, but not for elevation. Emphasise on fairly well, because these synoptics look a bit worse than ANTENAS. Unfortunatly.

So we need to build a smoothing function 

#working with 3-D is hard. full stop.
In this code chunk, we start by smooting a line to the lat lon data, which appears to be more accurate than the elevation

We will do this in parts though, be cause the relationship between lat lon can not be described as a function

Colmillo is not too far off from a funtion if lat is the "x" and lon is the 'y'
```{r first spline, echo=FALSE}

#Cut up lat long into peices, and then fit spline


Geomorph_sub <-Geomorph #%>% filter(lon >= -78.19302)
model <- lm(lon~bs(lat,
              #     knots = c(-0.3164286,-0.3163748,-0.3162296,                          -0.3161252,-0.3161399,-.3156738, -0.3154703,-0.3152688,-0.3152838), 
                   degree = 50),
            data=Geomorph_sub)

latlims <- range(Geomorph_sub$lat)
lat.grid <- seq(from=latlims[1],to=latlims[2], by=.00001)
pred <-predict(model,newdata=list(lat=lat.grid),se=T)

plot(Geomorph_sub$lat,Geomorph_sub$lon,main="regressionSplinePLot")
lines(lat.grid,pred$fit,col='red',lwd=3)

fig<-plot_ly(data = Geomorph_sub, x = ~lat, y = ~lon)

#this looks pretty good! So we will save the data in a data frame

lat <- lat.grid
lon <- pred$fit
df1<-as.data.frame(lat)
df1$lon <- lon
df1$num <- '1'
```

Wow! that was so much easier than antenas!! Amazing.

```{r bind dataframes, echo=FALSE}

#now we need to make a dataframe that discribes this relationship between lat lon
df_prediction <- df1

plot(df_prediction$lon~df_prediction$lat,col=df_prediction$num)

plot(Geomorph$lat,Geomorph$lon)

```

now we have a smooth data frame of lat/lon data, we calculate the distance between each point

```{r calc dist}

###create a loop and calculate distance along the river from the predict_df. THen we can bind in the GEOMORPH!
#df_prediction <- rbind(df1,df4,df2,df3) %>% drop_na(lat)
df_prediction <- df1

df_prediction$num <- NULL
#df_prediction <- df_prediction[,c("lon","lat")]
colnames(df_prediction) <- c("lat_fit","lon_fit")
df_prediction$lon_dist <- NA
df_prediction$lat_dist <- NA
i <- 2
for(i in 1:nrow(df_prediction)) {
  if (i == 1) {

      df_prediction$dist <- 0
#      df_prediction[i,"lon_dist"] <- 0
#      df_prediction[i,"lat_dist"] <- 0
      
    } else {
      df_prediction[i,"lon_dist"] <- df_prediction[i-1,"lon_fit"]
      df_prediction[i,"lat_dist"] <- df_prediction[i-1,"lat_fit"]
      df_prediction[i,"dist"] <- df_prediction[i-1,"dist"] + distHaversine(
        c(df_prediction[i,"lon_fit"], df_prediction[i,"lat_fit"]), 
        c(df_prediction[i,"lon_dist"], df_prediction[i,"lat_dist"]))
      }
}
```

snap the points in our origional dama frame to bring in the elevation data


```{r add synop to lat lon}
#synop <- read.csv(here::here("Synoptic/COLMILLO_2021-08-30.csv"))
#synop <- read.csv(here::here("Synoptic/COLMILLO_2022-01-27.csv"))
synop <- read.csv(here::here("Synoptic/COLMILLO_2022-02-14.csv"))

synop$X <- NULL

#df_prediction <- df_prediction[,c("lon_fit","lat_fit","ele")] 
x <- SpatialPoints(Geomorph[,c(1:2)])
y <- SpatialPoints(df_prediction[,c(1:2)]) 
plot(y, col = "red")
points(y, col = "green")
snap = apply(spDists(x, y), 1, which.min)
points(y[snap,], pch = 3)


snap_df <- y[snap,]
coords_df <- snap_df@coords
pred <- as.data.frame(coords_df)
Geomorph$lon_fit <- pred$lon
Geomorph$lat_fit <- pred$lat


df_prediction <- full_join(df_prediction,Geomorph,by=c("lon_fit","lat_fit"))
```
```{r 3d plot and synop, echo=FALSE}

df <- full_join(synop,Geomorph, by=c("lat","lon","ele")) 

fig <- plot_ly(df, x = ~lat, y = ~lon, z = ~ele, size = 1,
               marker = list(color = ~log10(CO2_ppm_ave), colorscale = c('#FFE1A1', '#683531'), showscale = TRUE)
            )
fig <- fig %>% add_markers()
#fig <- fig %>% add_trace(x = ~lat, y = ~lon, z = ~ele, #color = ~EOS_no#, colors = c('Blue','Yellow'),
#                         mode = 'markers')
fig <- fig %>% layout(scene = list(xaxis = list(title = 'lat'),
                                   yaxis = list(title = 'lon'),
                                   zaxis = list(title = 'elevation')))

fig
```
plot in 3d

```{r testing snap to line, echo=FALSE}


fig <- plot_ly(Geomorph, x = ~lat, y = ~lon, z = ~ele, size = 1)
fig <- fig %>% add_markers()
fig <- fig %>% add_trace(x = ~lat_fit, y = ~lon_fit, z = ~ele, colors = c('Yellow'),
                         mode = 'markers')
fig <- fig %>% layout(scene = list(xaxis = list(title = 'lat'),
                                   yaxis = list(title = 'lon'),
                                   zaxis = list(title = 'elevation')))

fig


```

ok sweet that looks really good

We also need to snap the synoptic df (for later)
```{r snap synop pts}

#df_prediction <- rbind(df1,df2,df3,df4)

#df_prediction <- df_prediction[,c("lon","lat","num")] 
x <- SpatialPoints(synop[,c(1:2)])
y <- SpatialPoints(df_prediction[,c(1:2)]) 
plot(x, col = "red")
points(y, col = "green")
snap = apply(spDists(x, y), 1, which.min)
points(y[snap,], pch = 3)


snap_df <- y[snap,]
coords_df <- snap_df@coords
pred <- as.data.frame(coords_df)
synop$lon_fit <- pred$lon
synop$lat_fit <- pred$lat
synop <- synop[,c("Date","EOS_no","Flux_ave","Point","CO2_ppm_ave","adjusted_ppm","lon_fit","lat_fit","AirTemp_c","VaisalaType","Total_hPa","COLM_waterTempAve")]

df_prediction <- full_join(df_prediction,synop,by=c("lon_fit","lat_fit"))


#Geomorph <- full_join(Geomorph,synop_2, by = c("lon_fit","lat_fit"))

```

##calculate distance between each coordinate.
Here's the deal. We need to calcualte the distance between each coordinate 

First, lets find the most western lat point



now we have created a distance column that we can plot the elevation data against. lets see how that looks

```{r plot dist v ele, echo = FALSE}

fig <- plot_ly(df_prediction, x = ~dist, y = ~ele, size = 1)
fig
```

kriddie, you are doing so good!
Okay, now lets fit another spline to this puppy


* deleted other type of spline



##loess spline
i think loess might be a little better for this? IT IS BETTER!

```{r diff way}

df_prediction <- df_prediction %>% filter(dist > 0)

fit <- loess(ele ~ dist, degree=2, span = 0.20, data=df_prediction)

df_prediction %>% 
  drop_na(ele) %>%
  mutate(smooth = fit$fitted) %>%
  ggplot(aes(dist, ele)) +
  geom_point(size = 3, alpha = .5, color = "grey") +
  geom_line(aes(dist, smooth), color="red")

fit <- loess(ele ~ dist, degree=2, span = 0.30, data=df_prediction)
distlims <- range(df_prediction$dist)


pred1 <- predict(fit, data.frame(dist = df_prediction$dist), se = TRUE)

df_prediction$ele_fit <- pred1$fit
#save <- df_prediction
df_prediction <- save
```

```{r fix some slope problems, echo=FALSE}

## there are problems in the middle 

up <- which.min(abs(df_prediction$dist-256.6658))
down <- which.min(abs(df_prediction$dist-223))

slope <- (df_prediction[down,"ele_fit"] - df_prediction[up,"ele_fit"])/(df_prediction[down,"dist"] - df_prediction[up,"dist"])
b = df_prediction[up,"ele_fit"] - slope*df_prediction[up,"dist"]
df_prediction_a <- df_prediction %>% 
  filter(dist > df_prediction[down,"dist"] & dist < df_prediction[up,"dist"])
df_prediction_b <- df_prediction %>% 
  filter(dist > df_prediction[up,"dist"] | dist < df_prediction[down,"dist"])
df_prediction_a$ele_fit <- slope*df_prediction_a$dist + b
df_prediction <- rbind(df_prediction_a,df_prediction_b)
rm(df_prediction_a,df_prediction_b)


## there are problems in the middle 

up <- which.min(abs(df_prediction$dist-315.0067))
down <- which.min(abs(df_prediction$dist-264.4607))

slope <- (df_prediction[down,"ele_fit"] - df_prediction[up,"ele_fit"])/(df_prediction[down,"dist"] - df_prediction[up,"dist"])
b = df_prediction[up,"ele_fit"] - slope*df_prediction[up,"dist"]
df_prediction_a <- df_prediction %>% 
  filter(dist > df_prediction[down,"dist"] & dist < df_prediction[up,"dist"])
df_prediction_b <- df_prediction %>% 
  filter(dist > df_prediction[up,"dist"] | dist < df_prediction[down,"dist"])
df_prediction_a$ele_fit <- slope*df_prediction_a$dist + b
df_prediction <- rbind(df_prediction_a,df_prediction_b)
rm(df_prediction_a,df_prediction_b)

```


```{r calc slope, echo=FALSE}

df_prediction$slope <- NA
for(i in 1:nrow(df_prediction)) {       # for-loop over rows
  df_prediction$dist_down[i] <- df_prediction$dist[i+1]
  df_prediction$ele_down[i] <- df_prediction$ele_fit[i+1]
}

df_prediction$slope <- (df_prediction$ele_fit - df_prediction$ele_down)/(df_prediction$dist - df_prediction$dist_down)
df_prediction$dist_down <- NULL
df_prediction$ele_down <- NULL

df_predictionblah <- df_prediction%>%filter(slope<0)

###
df_prediction <- df_prediction[order(df_prediction$dist),]
df_prediction$slope <- NA
loop <- df_prediction%>%drop_na(ele_fit)
for(i in 1:nrow(loop)) {       # for-loop over rows
  x = loop$dist[i] - 5
  loop$ele_minus[i] <- loop[which.min(abs(loop$dist-x)),]$ele_fit
  loop$dist_minus[i] <- loop[which.min(abs(loop$dist-x)),]$dist
  
  y = loop$dist[i] + 5
  loop$ele_plus[i] <- loop[which.min(abs(loop$dist-y)),]$ele_fit
  loop$dist_plus[i] <- loop[which.min(abs(loop$dist-y)),]$dist
  
  loop$slope <- -1*(loop$ele_minus-loop$ele_plus)/(loop$dist_minus-loop$dist_plus)
  
}
loop$dist_minus <- NULL
loop$dist_plus <- NULL
loop$ele_minus <- NULL
loop$ele_plus <- NULL

df_prediction <- loop 

```

take the loess spline and make a data frame that interpolates these data points

```{r interpolate loess, echo=FALSE}

flux <- ggplot(data=df_prediction %>%drop_na(Flux_ave), aes(dist, ele_fit, color=Flux_ave)) +
  geom_point()
CO2 <- ggplot(data=df_prediction %>%drop_na(Flux_ave), aes(dist, ele_fit, color=adjusted_ppm)) +
  geom_point()

grid.arrange(flux, CO2, ncol=1)
```




```{r write, echo=FALSE}

write.csv(df_prediction, here::here("ProcessedData/COLMILLO_synoptic_2022-02-17.csv"))
```


```{r 3d plot just synop, echo=FALSE}


fig <- plot_ly(df_prediction)
fig <- fig %>% add_trace(x = ~lat_fit, y = ~lon_fit, z = ~ele_fit, opacity = .05, size =1,type = 'scatter', mode = 'lines')
fig <- fig %>% add_markers(df_prediction%>%drop_na(Flux_ave), x = ~lat_fit, y = ~lon_fit, z = ~ele_fit, color = ~CO2_ppm_ave,opacity = 1)
fig <- fig %>% layout(scene = list(xaxis = list(title = 'lat'),
                                   yaxis = list(title = 'lon'),
                                   zaxis = list(title = 'elevation')))

fig



```
