---
title: "Geomorphology_GAVI"
author: "KWhitmore"
date: "12/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(lubridate)
library(plotly)
library(dplyr)
library(tidyr)
library(zoo)
library(plot3D)
library(splines)
library(Ecdat)
library(dplyr)
library(sp)
library(geosphere)


```

## BUild the geomorphology data frame for Ante mainstem

2021-07-26 9:50
```{r build df 2021-07-23}

Geomorph <- read.csv(here::here("/Geomorphology/Garmin_ALL/Internal Storage.csv"), skip = 28)


Geomorph <- Geomorph[,2:5]

#convert time in UTC to local time
Geomorph$time <- gsub("T"," ", Geomorph$time)
Geomorph$time <- gsub("Z","", Geomorph$time)

Geomorph$time <- as.POSIXct(Geomorph$time, format = "%Y-%m-%d %H:%M:%S", tz = "UTC" )
Geomorph$time <-Geomorph$time - 5*60*60 
#round to nearest half second
Geomorph$time <- round_date(Geomorph$time, unit = "30 second")

# 2021-07-23 START: 12:01:00  END:  12:33:37
Geomorph_July23 <- subset(Geomorph,
      time > as.POSIXct('2021-07-23 12:01:00', tz="UTC") & 
        time < as.POSIXct('2021-07-23 12:35:00', tz="UTC"))

```

```{r build df 2021-07-26}

Geomorph <- read.csv(here::here("/Geomorphology/Gavilan/GAVI_2021-07-26 09_49_22 Day.csv"), skip = 42)


Geomorph <- Geomorph[,3:6]

#convert time in UTC to local time
Geomorph$time <- gsub("T"," ", Geomorph$time)
Geomorph$time <- gsub("Z","", Geomorph$time)

Geomorph$time <- as.POSIXct(Geomorph$time, format = "%Y-%m-%d %H:%M:%S", tz = "UTC" )
Geomorph$time <-Geomorph$time - 5*60*60 
#round to nearest half second
Geomorph$time <- round_date(Geomorph$time, unit = "30 second")

# 2021-07-26 START: 09:50:03  END:  15:24:37
Geomorph <- subset(Geomorph,
      time > as.POSIXct('2021-07-26 09:50:03', tz="UTC") & 
        time < as.POSIXct('2021-07-26 14:45:00', tz="UTC"))

Geomorph_July26 <- Geomorph

```

```{r build df 2021-07-28}


Geomorph <- read.csv(here::here("/Geomorphology/Gavilan/Gavi_2021-07-28 14_01_03 Day.csv"), skip = 42)
Geomorph <- Geomorph[,3:6]

#convert time in UTC to local time
Geomorph$time <- gsub("T"," ", Geomorph$time)
Geomorph$time <- gsub("Z","", Geomorph$time)

Geomorph$time <- as.POSIXct(Geomorph$time, format = "%Y-%m-%d %H:%M:%S", tz = "UTC" )
Geomorph$time <-Geomorph$time - 5*60*60 
#round to nearest half second
Geomorph$time <- round_date(Geomorph$time, unit = "30 second")

# 2021-07-2 START: 14:04:28   END: 15:29:13Z 13:49:17
Geomorph_July28 <- subset(Geomorph,
      time > as.POSIXct('2021-07-28 14:46:17', tz="UTC") & 
        time < as.POSIXct('2021-07-28 15:29:00', tz="UTC"))


Geomorph <- rbind(Geomorph_July26,Geomorph_July28, Geomorph_July23)

Geomorph$lat <- as.numeric(Geomorph$lat)
Geomorph$lon <- as.numeric(Geomorph$lon)
Geomorph$ele <- as.numeric(Geomorph$ele)
```

```{r add synop to df}
synop <- read.csv(here::here("Synoptic/GAVI_mainstem_2021-08-29.csv"))
synop$X <- NULL

colnames(synop) <- c("lat","lon","Date","Eos_no","Flux_ave", "Tract","Point","CO2_ppm_ave")
```

##Plot the geomorphology data in 3-d

```{r 3d plot no synop, echo=FALSE}


fig <- plot_ly(Geomorph, x = ~lat, y = ~lon, z = ~ele, size = 1
)
fig <- fig %>% add_markers()
#fig <- fig %>% add_trace(x = ~lat, y = ~lon, z = ~ele, #color = ~EOS_no#, colors = c('Blue','Yellow'),
#                         mode = 'markers')
fig <- fig %>% layout(scene = list(xaxis = list(title = 'lat'),
                                   yaxis = list(title = 'lon'),
                                   zaxis = list(title = 'elevation')))

fig


```

## Now Plot data in 3D including synoptic points


```{r 3d plot and synop, echo=FALSE}

df <- full_join(synop,Geomorph, by=c("lat","lon")) 

fig <- plot_ly(df, x = ~lat, y = ~lon, z = ~ele, size = 1,
               marker = list(color = ~CO2_ppm_ave, colorscale = c('#FFE1A1', '#683531'), showscale = TRUE))

#FFE1A1 #683531

fig <- fig %>% add_markers()
#fig <- fig %>% add_trace(x = ~lat, y = ~lon, z = ~ele, #color = ~EOS_no#, colors = c('Blue','Yellow'),
#                         mode = 'markers')
fig <- fig %>% layout(scene = list(xaxis = list(title = 'lat'),
                                   yaxis = list(title = 'lon'),
                                   zaxis = list(title = 'elevation')))

fig

TrackMap <- qmplot(lon, lat, data = df, zoom = 13,
                   maptype = "toner-background", color=ele)

TrackMap
```
#are you seeing the problem? 
The synoptic data points seem to be fairly well geolocated for lat long, but not for elevation. Emphasise on fairly well, because these synoptics look a bit worse than ANTENAS. Unfortunatly.

So we need to build a smoothing function 

#working with 3-D is hard. full stop.
In this code chunk, we start by smooting a line to the lat lon data, which appears to be more accurate than the elevation

We will do this in parts though, be cause the relationship between lat lon can not be described as a function

Colmillo is not too far off from a funtion if lat is the "x" and lon is the 'y'
```{r first spline, echo=FALSE}

#Cut up lat long into peices, and then fit spline


Geomorph_sub <-Geomorph #%>% filter(lon >= -78.19302)
model <- lm(lon~bs(lat,
              #     knots = c(-0.3164286,-0.3163748,-0.3162296,                          -0.3161252,-0.3161399,-.3156738, -0.3154703,-0.3152688,-0.3152838), 
                   degree = 50),
            data=Geomorph_sub)

latlims <- range(Geomorph_sub$lat)
lat.grid <- seq(from=latlims[1],to=latlims[2], by=.00001)
pred <-predict(model,newdata=list(lat=lat.grid),se=T)

plot(Geomorph_sub$lat,Geomorph_sub$lon,main="regressionSplinePLot")
lines(lat.grid,pred$fit,col='red',lwd=3)

fig<-plot_ly(data = Geomorph_sub, x = ~lat, y = ~lon)

#this looks pretty good! So we will save the data in a data frame

lat <- lat.grid
lon <- pred$fit
df1<-as.data.frame(lat)
df1$lon <- lon
df1$num <- '1'
```

Wow! that was so much easier than antenas!! Amazing.

```{r bind dataframes, echo=FALSE}

#now we need to make a dataframe that discribes this relationship between lat lon
df_prediction <- df1

plot(df_prediction$lon~df_prediction$lat,col=df_prediction$num)

plot(Geomorph$lat,Geomorph$lon)

```

now we have a smooth data frame of lat/lon data, we calculate the distance between each point

```{r calc dist}

###create a loop and calculate distance along the river from the predict_df. THen we can bind in the GEOMORPH!
#df_prediction <- rbind(df1,df4,df2,df3) %>% drop_na(lat)
df_prediction <- df1

df_prediction$num <- NULL
#df_prediction <- df_prediction[,c("lon","lat")]
colnames(df_prediction) <- c("lat_fit","lon_fit")
df_prediction$lon_dist <- NA
df_prediction$lat_dist <- NA
i <- 2
for(i in 1:nrow(df_prediction)) {
  if (i == 1) {

      df_prediction$dist <- 0
#      df_prediction[i,"lon_dist"] <- 0
#      df_prediction[i,"lat_dist"] <- 0
      
    } else {
      df_prediction[i,"lon_dist"] <- df_prediction[i-1,"lon_fit"]
      df_prediction[i,"lat_dist"] <- df_prediction[i-1,"lat_fit"]
      df_prediction[i,"dist"] <- df_prediction[i-1,"dist"] + distHaversine(
        c(df_prediction[i,"lon_fit"], df_prediction[i,"lat_fit"]), 
        c(df_prediction[i,"lon_dist"], df_prediction[i,"lat_dist"]))
      }
}
```

snap the points in our origional dama frame to bring in the elevation data


```{r snap points to lat lon}


#df_prediction <- df_prediction[,c("lon_fit","lat_fit","ele")] 
x <- SpatialPoints(Geomorph[,c(1:2)])
y <- SpatialPoints(df_prediction[,c(1:2)]) 
plot(y, col = "red")
points(y, col = "green")
snap = apply(spDists(x, y), 1, which.min)
points(y[snap,], pch = 3)


snap_df <- y[snap,]
coords_df <- snap_df@coords
pred <- as.data.frame(coords_df)
Geomorph$lon_fit <- pred$lon
Geomorph$lat_fit <- pred$lat


df_prediction <- full_join(df_prediction,Geomorph,by=c("lon_fit","lat_fit"))
```
first I need to make sure that what I have done really worked

```{r testing snap to line, echo=FALSE}


fig <- plot_ly(Geomorph, x = ~lat, y = ~lon, z = ~ele, size = 1)
fig <- fig %>% add_markers()
fig <- fig %>% add_trace(x = ~lat_fit, y = ~lon_fit, z = ~ele, colors = c('Yellow'),
                         mode = 'markers')
fig <- fig %>% layout(scene = list(xaxis = list(title = 'lat'),
                                   yaxis = list(title = 'lon'),
                                   zaxis = list(title = 'elevation')))

fig


```

ok sweet that looks really good

We also need to snap the synoptic df (for later)
```{r snap synop pts}

#df_prediction <- rbind(df1,df2,df3,df4)

#df_prediction <- df_prediction[,c("lon","lat","num")] 
x <- SpatialPoints(synop[,c(1:2)])
y <- SpatialPoints(df_prediction[,c(1:2)]) 
plot(x, col = "red")
points(y, col = "green")
snap = apply(spDists(x, y), 1, which.min)
points(y[snap,], pch = 3)


snap_df <- y[snap,]
coords_df <- snap_df@coords
pred <- as.data.frame(coords_df)
synop$lon_fit <- pred$lon
synop$lat_fit <- pred$lat
synop <- synop[,c("Date","EOS_no","Flux_ave","Point","CO2_ppm_ave","lon_fit","lat_fit")]


df_prediction <- full_join(df_prediction,synop,by=c("lon_fit","lat_fit"))


#Geomorph <- full_join(Geomorph,synop_2, by = c("lon_fit","lat_fit"))

```

##calculate distance between each coordinate.
Here's the deal. We need to calcualte the distance between each coordinate 

First, lets find the most western lat point



now we have created a distance column that we can plot the elevation data against. lets see how that looks

```{r plot dist v ele, echo = FALSE}

fig <- plot_ly(df_prediction, x = ~dist, y = ~ele, size = 1)
fig
```

kriddie, you are doing so good!
Okay, now lets fit another spline to this puppy

```{r another spline, echo=FALSE}
df_prediction <- df_prediction %>% filter(dist > 0)

model <- lm(ele~bs(dist,
                   knots = c(395), 
                   degree = 10),
            data=df_prediction)

distlims <- range(df_prediction$dist)
dist.grid <- seq(from=distlims[1],to=distlims[2], by=.1)
pred <-predict(model,newdata=list(dist=dist.grid),se=T)

plot(df_prediction$dist,df_prediction$ele)
lines(dist.grid,pred$fit,col='red',lwd=3)

dist <- dist.grid
ele <- pred$fit
ele_fit<-as.data.frame(dist)
ele_fit$ele <- ele

```
##loess spline
i think loess might be a little better for this? IT IS BETTER!

```{r diff way}

df_prediction <- df_prediction %>% filter(dist > 0)

fit <- loess(ele ~ dist, degree=2, span = 0.30, data=df_prediction)

df_prediction %>% 
  drop_na(ele) %>%
  mutate(smooth = fit$fitted) %>%
  ggplot(aes(dist, ele)) +
  geom_point(size = 3, alpha = .5, color = "grey") +
  geom_line(aes(dist, smooth), color="red")


```

take the loess spline and make a data frame that interpolates these data points

```{r interpolate loess, echo=FALSE}

fit <- loess(ele ~ dist, degree=2, span = 0.30, data=df_prediction)
distlims <- range(df_prediction$dist)


pred1 <- predict(fit, data.frame(dist = df_prediction$dist), se = TRUE)

df_prediction$ele_fit <- pred1$fit

ggplot(data=df_prediction%>%drop_na(Flux_ave), aes(dist, ele_fit, color=CO2_ppm_ave)) +
  geom_point()

#ggplot(data=df_prediction, aes(dist, ele_fit, col="CO2_ppm_ave")) +
 # geom_point(size = 3, alpha = .5, color = "blue")



```

