---
title: 'Long Term Data: Station02'
author: "Kriddie"
date: "2022-11-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

long term data for station 1

```{r library}
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyverse)
library(plotly)
library(here)
library(dplyr)
library(reshape2)
library(purrr)
library(sjmisc)
library(ggpubr)
library(gridExtra)
```

##read in wl02

```{r Hobo WL}
#First the Hobos

setwd(here::here("WaterLevel"))
all_files=list.files(pattern=".csv") #pulls out the csv files from CO2 folder
sites_rp = sub('_[^_]+$', '', all_files)
site_names=unique(sites_rp) #creates list of site names for following loop

site_names = "WL_02"
#site_names = site_names[c(2,3,5,6)]

#rm old files, if they exist
rm(WLData)
rm(Temp_WLData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("WLData")){
      WLData <- read.csv(file, skip=1, header = FALSE, sep = ",",
                         quote = "\"",dec = ".", fill = TRUE, comment.char = "")
      
      if(str_contains(WLData[1,3],"Abs Pres, psi")){
        WLData <- WLData[-1,]
        colnames(WLData)=c("row","DateTime","WLPres_kpa","WLTemp_c")
        WLData <- WLData[2:4]
        WLData$WLPres_kpa <- as.numeric(as.character(WLData$WLPres_kpa), digits=6)
        WLData$WLTemp_c <- as.numeric(as.character(WLData$WLTemp_c), digits=5)
        WLData$WLPres_kpa <- WLData$WLPres_kpa*6.89476
        WLData$WLTemp_c <- (WLData$WLTemp_c - 32)/1.8000

      } else { 
        WLData <- WLData[-1,]
        colnames(WLData)=c("row","DateTime","WLPres_kpa","WLTemp_c")
        WLData <- WLData[2:4]
        WLData$WLPres_kpa <- as.numeric(as.character(WLData$WLPres_kpa), digits=6)
        WLData$WLTemp_c <- as.numeric(as.character(WLData$WLTemp_c), digits=5)
        }
      
#      WLData$DateTime <- as.POSIXct(WLData$DateTime, format="%m/%d/%y %I:%M:%S %p", tz="UTC")
    WLData$DateTime <- as.POSIXct(WLData$DateTime, tz="UTC",
           tryFormats = c("%m/%d/%y %I:%M:%S %p",
                          "%m/%d/%Y %H:%M"))
    }
    if (exists("WLData")){
      Temp_WLData <- read.csv(file, skip=1, header = FALSE, sep = ",",
                              quote = "\"",dec = ".", fill = TRUE, comment.char = "")  
#      
      
      if(str_contains(Temp_WLData[1,3],"Abs Pres, psi")){
        Temp_WLData <- Temp_WLData[-1,]
        colnames(Temp_WLData)=c("row","DateTime","WLPres_kpa","WLTemp_c")
        Temp_WLData <- Temp_WLData[2:4]
        Temp_WLData$WLPres_kpa <- as.numeric(as.character(Temp_WLData$WLPres_kpa), digits=6)
        Temp_WLData$WLTemp_c <- as.numeric(as.character(Temp_WLData$WLTemp_c), digits=5)
        Temp_WLData$WLPres_kpa <- Temp_WLData$WLPres_kpa*6.89476
        Temp_WLData$WLTemp_c <- (Temp_WLData$WLTemp_c - 32)/1.8000
        
        
      } else { 
        Temp_WLData <- Temp_WLData[-1,]
        colnames(Temp_WLData)=c("row","DateTime","WLPres_kpa","WLTemp_c")
        Temp_WLData <- Temp_WLData[2:4]
        Temp_WLData$WLPres_kpa <- as.numeric(as.character(Temp_WLData$WLPres_kpa), digits=6)
        Temp_WLData$WLTemp_c <- as.numeric(as.character(Temp_WLData$WLTemp_c), digits=5)
        }
      
#      Temp_WLData$DateTime <- as.POSIXct(Temp_WLData$DateTime, format="%m/%d/%y %I:%M:%S %p", tz="UTC")
          Temp_WLData$DateTime <- as.POSIXct(Temp_WLData$DateTime, tz="UTC",
           tryFormats = c("%m/%d/%y %I:%M:%S %p",
                          "%m/%d/%Y %H:%M"))
      
      
      WLData <- rbind(WLData, Temp_WLData)
      rm(Temp_WLData)
    }
    
  }
  WLData$DateTime <- round_date(WLData$DateTime, "15 mins")
  WLData$Station <- "Stn02"
  WLData=unique(WLData)
  assign((paste(site,sep="_")),WLData) #creates object with new appended data
  rm(WLData) #removes WLdata so that multiple sites aren't appended together
}

WL_02 <- WL_02%>%filter(WLPres_kpa != 62.566)
```
## plot 
plot the water level so that each station data can be cleaned

```{r plot, echo=FALSE}

##clean data

plot_ly(WL_02, x = ~DateTime, y = ~WLPres_kpa, type = 'scatter', mode = 'markers') 

```




```{r clean, echo=FALSE}

WL_02 <- WL_02%>%filter(DateTime != as.POSIXct("2022-06-30 13:30", tz="UTC"))%>%filter(DateTime != as.POSIXct("2022-07-12 10:30", tz="UTC"))

#Looks like there was a shift during the last download of 2022 field seaseon. entonces:
#64.347 - 62.987

#this is hard - it looks like the sensor moved 2x, once on the first dl of the field season, again in October during dl, not only that, it seems like the baseline has moved or something--- could logger be out of the water??

#WL_02$test <- WL_02$WLPres_kpa

#below is the best I got o far
WL_02[which(WL_02$DateTime > as.POSIXct("2022-07-27 10:15:00", tz="UTC")&WL_02$DateTime < as.POSIXct("2022-10-12 13:45:00", tz="UTC")),]$WLPres_kpa <- 
  WL_02[which(WL_02$DateTime > as.POSIXct("2022-07-27 10:15:00", tz="UTC")&WL_02$DateTime < as.POSIXct("2022-10-12 13:45:00", tz="UTC")),]$WLPres_kpa + (64.347-63.041)

WL_02[which(WL_02$DateTime < as.POSIXct("2022-10-12 13:45:00", tz="UTC")),]$WLPres_kpa <- 
  WL_02[which(WL_02$DateTime < as.POSIXct("2022-10-12 13:45:00", tz="UTC")),]$WLPres_kpa - (62.981-62.541)
#WL_02 <- WL_02%>%filter(WLPres_kpa != 62.566)


```

##Unresolved issues

Something is up with the data post field season 2022 >:(
I guess we should look at discharge collected in these location to try to figure this shit out


```{r plot, echo=FALSE}

ggplot(WL_02, aes(x=DateTime, y=WLPres_kpa)) + geom_point()
```

## barometric data
now read in the barometric data

```{r baro loop, echo=FALSE}

###merge data with baro data###
setwd(here::here("Baro"))
all_files=list.files(pattern=".csv") #pulls out the csv files from WL folder in HOBOware folder
sites_rp=gsub("_.*","",all_files) #selects the correct pattern so as to seelct only desired files
site_names=unique(sites_rp) #creates list of site names for following loop

#rm old files, if they exsist
rm(BaroData)
rm(Temp_BaroData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("BaroData")){
      BaroData <- read.csv(file, skip=10, header = TRUE, sep = ",",
                           quote = "\"",dec = ".", fill = TRUE, comment.char = "")
    }
    if (exists("BaroData")){
      Temp_BaroData <- read.csv(file, skip=10, header = TRUE, sep = ",",
                                quote = "\"",dec = ".", fill = TRUE, comment.char = "")  
      BaroData <- rbind(BaroData, Temp_BaroData)
      rm(Temp_BaroData)
    }
    
  }
  colnames(BaroData)=c("Date","Time","ms","AirPres_kpa","AirTemp_c")
  BaroData=unique(BaroData)
  BaroData$DateTime <- paste(BaroData$Date, BaroData$Time)
  BaroData$DateTime <- as.POSIXct(BaroData$DateTime, format="%m/%d/%Y %I:%M:%S %p", tz="UTC")
  BaroData$DateTime <- round_date(BaroData$DateTime, "15 mins")
  BaroData$ms <- NULL
  BaroData$Date <- NULL
  BaroData$Time <- NULL
  BaroData <- BaroData[,c(3,1,2)]
  BaroData=unique(BaroData)
  assign((paste(site,sep="_")),BaroData) #creates object with new appended data
  rm(BaroData) #removes WLdata so that multiple sites aren't appended together
}
```

### clean baro
```{r clean baro, echo=FALSE}

##clean BaroData
#plot_ly(Baro%>%filter(DateTime > as.POSIXct("2021-06-11 00:00:00", tz = "UTC")), x = ~DateTime, y = ~AirPres_kpa, type = 'scatter', mode = 'markers') 

Baro <- Baro%>%filter(DateTime > as.POSIXct("2021-06-01 00:00:00", tz = "UTC"))

Baro <- Baro%>%filter(DateTime < as.POSIXct("2021-07-27 15:00:00", tz = "UTC")|
                          DateTime > as.POSIXct("2021-07-28 13:30:00", tz = "UTC"))

ggplot(Baro,aes(x=DateTime,y=AirPres_kpa))+ geom_point()

```

### correct for barometric pressure
```{r baro correct, echo=FALSE}

#correct for baro 

WL_02 <- left_join(Baro,WL_02,by="DateTime")

WL_02$Corrected_kpa <- WL_02$WLPres_kpa - WL_02$AirPres_kpa

#calculate total pressure to correct viasala readings
WL_02$Total_kpa <- 
  WL_02$WLPres_kpa

#convert kpa to meters of water
# constant, 1 kpa = 0.101972 m water
WL_02$WL_m <- WL_02$Corrected_kpa * 0.101972
WL_02$Corrected_kpa <- NULL

```
#plot data
```{r plot final, echo=FALSE}

##Now we can graph 
    ## will need to change the right limit accordingly

ggplot(data = WL_02 %>% filter(DateTime > "2021-06-10"), 
       aes(DateTime, WL_m)) +
  geom_point(color = "steelblue") +
  labs(title = "Station 02 Water level",
    y = "water level [m]", x = "") 

```


#Time for discharge!
this will take awhile so buckle up, baby

```{r Find WL data for rating curve, echo=FALSE}

#enter date of collection
date <- "2022-07-27"
#enter start and end time that wetland was sampled
time <- "09:45:00"


WL_m <- WL_02%>%filter(DateTime == as.POSIXct(paste(date, time), format="%Y-%m-%d %H:%M:%S", tz = "UTC"))

print(WL_m)

```

#dischage rating curve
see excel file for station 01
field season 2022 looks compatible with field season 2021

y = 1.4892x2 - 0.1365x + 0.0059
R² = 0.9711


```{r discharge, echo=FALSE}

WL_02$Q_m3s <- 1.4892*(WL_02$WL_m)^2 - 0.1365*WL_02$WL_m + 0.0059

```

#plot discharge
```{r plot final, echo=FALSE}

##Now we can graph 
    ## will need to change the right limit accordingly

ggplot(data = WL_02 %>% filter(DateTime > "2021-06-10"), 
       aes(DateTime, Q_m3s)) +
  geom_point(color = "steelblue") +
  labs(title = "Station 02 Discharge",
    y = "Q [m3 s-1]", x = "") 

ggplot(data = WL_02 %>% filter(DateTime > "2021-06-10"), 
       aes(DateTime, WL_m)) +
  geom_point(color = "steelblue") +
  labs(title = "Station 02 WATER LEVEL",
    y = "water level [m]", x = "") 

```


#CO2 time

```{r pressure, echo=FALSE}

setwd(here::here("CO2"))
all_files=list.files(pattern=".csv") #pulls out the csv files from WL folder in HOBOware folder
#sites_rp=gsub("_.*","",all_files) #selects the correct pattern so as to seelct only desired files
sites_rp = sub('_[^_]+$', '', all_files)
site_names=unique(sites_rp) #creates list of site names for following loop

site_names="CO2_02"


#rm old files, if they exist
rm(CO2Data)
rm(Temp_CO2Data)

for (site in site_names){
 # if(site == "CO2_02"){

  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("CO2Data")){
      CO2Data <- read.csv(file, skip=6, header = TRUE)
      CO2Data=CO2Data[,1:3]
        if(names(CO2Data)[1] == "Date"){
          colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time),  format="%m/%d/%Y %I:%M:%S %p", tz = "UTC")
      } else { 
        colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%d/%m/%Y %H:%M:%S", tz = "UTC")
      }
      
      CO2Data$Station <- site
    }
    if (exists("CO2Data")) {
      Temp_CO2Data <- read.csv(file, skip=6, header = TRUE)  
      Temp_CO2Data=Temp_CO2Data[,1:3]
      if(colnames(Temp_CO2Data)[1]=="Date"){
        colnames(Temp_CO2Data) <- c("Date","Time","ppm")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Date, Temp_CO2Data$Time), format="%m/%d/%Y %I:%M:%S %p", tz = "UTC")
        Temp_CO2Data$Station <- site
      } else {
#        Temp_CO2Data$Fecha <- as.Date(Temp_CO2Data$Fecha, format = "%d / %m / %Y")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Fecha, Temp_CO2Data$Tiempo), format="%d/%m/%Y %H:%M:%S", tz = "UTC")
        colnames(Temp_CO2Data) <- c("Date","Time","ppm","DateTime")
        Temp_CO2Data$Station <- site
      }
      CO2Data <- rbind(CO2Data, Temp_CO2Data)
      rm(Temp_CO2Data)
    }
    
  }
  
#   CO2Data$DateTime <- round_date(CO2Data$DateTime, "15 mins")

  CO2Data=unique(CO2Data)
  CO2Data$Date <- NULL
  CO2Data$Time <- NULL
  CO2Data <- CO2Data[,c(3,2,1)]
  assign((paste(site,sep="_")),CO2Data) #creates object with new appended data
  rm(CO2Data) #removes CO2 data so that multiple sites aren't appended together
}

CO2_02$Station <- "Stn02"

```


#check data 

```{r check CO2 data plot, echo=FALSE}


##check data
plot_ly(CO2_02, x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 

#plot_ly(CO2_01%>%
#  filter(DateTime < as.POSIXct("2021-07-30 07:27:00", tz = "UTC")), x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 

```

```{r clean, echo=FALSE}
CO2_02  <- CO2_02 %>% 
  filter(DateTime < as.POSIXct("2021-06-11 03:34:00", tz = "UTC") | DateTime > as.POSIXct("2021-06-16 11:52:00", tz = "UTC")) %>%
    filter(DateTime < as.POSIXct("2021-06-29 14:40:00", tz = "UTC") | DateTime > as.POSIXct("2021-06-29 15:00:00", tz = "UTC")) %>%
  filter(DateTime < as.POSIXct("2021-06-30 10:42:00", tz = "UTC") | DateTime > as.POSIXct("2021-06-30 11:45:00", tz = "UTC")) %>%
#  filter(DateTime < as.POSIXct("2021-07-14 11:06:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-14 11:11:00", tz = "UTC")) %>% 
#  filter(DateTime < as.POSIXct("2021-07-14 13:18:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-14 14:13:00", tz = "UTC")) %>%
  filter(DateTime < as.POSIXct("2021-07-16 11:56:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-16 11:57:00", tz = "UTC")) %>%
  filter(DateTime != as.POSIXct("2021-07-16 12:00:05", tz = "UTC")) %>% 
  filter(DateTime != as.POSIXct("2021-07-19 10:30:05", tz = "UTC"))  %>%
  filter(DateTime != as.POSIXct("2021-06-25 10:04:00", tz = "UTC"))  %>%
#injection July 13
  filter(DateTime < as.POSIXct("2021-07-13 10:15:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-13 15:15:00", tz = "UTC"))%>%
#injection July 14
  filter(DateTime < as.POSIXct("2021-07-14 09:00:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-14 15:30:00", tz = "UTC"))%>%
#bad data
  filter(DateTime < as.POSIXct("2022-06-20 00:00:00", tz = "UTC"))

CO2_02 <- CO2_02
CO2_02$DateTime <- round_date(CO2_02$DateTime,unit="15 minutes")
CO2_02 <- CO2_02 %>% 
  group_by(DateTime) %>% 
  summarise(ppm = mean(ppm))

```

```{r plot, echo=FALSE}


ggplot(data = CO2_02, aes(DateTime, ppm)) +
  geom_point(color = "steelblue") +
  labs(#title = "CO2  stations",
       y = "CO2 ppm", x = "") 

```

##Create Station Dataframes
we two different models of vaisala

```{r stations df, echo=FALSE}

Stn02 <- full_join(WL_02,CO2_02, by=c("DateTime","Station"))

#convert baro to hpa
#1 kPa = 10 hPa
#1 kPa = 0.101972 m
Stn02$Total_hPa <- Stn02$Total_kpa * 10

```

#correction vaisala data
make adjustments to ppm using water level data

```{r corect viaslal, echo=FALSE}
#new

#The new viasalas are set to 700hPa and have an internal temperature, so do not ned to be corrected for temp
#the units for new vasialas are half of what they should be! 

#Station 2, 3 and Well 1 and 2 are new V

#df_new$adjusted_ppm <- df_new$ppm * (1 + (700 - df_new$Total_hPa) * 0.0015) * (1 - (6.7 - df_new$WLTemp_c) * 0.003)
Stn02$adjusted_ppm <- (Stn02$ppm * 2 )* (1 + (700 - Stn02$Total_hPa) * 0.0015) 

```

#plot

```{r plot, echo=FALSE}


co2 <- ggplot(data = Stn02, aes(DateTime, adjusted_ppm)) +
  geom_point(color = "steelblue") +
  labs(#title = "CO2  stations",
       y = "CO2 ppm", x = "") 
  
Q <- ggplot(data = Stn02, aes(DateTime, Q_m3s)) +
  geom_point(color = "steelblue") +
  labs(#title = "Q  stations",
       y = "Q", x = "") 



grid.arrange(co2, Q, ncol=1)

all.figs <- ggarrange(NULL,co2, NULL,Q, ncol = 1,
               heights = c(0.2,1,0.2,1),
               labels = c("A","","B",""),
               font.label = list(size = 24, color = "black", face = "bold"),
              # label.x = .1,
              # label.y = .1,
               align="h", common.legend = FALSE
               )

```

#dissolved o2


```{r loop DO data, echo = FALSE}

setwd(here::here("DO"))
all_files=list.files(pattern=".csv") #pulls out the csv files from CO2 folder
sites_rp = sub('_[^_]+$', '', all_files)
site_names=unique(sites_rp) #creates list of site names for following loop

site_names = "DO_02"

#rm old files, if they exist
rm(DOData)
rm(Temp_DOData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("DOData")){
      DOData <- read.csv(file, skip=1, header = TRUE, sep = ",",
                         quote = "\"",dec = ".", fill = TRUE, comment.char = "")
      
  
        colnames(DOData)=c("row","DateTime","DO_mgL","DOTemp_c")
        DOData <- DOData[2:4]
        DOData$DO_mgL <- as.numeric(as.character(DOData$DO_mgL), digits=6)
        DOData$DOTemp_c <- as.numeric(as.character(DOData$DOTemp_c), digits=5)
      

    DOData$DateTime <- as.POSIXct(DOData$DateTime, tz="UTC",
           tryFormats = c("%m/%d/%y %I:%M:%S %p",
                          "%m/%d/%Y %H:%M"))
    }
    if (exists("DOData")){
      Temp_DOData <- read.csv(file, skip=1, header = TRUE, sep = ",",
                              quote = "\"",dec = ".", fill = TRUE, comment.char = "")  

        colnames(Temp_DOData)=c("row","DateTime","DO_mgL","DOTemp_c")
        Temp_DOData <- Temp_DOData[2:4]
        Temp_DOData$DO_mgL <- as.numeric(as.character(Temp_DOData$DO_mgL), digits=6)
        Temp_DOData$DOTemp_c <- as.numeric(as.character(Temp_DOData$DOTemp_c), digits=5)
        }
      

          Temp_DOData$DateTime <- as.POSIXct(Temp_DOData$DateTime, tz="UTC",
           tryFormats = c("%m/%d/%y %I:%M:%S %p",
                          "%m/%d/%Y %H:%M"))
      
      
      DOData <- rbind(DOData, Temp_DOData)
      rm(Temp_DOData)
#    }
    
  }
  DOData$DateTime <- round_date(DOData$DateTime, "15 mins")
  DOData$Station <- site
  DOData=unique(DOData)
  assign((paste(site,sep="_")),DOData) #creates object with new appended data
  rm(DOData) #removes DOdata so that multiple sites aren't appended together
}

DO_02$Station <- "Stn02"

```

#check do data

```{r check DO data plot, echo=FALSE}


##check data
plot_ly(DO_02, x = ~DateTime, y = ~DO_mgL, type = 'scatter', mode = 'markers') 

#clean 
DO_02 <- DO_02%>%filter(DO_mgL > -100)
```


```{r loop Lux data, echo=FALSE}
##set folder for site ##

setwd(here::here("Lux"))

all_files=list.files(pattern=".csv") #pulls out the csv files from WL folder in HOBOware folder
#sites_rp=gsub("_.*","",all_files) #selects the correct pattern so as to seelct only desired files
sites_rp = sub('_[^_]+$', '', all_files)
site_names=unique(sites_rp) #creates list of site names for following loop

site_names = c("LUXabajo_02","LUXarriba_02")

#rm old files, if they exist
rm(LuxData)
rm(Temp_LuxData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("LuxData")){
      LuxData <- read.csv(file, skip=2, header = FALSE, sep = ",",
                         quote = "\"",dec = ".", fill = TRUE, comment.char = "")
      LuxData=LuxData[,2:4]
      colnames(LuxData)=c("DateTime","Temp_C","Lux")  
      
    }
    if (exists("LuxData")){
      Temp_LuxData <- read.csv(file, skip=2, header = FALSE, sep = ",",
                              quote = "\"",dec = ".", fill = TRUE, comment.char = "")  
      #if (!"Temp_C" %in% colnames(Temp_LuxData)){Temp_LuxData$Temp_C <- NA}
      Temp_LuxData=Temp_LuxData[,2:4]
      colnames(Temp_LuxData)=c("DateTime","Temp_C","Lux")  
      
      
      LuxData <- rbind(LuxData, Temp_LuxData)
      rm(Temp_LuxData)
    }
    
    
  }
  #colnames(LuxData)=c("row","DateTime","Temp_C","Lux")
  #LuxData=LuxData[,2:4]
  LuxData=unique(LuxData)
  LuxData$DateTime <- as.POSIXct(LuxData$DateTime, format="%m/%d/%y %I:%M:%S %p", tz="UTC")
  assign((paste(site,"Lux_data",sep="_")),LuxData) #creates object with new appended data
  rm(LuxData) #removes WLdata so that multiple sites aren't appended together
}

LUXabajo_02_Lux_data$Station <- "Stn02"
LUXarriba_02_Lux_data$Station <- "Stn02"


```

#plot lux

```{r check LUX data plot, echo=FALSE}


##check data
plot_ly(LUXabajo_02_Lux_data, x = ~DateTime, y = ~Lux, type = 'scatter', mode = 'lines') 


plot_ly(LUXarriba_02_Lux_data, x = ~DateTime, y = ~Lux, type = 'scatter', mode = 'lines')

#bind lux data
colnames(LUXabajo_02_Lux_data) <- c("DateTime","LUXabajoTemp_c","LUXabajo","Station")
colnames(LUXarriba_02_Lux_data) <- c("DateTime","LUXarribaTemp_c","LUXarriba","Station")

Lux_02 <- full_join(LUXarriba_02_Lux_data, LUXabajo_02_Lux_data, by=c("DateTime","Station"))


```

#now we merge everything together!!

```{r merge dataframe, echo=FALSE}
Stn02_df <- full_join(WL_02, CO2_02, by=c("DateTime","Station"))
Stn02_df <- full_join(Stn02_df, DO_02, by=c("DateTime","Station"))
Stn02_df <- full_join(Stn02_df, Lux_02, by=c("DateTime","Station"))

```

```{r write out data, echo=FALSE}
write.csv(Stn02_df,here::here("LongTermData/Stn02_df_2022-10-16.csv"))

```