---
title: 'Long Term Data: Station01'
author: "Kriddie"
date: "2022-11-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

long term data for station 1

```{r library}
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyverse)
library(plotly)
library(here)
library(dplyr)
library(reshape2)
library(purrr)
library(sjmisc)
```

#water level

```{r Solinst, echo=FALSE}

setwd(here::here("WaterLevel"))
all_files=list.files(pattern=".csv") #pulls out the csv files from CO2 folder
sites_rp = sub('_[^_]+$', '', all_files)
site_names=unique(sites_rp) #creates list of site names for following loop

site_names = "WL_01"

#rm old files, if they exist
rm(WLData)
rm(Temp_WLData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("WLData")){
      Trash_WLData <- read.csv(file, skip=0, header = TRUE, sep = ",",
                         quote = "\"",dec = ".", fill = TRUE, comment.char = "")
      
      if(str_contains(Trash_WLData[6,1],"m")){
        print("m")
        WLData <- read.csv(file, skip=11, header = TRUE, sep = ",",
                    quote = "\"",dec = ".", fill = TRUE, comment.char = "")
        colnames(WLData)=c("Date","Time","ms","WLPres_kpa","WLTemp_c")
        WLData$WLPres_kpa <- as.numeric(as.character(WLData$WLPres_kpa), digits=6)
        WLData$WLTemp_c <- as.numeric(as.character(WLData$WLTemp_c), digits=5)
        WLData$WLPres_kpa <- WLData$WLPres_kpa*9.8064
#        WLData$WLTemp_c <- (WLData$WLTemp_c - 32)/1.8000
        } else { 
        print("kPa")
        WLData <- read.csv(file, skip=11, header = TRUE, sep = ",",
            quote = "\"",dec = ".", fill = TRUE, comment.char = "")
        colnames(WLData)=c("Date","Time","ms","WLPres_kpa","WLTemp_c")
        WLData$WLPres_kpa <- as.numeric(as.character(WLData$WLPres_kpa), digits=6)
        WLData$WLTemp_c <- as.numeric(as.character(WLData$WLTemp_c), digits=5)
      }
    }
    if (exists("WLData")){
      Trash_WLData <- read.csv(file, skip=0, header = FALSE, sep = ",",
                              quote = "\"",dec = ".", fill = TRUE, comment.char = "")  
      if(str_contains(Trash_WLData[6,1],"m")){
        print("m")
        Temp_WLData <- read.csv(file, skip=11, header = TRUE, sep = ",",
                           quote = "\"",dec = ".", fill = TRUE, comment.char = "")
        Temp_WLData <- Temp_WLData[c(-1),]
        colnames(Temp_WLData)=c("Date","Time","ms","WLPres_kpa","WLTemp_c")
        Temp_WLData$WLPres_kpa <- as.numeric(as.character(Temp_WLData$WLPres_kpa), digits=6)
        Temp_WLData$WLTemp_c <- as.numeric(as.character(Temp_WLData$WLTemp_c), digits=5)
        Temp_WLData$WLPres_kpa <- Temp_WLData$WLPres_kpa*9.8064
#        Temp_WLData$WLTemp_c <- (Temp_WLData$WLTemp_c - 32)/1.8000
        } else { 
        print("kpa")
        Temp_WLData <- read.csv(file, skip=11, header = TRUE, sep = ",",
                                quote = "\"",dec = ".", fill = TRUE, comment.char = "")
        Temp_WLData <- Temp_WLData[c(-1),]
        colnames(Temp_WLData)=c("Date","Time","ms","WLPres_kpa","WLTemp_c")
        Temp_WLData$WLPres_kpa <- as.numeric(as.character(Temp_WLData$WLPres_kpa), digits=6)
        Temp_WLData$WLTemp_c <- as.numeric(as.character(Temp_WLData$WLTemp_c), digits=5)
      }
      
      WLData <- rbind(WLData, Temp_WLData)
      rm(Temp_WLData)
    }
    
  }
  WLData=unique(WLData)
  WLData$DateTime <- paste(WLData$Date, WLData$Time)
  WLData$DateTime <- as.POSIXct(WLData$DateTime, format="%m/%d/%Y %I:%M:%S %p", tz="UTC")
  WLData$DateTime <- round_date(WLData$DateTime, "5 mins")
  WLData <- WLData[,c("DateTime","WLPres_kpa","WLTemp_c")]
  WLData$Station <- "Stn01"
  assign((paste(site,sep="_")),WLData) #creates object with new appended data
  rm(WLData) #removes WLdata so that multiple sites aren't appended together
}

rm(Trash_WLData)

```
##read in wl02
we also need to read in wl02 data because we will use it to fill in a gap in station 01 data
```{r Hobo WL}
#First the Hobos

setwd(here::here("WaterLevel"))
all_files=list.files(pattern=".csv") #pulls out the csv files from CO2 folder
sites_rp = sub('_[^_]+$', '', all_files)
site_names=unique(sites_rp) #creates list of site names for following loop

site_names = "WL_02"
#site_names = site_names[c(2,3,5,6)]

#rm old files, if they exist
rm(WLData)
rm(Temp_WLData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("WLData")){
      WLData <- read.csv(file, skip=1, header = FALSE, sep = ",",
                         quote = "\"",dec = ".", fill = TRUE, comment.char = "")
      
      if(str_contains(WLData[1,3],"Abs Pres, psi")){
        WLData <- WLData[-1,]
        colnames(WLData)=c("row","DateTime","WLPres_kpa","WLTemp_c")
        WLData <- WLData[2:4]
        WLData$WLPres_kpa <- as.numeric(as.character(WLData$WLPres_kpa), digits=6)
        WLData$WLTemp_c <- as.numeric(as.character(WLData$WLTemp_c), digits=5)
        WLData$WLPres_kpa <- WLData$WLPres_kpa*6.89476
        WLData$WLTemp_c <- (WLData$WLTemp_c - 32)/1.8000

      } else { 
        WLData <- WLData[-1,]
        colnames(WLData)=c("row","DateTime","WLPres_kpa","WLTemp_c")
        WLData <- WLData[2:4]
        WLData$WLPres_kpa <- as.numeric(as.character(WLData$WLPres_kpa), digits=6)
        WLData$WLTemp_c <- as.numeric(as.character(WLData$WLTemp_c), digits=5)
        }
      
#      WLData$DateTime <- as.POSIXct(WLData$DateTime, format="%m/%d/%y %I:%M:%S %p", tz="UTC")
    WLData$DateTime <- as.POSIXct(WLData$DateTime, tz="UTC",
           tryFormats = c("%m/%d/%y %I:%M:%S %p",
                          "%m/%d/%Y %H:%M"))
    }
    if (exists("WLData")){
      Temp_WLData <- read.csv(file, skip=1, header = FALSE, sep = ",",
                              quote = "\"",dec = ".", fill = TRUE, comment.char = "")  
#      
      
      if(str_contains(Temp_WLData[1,3],"Abs Pres, psi")){
        Temp_WLData <- Temp_WLData[-1,]
        colnames(Temp_WLData)=c("row","DateTime","WLPres_kpa","WLTemp_c")
        Temp_WLData <- Temp_WLData[2:4]
        Temp_WLData$WLPres_kpa <- as.numeric(as.character(Temp_WLData$WLPres_kpa), digits=6)
        Temp_WLData$WLTemp_c <- as.numeric(as.character(Temp_WLData$WLTemp_c), digits=5)
        Temp_WLData$WLPres_kpa <- Temp_WLData$WLPres_kpa*6.89476
        Temp_WLData$WLTemp_c <- (Temp_WLData$WLTemp_c - 32)/1.8000
        
        
      } else { 
        Temp_WLData <- Temp_WLData[-1,]
        colnames(Temp_WLData)=c("row","DateTime","WLPres_kpa","WLTemp_c")
        Temp_WLData <- Temp_WLData[2:4]
        Temp_WLData$WLPres_kpa <- as.numeric(as.character(Temp_WLData$WLPres_kpa), digits=6)
        Temp_WLData$WLTemp_c <- as.numeric(as.character(Temp_WLData$WLTemp_c), digits=5)
        }
      
#      Temp_WLData$DateTime <- as.POSIXct(Temp_WLData$DateTime, format="%m/%d/%y %I:%M:%S %p", tz="UTC")
          Temp_WLData$DateTime <- as.POSIXct(Temp_WLData$DateTime, tz="UTC",
           tryFormats = c("%m/%d/%y %I:%M:%S %p",
                          "%m/%d/%Y %H:%M"))
      
      
      WLData <- rbind(WLData, Temp_WLData)
      rm(Temp_WLData)
    }
    
  }
  WLData$DateTime <- round_date(WLData$DateTime, "15 mins")
  WLData$Station <- site
  WLData=unique(WLData)
  assign((paste(site,sep="_")),WLData) #creates object with new appended data
  rm(WLData) #removes WLdata so that multiple sites aren't appended together
}

WL_02 <- WL_02%>%filter(WLPres_kpa != 62.566)
```
## plot 
plot the water level so that each station data can be cleaned

```{r plot, echo=FALSE}

##clean data

plot_ly(WL_01, x = ~DateTime, y = ~WLPres_kpa, type = 'scatter', mode = 'markers') 

```




```{r clean, echo=FALSE}

WL_01$DateTime <- round_date(WL_01$DateTime,unit="15 minutes")

WL_01 <- WL_01%>%filter(WLPres_kpa > 63 & WLPres_kpa < 70)
#looks like WL changed in febuary
#Actually no - wierd
#WL_01$WLPres_kpa[which(WL_01$DateTime < as.POSIXct("2022-02-12 13:00", tz="UTC"))] <- WL_01$WLPres_kpa[which(WL_01$DateTime < as.POSIXct("2022-02-12 13:00", tz="UTC"))] - (64.3919-63.8785)
WL_01 <- WL_01%>%filter(DateTime != as.POSIXct("2022-06-07 10:45", tz="UTC"))%>%filter(DateTime != as.POSIXct("2022-06-07 11:00", tz="UTC"))
```

##Unresolved issues
there i a discontinuity on February 12 2022. My best guess is that a damn built up, raising water level, and then broke through dropping it down again

 I'm not sure what I should doooo
 
### Use WL_02 to predict WL_01
we are missing some data from WL_01. I'm hoping there is a strong enough relationship between WL_01 and WL_02 to fill in missing data

July 13th 10:15 to July 28 14:15


```{r fill in wl_01, echo=FALSE}
WL_01_02 <- full_join(WL_01,WL_02, by= "DateTime")
WL_01_02 <- WL_01_02[,c("DateTime","WLPres_kpa.x","WLPres_kpa.y")]
colnames(WL_01_02) <- c("DateTime","WL_01","WL_02")
WL_01_02 <- WL_01_02%>%filter(DateTime > as.POSIXct("2021-07-01 10:15:00", tz = "UTC")& DateTime < as.POSIXct("2021-07-13 14:15:00", tz = "UTC"))

mdl1_1 <- lm(WL_01_02$WL_01 ~ WL_01_02$WL_02)
mdl2_1 <- lm(WL_01_02$WL_01 ~ WL_01_02$WL_02 + I(WL_01_02$WL_02^2))
mdl3_1 <- lm(WL_01_02$WL_01 ~ WL_01_02$WL_02 + I(WL_01_02$WL_02^2) + I(WL_01_02$WL_02^3))
mdl4_1 <- lm(WL_01_02$WL_01 ~ I(WL_01_02$WL_02^2))

set.seed(20)
q <- seq(from=0, to=66, by=0.5)
y_mdl1 <- mdl1_1$coefficients[1] + mdl1_1$coefficients[2]*q
y_mdl2 <- mdl2_1$coefficients[1] + mdl2_1$coefficients[2]*q + mdl2_1$coefficients[3]*q^2
y_mdl3 <- mdl3_1$coefficients[1] + mdl3_1$coefficients[2]*q + mdl3_1$coefficients[3]*q^2 + mdl3_1$coefficients[4]*q^3
y_mdl4 <- mdl4_1$coefficients[1] + mdl4_1$coefficients[2]*q^2


plot(WL_01 ~ WL_02, data = WL_01_02 )
#lines(q,y_mdl1,col='firebrick1',lwd=1)
lines(q,y_mdl2,col='blue',lwd=1)
#lines(q,y_mdl3,col='yellow',lwd=1)
#lines(q,y_mdl4,col='green',lwd=1)
mtext("y=  - 72380  + 3420 *x - 53.81 *x^2 + 0.2823*x^3", side=3)

rm(mdl1_1,mdl2_1,mdl3_1,mdl4_1)
rm(WL_01_02)
```



```{r wl_01 gap, echo=FALSE}
WL_01_fill <- WL_02
WL_01_fill$WLPres_kpa <-   1351.0808 - 40.9546  *WL_01_fill$WLPres_kpa + 0.3257 *(WL_01_fill$WLPres_kpa)^2 
WL_01_fill <- WL_01_fill%>%filter(DateTime > as.POSIXct("2021-07-14 10:15:00", tz = "UTC")&
                          DateTime < as.POSIXct("2021-07-27 14:15:00", tz = "UTC"))
WL_01_fill$Station <- "WL_01"

WL_01 <- rbind(WL_01,WL_01_fill)
rm(WL_01_fill,WL_02)

ggplot(WL_01, aes(x=DateTime, y=WLPres_kpa)) + geom_point()
```

## barometric data
now read in the barometric data

```{r baro loop, echo=FALSE}

###merge data with baro data###
setwd(here::here("Baro"))
all_files=list.files(pattern=".csv") #pulls out the csv files from WL folder in HOBOware folder
sites_rp=gsub("_.*","",all_files) #selects the correct pattern so as to seelct only desired files
site_names=unique(sites_rp) #creates list of site names for following loop

#rm old files, if they exsist
rm(BaroData)
rm(Temp_BaroData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("BaroData")){
      BaroData <- read.csv(file, skip=10, header = TRUE, sep = ",",
                           quote = "\"",dec = ".", fill = TRUE, comment.char = "")
    }
    if (exists("BaroData")){
      Temp_BaroData <- read.csv(file, skip=10, header = TRUE, sep = ",",
                                quote = "\"",dec = ".", fill = TRUE, comment.char = "")  
      BaroData <- rbind(BaroData, Temp_BaroData)
      rm(Temp_BaroData)
    }
    
  }
  colnames(BaroData)=c("Date","Time","ms","AirPres_kpa","AirTemp_c")
  BaroData=unique(BaroData)
  BaroData$DateTime <- paste(BaroData$Date, BaroData$Time)
  BaroData$DateTime <- as.POSIXct(BaroData$DateTime, format="%m/%d/%Y %I:%M:%S %p", tz="UTC")
  BaroData$DateTime <- round_date(BaroData$DateTime, "15 mins")
  BaroData$ms <- NULL
  BaroData$Date <- NULL
  BaroData$Time <- NULL
  BaroData <- BaroData[,c(3,1,2)]
  BaroData=unique(BaroData)
  assign((paste(site,sep="_")),BaroData) #creates object with new appended data
  rm(BaroData) #removes WLdata so that multiple sites aren't appended together
}
```

### clean baro
```{r clean baro, echo=FALSE}

##clean BaroData
#plot_ly(Baro%>%filter(DateTime > as.POSIXct("2021-06-11 00:00:00", tz = "UTC")), x = ~DateTime, y = ~AirPres_kpa, type = 'scatter', mode = 'markers') 

Baro <- Baro%>%filter(DateTime > as.POSIXct("2021-06-01 00:00:00", tz = "UTC"))

Baro <- Baro%>%filter(DateTime < as.POSIXct("2021-07-27 15:00:00", tz = "UTC")|
                          DateTime > as.POSIXct("2021-07-28 13:30:00", tz = "UTC"))

ggplot(Baro,aes(x=DateTime,y=AirPres_kpa))+ geom_point()

```

### correct for barometric pressure
```{r baro correct, echo=FALSE}

#correct for baro 

WL_01 <- left_join(Baro,WL_01,by="DateTime")

WL_01$Corrected_kpa <- WL_01$WLPres_kpa - WL_01$AirPres_kpa

#calculate total pressure to correct viasala readings
WL_01$Total_kpa <- 
  WL_01$WLPres_kpa

#convert kpa to meters of water
# constant, 1 kpa = 0.101972 m water
WL_01$WL_m <- WL_01$Corrected_kpa * 0.101972
WL_01$Corrected_kpa <- NULL

```
#plot data
```{r plot final, echo=FALSE}

##Now we can graph 
    ## will need to change the right limit accordingly

ggplot(data = WL_01 %>% filter(DateTime > "2021-06-10"), 
       aes(DateTime, WL_m)) +
  geom_point(color = "steelblue") +
  labs(title = "Station 01 Water level",
    y = "water level [m]", x = "") 

```

#Time for discharge!
this will take awhile so buckle up, baby

```{r Find WL data for rating curve, echo=FALSE}

#enter date of collection
date <- "2022-07-27"
#enter start and end time that wetland was sampled
time <- "09:15:00"


WL_m <- WL_01%>%filter(DateTime == as.POSIXct(paste(date, time), format="%Y-%m-%d %H:%M:%S", tz = "UTC"))

print(WL_m)

```

#dischage rating curve
see excel file for station 01
field season 2022 looks compatible with field season 2021

This is before adding dummy data to improve x axis intercet
y = -0.0647x2 + 0.4162x - 0.0554
R² = 0.9567

This is after dummey data
y = .1789x2 + 0.2095x - 0.0246
R² = 0.9478

This is breaking up low and high flows
>low 
y = 2.0906x2 - 0.5608x + 0.0439
R² = 0.8983

>high with dummy values
y = 0.126*x2 + 0.255x - 0.0314
R² = 0.9473

intersect: 0.3019385

```{r discharge, echo=FALSE}
intercept <- 0.276817

#low
WL_01[which(WL_01$WL_m < intercept),]$Q_m3s <- 2.0906*(WL_01[which(WL_01$WL_m < intercept),]$WL_m)^2 - 0.5608*WL_01[which(WL_01$WL_m < intercept),]$WL_m + 0.0439
#high
WL_01[which(WL_01$WL_m > intercept),]$Q_m3s <- 0.126*(WL_01[which(WL_01$WL_m > intercept),]$WL_m)^2 + 0.255*WL_01[which(WL_01$WL_m > intercept),]$WL_m - 0.0314

#WL_01$Q_m3s <- 0.126*(WL_01$WL_m)^2 + 0.255*WL_01$WL_m - 0.0314
```

#plot discharge
```{r plot final, echo=FALSE}

##Now we can graph 
    ## will need to change the right limit accordingly

ggplot(data = WL_01 %>% filter(DateTime > "2021-06-10"), 
       aes(DateTime, Q_m3s)) +
  geom_point(color = "steelblue") +
  labs(title = "Station 01 Discharge",
    y = "Q [m3 s-1]", x = "") 

ggplot(data = WL_01 %>% filter(DateTime > "2021-06-10"), 
       aes(DateTime, WL_m)) +
  geom_point(color = "steelblue") +
  labs(title = "Station 01 Water level",
    y = "water level [m]", x = "") 

```