---
title: "synop_fig1_2022-03-21"
author: "Kriddie"
date: "3/21/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(dplyr) # for `rename`
library(tidyr) # for `gather`
library(ggplot2)
library(cowplot)
library(tidyverse)
#library(rstatix)
library(ggpubr)
library(plotly)
#library(rstatix)
```

## synop_fig1_2022-03-21
This file is meant to keep better track of my progress towards figure 1 for my synop paper
The goal of this figure is to show how much CO2 is coming off these rivers on a grams of carbon per sec bases

or something like that


We start with the most recently processes synoptic data. It includes calculates k600 values.


```{r read in}
#read in the most recent synoptic data

#df <- read.csv(here::here("ProcessedData/ALL_synoptic_2022-03-21.csv"))
#df <- read.csv(here::here("ProcessedData/ALL_synoptic_2022-03-24.csv"))
df <- read.csv(here::here("ProcessedData/ALL_synoptic_2022-04-19.csv"))
df$X <- NULL
df <- unique(df)
df$EOS_no[df$EOS_no == "EOS1"] <- "EOS_1"
df$EOS_no[df$EOS_no == "EOS2"] <- "EOS_2"
df$Date <- format(as.POSIXct(df$Date,format='%Y-%m-%d'))

df$Flux_ave <- signif(df$Flux_ave, digits = 3)
##add raster data
#Synop_all_raster3 <- read.csv(here::here("Synoptic/Synop_all_raster3.csv"))
Synop_all_raster3 <- read.csv(here::here("Synoptic/SynopFlowAccu_20220419.csv"))


Synop_all_raster3 <- Synop_all_raster3[,c("Wetland","Date","EOS_no","Flux_ave","Wetland_1","Elevation","lon","lat","FlowAccu","Flowlen","Slope")]
colnames(Synop_all_raster3) <- c("Wetland_tribs","Date","EOS_no","Flux_ave","Wetland","Elevation_raster","lon_raster","lat_raster","FlowAccu","Flowlen","Slope_raster")
Synop_all_raster3$Date <- format(as.POSIXct(Synop_all_raster3$Date,format='%m/%d/%Y %H:%M:%S'),format='%Y-%m-%d')
Synop_all_raster3$EOS_no[Synop_all_raster3$EOS_no == "EOS1"] <- "EOS_1"
Synop_all_raster3$EOS_no[Synop_all_raster3$EOS_no == "EOS2"] <- "EOS_2"
Synop_all_raster3$Flux_ave <- signif(Synop_all_raster3$Flux_ave, digits = 3)


df_2 <- full_join(df,Synop_all_raster3, by =  c("Date","EOS_no","Flux_ave","Wetland"))
check <- df_2[,c("Date","EOS_no","Flux_ave","FlowAccu","Totalflux_umolpers","Wetland_tribs","Wetland")]%>%drop_na(Date)%>%filter(Wetland=="GAVI")
check$Wetland_tribs[is.na(check$Wetland_tribs)]<-"GAVI-mainstem"
check <- check%>%filter(Wetland_tribs=="GAVI-mainstem")

```

I think I can just read in one file now...

```{r read in}
df <- read.csv(here::here("ProcessedData/SynopFlowAccu_20220419.csv"))

df$EOS_no[df$EOS_no == "EOS1"] <- "EOS_1"
df$EOS_no[df$EOS_no == "EOS2"] <- "EOS_2"
df$Date <- format(as.POSIXct(df$Date,format='%Y-%m-%d'))
df$Flux_ave <- signif(df$Flux_ave, digits = 3)

```
## Plot data

plot the data by wetland to see whats up.

Most of the streams go from dist = 0 is downstream and then progress upstream. Too bad, because we actually want it to be the other way around. The only one that doesn't need to be fixed in ANTE

```{r visualize streamprofile, echo=FALSE}
ggplot(data=df%>%filter(Wetland=="GAVItrib2"), aes(x=dist, y=ele_fit, group=1)) +
  geom_line()+
  geom_point()
```


#use plot below to visualize new stream profile
and flux total data

```{r visualize profile again, echo=FALSE}
ggplot(data=df%>%filter(Wetland=="GAVI"), aes(x=dist, y=ele_fit, group=1)) +
  geom_line()+
  geom_point()

ggplot(data=df %>%filter(Wetland=="GAVI")%>%drop_na(adjusted_ppm), aes(x=dist, y=Totalflux_umolpers, group=1)) +
  geom_line()+
  geom_point()
```


#join

```{r join and plot, echo=FALSE}


ggplot(df%>%drop_na(adjusted_ppm) %>% filter(dist<250)#%>%filter(Wetland!="COLM")
       , aes(x=dist, y=Totalflux_umolpers, group=Wetland)) +
  geom_line(aes(#linetype=Wetland,
    color=Wetland),
    size=2)


ggplot(df%>%drop_na(adjusted_ppm) %>% filter(dist>500)#%>%filter(Wetland!="COLM")
       , aes(x=dist, y=Totalflux_umolpers, group=Wetland)) +
  geom_line(aes(#linetype=Wetland,
    color=Wetland),
    size=2)
  

```

